---
title: "Qualtrics LLM Panel Preregistration"
author: "Colin Maggard and Claire Punturieri"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 4
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
---

# To do

Claire:
 - Rewrite questions to be more specific
 - Write out more specific qualities of simulated data
 - Write out models
 - Email Markus to ask about model/set up meeting

Colin:
  - Generating the data
  - Start outlining the study overview section

# Study Overview

## Specific Aims

## Data

# Purpose of Preregistration

## Outcomes

## Focal and Secondary Effects

# Data Generation

# Preregistered Analyses

Variables:
 - sub_id
 - pref_rating (how much would you like to receive a message in this style/tone)
 - pref_rating_style
 - pref_rating_tone
 - actual_rating (how helpful do you find this message)
 - style (informal, formal)
 - tone (value affirmation, norms, acknowledging, self-efficacy, caring/supportive, legitimizing)
 - context (high/increasing, low/increasing, high/decreasing, low/decreasing)
 - age
 - sex
 - gender_id
 - sexual_orientation
 - race_ethn
 - education
 - income
 - marital_status
 - no_in_household
 - minoritized
 - income_adj (will be calculated as: income / no_in_household)
 
## Do people have message tone and/or style preferences? (stated preferences from categories)

> Simulate data where subjects OVERALL prefer a particular tone and style (e.g., everyone loves acknowledging and formal)

```{r}
m1 <- lm(pref_rating_style ~ style, data = d)

m2 <- lm(pref_rating_tone ~ tone, data = d)
```

## Do people have actual message tone and/or style differences? (actual ratings from messages)

> Simulate data where subjects OVERALL rate a particular tone and style higher

## Are there demographics differences across tone and/or style preferences? (stated preferences from categories)

> Pick one demographic category of your choosing and have clear differences in preference stratified across that variable.

## Are there demographics differences across tone and/or style actual ratings? (actual ratings from messages)

> Same as above, but with clear differences in actual ratings across demographic variable.

## Do tone and style interact in how actual messages are rated?

> Simulate data where subjects prefer a tone in a particular style but not when it's another style (e.g., they like legitimizing when it's informal but not formal)

## What is the relationship between stated preferences and actual ratings? (LMEM)

> Simulate data where subjects stated preferences and actual ratings are similar

```{r}

```

## Are participant ratings more different across preference categories than within preference categories?

## Are participant ratings more different across actual categories than within actual categories?

## How does user context impact actual ratings?
 
# Notes

 - Are pref_rating_style/tone and actual_rating comparable? Should pref be "helpful" instead of like?
 - Should pref_rating be one variable or separated into two?
 - Are we going to use context?
 - Note that gender_id is fill in the blank so probably can't use in analyses. Should this be specific categories?
 - 
 
 