---
title: "Clean Panel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false

---

## Code Status

In progress

## Notes

***** NOTE: about 2/3s of the time I run this I get a 404 error from Qualtrics. Just retry until it works. ******


## Purpose

* Review incoming panel data
* Remove dropouts by screening method:
   * Unfinished
   * Previews
   * Duplicate Responses
   * CAPTCHA fails
   * Healthy screen fails
   * AUDIT fails
   * Consent declines
   * Age fails
   * Attention check fails 
   * Timing check fails 
* save out final clean dataset for modeling

## Set up

```{r setup, warning=FALSE}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/download_qualtrics.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")

#source function file
# source("functions/fun_opt.R")

path_qualtrics <- format_path("optimize/data_raw/qualtrics")
path_panel <- format_path("optimize/data_raw/panel")
path_processed <- format_path("optimize/data_processed")
path_credentials <- format_path("other")
```


 Get credentials
```{r}
token_qualtrics <- 
  get_credentials("qualtrics", file.path(path_credentials, "credentials.csv")) |>
  pull(token)
```

Download results by API and clean variable names

```{r}
panel_export_raw <- NULL

# Retry on intermittent 404s from Qualtrics until a successful download. I haven't gotten a 404 so I don't know if this works fully
# but it works on successful runs
repeat {
  panel_export_raw <- tryCatch(
    {
      download_qualtrics(
        survey_id = "SV_dbAKSR75ATWSo2q",
        api_token = token_qualtrics,
        display_progress = FALSE
      )
    },
    error = function(e) {
      if (str_detect(conditionMessage(e), "404")) {
        message("Qualtrics returned 404. Retrying in 5 seconds...")
        Sys.sleep(5)
        return(NULL)
      }
      stop(e)
    }
  )

  if (!is.null(panel_export_raw)) {
    break
  }
}

panel_export_raw <- panel_export_raw |>
  janitor::clean_names("snake")  |> 
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  # remove text intro variables
  select(-c(intro_1, audit_inst, q89, description,intro_tone, intro_context, x, x_1, x_2, x_3, x_4, x_5, x_6, x_7, x_8, x_9, x_10, x_11)) |>
    rename_with(~ str_replace_all(.x, pattern = ("^x"), replacement ="")) |>
    rename_with(~ str_replace_all(.x, pattern = "_1$", replacement ="")) |>
  #fix one that got caught by the rename  
  rename(audit_1 = audit)   |>
  glimpse()
```

Clean randomizer variables for easier reading (although I'm still leaving them in the dataframe)
```{r}
randomizer_vars <- panel_export_raw |>  select(response_id, starts_with("ro_"), starts_with("block_order")) |> 
  rename(tone_message_ro = ro_br_fl_99,
         survey_version_ro = ro_br_fl_12,
         survey1_block_ro = ro_br_fl_85,
         survey2_block_ro = ro_br_fl_23,
         survey3_block_ro = ro_br_fl_35,
         survey4_block_ro = ro_br_fl_47) |>
  mutate(tone_message_ro = if_else(tone_message_ro == "FL_146|FL_98", "tone first", "messages first")) |>
  mutate(survey_version_ro = case_when(survey_version_ro == "FL_81" ~ 1,
                                       survey_version_ro == "FL_82" ~ 2,
                                       survey_version_ro == "FL_83" ~ 3,
                                       survey_version_ro == "FL_84" ~ 4)) |>
  mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_86|FL_70|FL_59|FL_48",
                                                                        replacement = "hi"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_87|FL_71|FL_60|FL_49",
                                                                        replacement = "hd"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_88|FL_72|FL_61|FL_50",
                                                                        replacement = "li"))) |> 
   unite(context_order, survey1_block_ro:survey4_block_ro, sep = "") |>  
   mutate(block_1 = case_when(tone_message_ro == "tone first" ~ "tone",
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                             .default = "")) |>
   mutate(block_2= case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                               tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                             .default = "")) |>
   mutate(block_3 = case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>        
   mutate(block_4 = case_when(tone_message_ro == "messages first" ~ "tone",
                              tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>  
            glimpse()

# rejoin to main dataframe
panel_export <- panel_export_raw |>
  left_join(randomizer_vars)

```

There ARE variables in the export that aren't in the API download. Use the download to add them back in.
```{r}
panel_download <- read_csv(tibble(path = list.files(path_panel, pattern = "^panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
    janitor::clean_names("snake")  |> 
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  select(response_id, q_recaptcha_score, q_duplicate_respondent)


panel_export <- panel_export |>
  left_join(panel_download)
  
```




## Filtering by screenout

Start a tibble to track participant flow now that we've removed the most basic non-real responses
```{r}

panel_clean <- panel_export

flow <- tibble(flow = "total_submissions", 
               n_passed = nrow(panel_clean), 
               n_failed = NA) |> print()

```


### Finished surveys
```{r}
# remove incomplete submissions and update flow
flow <- flow |>
  full_join(tibble(flow = "finished", 
                   n_passed = nrow(panel_clean |> filter(finished == "1")), 
                   n_failed = nrow(panel_clean |> filter(finished == "0") ))) |>
  print()

panel_clean <- panel_clean |> filter(finished == "1") 


```


### Previews
```{r}
flow <- flow |>
  full_join(tibble(flow = "preview", 
                   n_passed = nrow(panel_clean |> filter(q_chl  == "anonymous")), 
                   n_failed = nrow(panel_clean |> filter(q_chl  == "preview") ))) |>
  print()
#remove previews
panel_clean <- panel_clean |> 
  filter(q_chl != "preview") 
```

### Duplicate responses

Note: Email from Qualtrics 2026_0225 states they removed q_duplicate_respondent and now are only using q_ballot_box_stuffing to show duplicates.

HOWEVER, all values of q_ballot_box_stuffing are NA. I will use the downloaded extra variables for now, which may be incomplete, and then continue to yell at qualtrics to provide me with valid information, since they seem to consistently ignore those requests.
```{r}

flow <- flow |>
  full_join(tibble(flow = "duplicate respondents (not available by API)", 
                   n_passed = panel_clean |> filter(is.na(q_duplicate_respondent)) |> nrow(),
                   n_failed = panel_clean |> filter(q_duplicate_respondent == "true") |> nrow())) |>
  print()

#remove duplicates
panel_clean <- panel_clean |> 
  filter(is.na(q_duplicate_respondent))
```

### Recaptcha score

- This variable is also missing from API pulls.
- We are keeping NA values (they took a captcha from the panel provider before hitting our survey) and values > .5
```{r}
flow <- flow |>
  full_join(tibble(flow = "captcha (not available by API)", 
                   n_passed = panel_clean |> filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5) |> nrow(),
                   n_failed = panel_clean |> filter(q_recaptcha_score <.5) |> nrow())) |>
  print()

#remove captcha fails
panel_clean <- panel_clean |> 
  filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5)


```

### Health Screener
```{r}
#add some summary variable
panel_clean <- panel_clean |> 
  mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) 


# All no's
flow <- flow |>
  full_join(tibble(flow = "health screener - all No's", 
                   n_passed = panel_clean |> filter(!all_no) |> nrow(),
                   n_failed = panel_clean |> filter(all_no) |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(!all_no) 

# non drinkers
flow <- flow |>
  full_join(tibble(flow = "health screener - non-binge drinker", 
                   n_passed = panel_clean |> filter(eligible_health == "eligible") |> nrow(),
                   n_failed = panel_clean |> filter(eligible_health == "ineligible") |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(eligible_health == "eligible")

```

### AUDIT Screener
```{r}
flow <- flow |>
  full_join(tibble(flow = "AUDIT screener", 
                   n_passed = panel_clean |> filter(audit_score >= 8) |> nrow(),
                   n_failed = panel_clean |> filter(audit_score < 8) |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(audit_score >= 8)
```

### Consent

```{r}
flow <- flow |>
  full_join(tibble(flow = "consented", 
                   n_passed = panel_clean |> 
                     filter(consent_agree == "I consent to participate and wish to proceed to the survey.") |> nrow(),
                   n_failed = panel_clean |> 
                     filter(consent_agree == "I wish to exit the survey without providing consent.") |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(consent_agree == "I consent to participate and wish to proceed to the survey.") 
```

### Age

Has anyone got this far who was under 18 and screened out on demographics?
```{r}
flow <- flow |>
  full_join(tibble(flow = "over 18", 
                   n_passed = panel_clean |> 
                     filter(q1_age >=18) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(q1_age <18) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(q1_age >=18) 

```


### Per-block failures

Set up thresholds and pull our attention and timing variables
```{r}
#| echo: false

#get timing thresholds
timing <- tibble(block = c(
"tone", 
"1_hi", "1_hd", "1_li",
"2_hi", "2_hd", "2_li", 
"3_hi", "3_hd", "3_li", 
"4_hi", "4_hd", "4_li"),
threshold = c(
59,
101, 104, 94,
102, 104, 98,
102, 106, 98,
100, 105, 99),
max_100 = c(
235,
405, 417, 375,
406, 414, 393,
410, 422, 394,
400, 419, 397))

panel_integrity <- panel_clean |>
  select(response_id, contains((c("timing_2","attention"))), starts_with("block_order"), tone_order, survey_order, survey_version, block_1:block_4) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_2", replacement ="")) |>
  glimpse()
```

Block 1 fails (Timing only)
```{r}
block1 <- panel_integrity |>
  rowwise() |>
  mutate(block_1_timing = (panel_integrity |> 
           select(ends_with(block_1)) |> 
           filter(response_id == panel_integrity$response_id) |> pull()) ) |> 
  mutate(block_1_threshold = if_else(is.na(block_1), NA, timing$threshold[timing$block == block_1])) |> 
  mutate(block1_timing_fail = block_1_timing < block_1_threshold) |>
  glimpse()

block1 |> select(response_id, block1_timing_fail) |> glimpse()

flow <- flow |>
  full_join(tibble(flow = "block1 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block1 |> filter(!block1_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block1 |> filter(block1_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block1 |> filter(!block1_timing_fail) |> pull(response_id)))

```


Block 2 Timing:
```{r}
block2 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_2_timing = panel_integrity |> 
           select(ends_with(block_2)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_2_threshold = if_else(is.na(block_2), NA, timing$threshold[timing$block == block_2])) |> 
  mutate(block2_timing_fail = block_2_timing < block_2_threshold) |>
  mutate(block_2_attention = panel_integrity |> 
           select(starts_with(block_2) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block2 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block2_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id)))

```

Block 2 Attention: 
```{r}
flow <- flow |>
  full_join(tibble(flow = "block2 attention", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block_2_attention == "Strongly Disagree" || block_2_attention == "") |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block_2_attention != "Strongly Disagree" && !(block_2_attention == "")) |> pull(response_id)))  |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block2 |> filter(block_2_attention == "Strongly Disagree" || block_2_attention == "") |> pull(response_id)))
```



Block 3 Timing:
```{r}
block3 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_3_timing = panel_integrity |> 
           select(ends_with(block_3)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_3_threshold = if_else(is.na(block_3), NA, timing$threshold[timing$block == block_3])) |> 
  mutate(block3_timing_fail = block_3_timing < block_3_threshold) |>
  mutate(block_3_attention = panel_integrity |> 
           select(starts_with(block_3) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block3 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block3_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id)))

```

Block 3 Attention: 
```{r}
flow <- flow |>
  full_join(tibble(flow = "block3 attention", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block_3_attention == "Strongly Disagree" || block_3_attention == "") |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block_3_attention != "Strongly Disagree" && !(block_3_attention == "")) |> pull(response_id)))  |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block3 |> filter(block_3_attention == "Strongly Disagree" || block_3_attention == "") |> pull(response_id)))
```



Block 4 (Timing only)
```{r}
block4 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_4_timing = panel_integrity |> 
           select(ends_with(block_4)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_4_threshold = if_else(is.na(block_4), NA, timing$threshold[timing$block == block_4])) |> 
  mutate(block4_timing_fail = block_4_timing < block_4_threshold) |>
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block4 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block4 |> filter(block4_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id)))

```

Write out clean sample
```{r}
panel_clean |> write_csv(file.path(path_processed, str_c("panel/panel_clean_", today(), ".csv")))
```

```{r}

```

