---
title: "Panel EDA"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false

---

## Code Status

In progress


## Purpose

* Review incoming panel data
* remove dropouts by screening method:
   * CAPTCHA fails
   * Healthy screen fails
   * AUDIT fails 
   * Attention check fails 
   * Timing check fails 
* save out final clean dataset for modeling

## Set up

```{r setup, warning=FALSE}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/download_qualtrics.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")

#source function file
# source("functions/fun_opt.R")

path_qualtrics <- format_path("optimize/data_raw/qualtrics")
path_panel <- format_path("optimize/data_raw/panel")
path_processed <- format_path("optimize/data_processed")
path_credentials <- format_path("other")
```


 Get credentials
```{r}
token_qualtrics <- 
  get_credentials("qualtrics", file.path(path_credentials, "credentials.csv")) |>
  pull(token)
```

Download results by API and clean variable names

***** NOTE: about half the time I run this I get a 404 error from Qualtrics. Just retry. ******

```{r}
panel_export_raw <- download_qualtrics(survey_id = "SV_dbAKSR75ATWSo2q", api_token = token_qualtrics,
                             display_progress = FALSE) |>
  janitor::clean_names("snake")  |> 
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  # remove text intro variables
  select(-c(intro_1, audit_inst, q89, description,intro_tone, intro_context, x, x_1, x_2, x_3, x_4, x_5, x_6, x_7, x_9, x_9, x_10, x_11)) |>
    rename_with(~ str_replace_all(.x, pattern = ("^x"), replacement ="")) |>
    rename_with(~ str_replace_all(.x, pattern = "_1$", replacement ="")) |>
  #fix one that got caught by the rename  
  rename(audit_1 = audit)   |>
  glimpse()
```

Clean randomizer variables for easier reading (although I'm still leaving them in the dataframe)
```{r}
randomizer_vars <- panel_export_raw |>  select(response_id, starts_with("ro_"), starts_with("block_order")) |> 
  rename(tone_message_ro = ro_br_fl_99,
         survey_version_ro = ro_br_fl_12,
         survey1_block_ro = ro_br_fl_85,
         survey2_block_ro = ro_br_fl_23,
         survey3_block_ro = ro_br_fl_35,
         survey4_block_ro = ro_br_fl_47) |>
  mutate(tone_message_ro = if_else(tone_message_ro == "FL_146|FL_98", "tone first", "messages first")) |>
  mutate(survey_version_ro = case_when(survey_version_ro == "FL_81" ~ 1,
                                       survey_version_ro == "FL_82" ~ 2,
                                       survey_version_ro == "FL_83" ~ 3,
                                       survey_version_ro == "FL_84" ~ 4)) |>
  mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_86|FL_70|FL_59|FL_48",
                                                                        replacement = "hi"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_87|FL_71|FL_60|FL_49",
                                                                        replacement = "hd"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_88|FL_72|FL_61|FL_50",
                                                                        replacement = "li"))) |> 
   unite(context_order, survey1_block_ro:survey4_block_ro, sep = "") |>  
   mutate(block_1 = case_when(tone_message_ro == "tone first" ~ "tone",
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                             .default = "")) |>
   mutate(block_2= case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                               tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                             .default = "")) |>
   mutate(block_3 = case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>        
   mutate(block_4 = case_when(tone_message_ro == "messages first" ~ "tone",
                              tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>  
            glimpse()

# rejoin to main dataframe
panel_export <- panel_export_raw |>
  left_join(randomizer_vars)

```

There ARE variables in the export that aren't in the API download. Use the download to add them back in.
```{r}
panel_download <- read_csv(tibble(path = list.files(path_panel, pattern = "panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
    janitor::clean_names("snake")  |> 
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  select(response_id, q_recaptcha_score, q_duplicate_respondent)


panel_export <- panel_export |>
  left_join(panel_download)
  
```




## Filtering by screenout

Start a tibble to track participant flow now that we've removed the most basic non-real responses
```{r}

panel_clean <- panel_export

flow <- tibble(flow = "total_submissions", 
               n_passed = nrow(panel_clean), 
               n_failed = NA) |> print()

```


### Finished surveys
```{r}
# remove incomplete submissions and update flow
flow <- flow |>
  full_join(tibble(flow = "finished", 
                   n_passed = nrow(panel_clean |> filter(finished == "1")), 
                   n_failed = nrow(panel_clean |> filter(finished == "0") ))) |>
  print()

panel_clean <- panel_clean |> filter(finished == "1") 


```


### Previews
```{r}
flow <- flow |>
  full_join(tibble(flow = "preview", 
                   n_passed = nrow(panel_clean |> filter(q_chl  == "anonymous")), 
                   n_failed = nrow(panel_clean |> filter(q_chl  == "preview") ))) |>
  print()
#remove previews
panel_clean <- panel_clean |> 
  filter(q_chl != "preview") 
```

### Duplicate responses

Note: Email from Qualtrics 2026_0225 states they removed q_duplicate_respondent and now are only using q_ballot_box_stuffing to show duplicates.

HOWEVER, all values of q_ballot_box_stuffing are NA. I will use the downloaded extra variables for now, which may be incomplete, and then continue to yell at qualtrics to provide me with valid information, since they seem to consistently ignore those requests.
```{r}

flow <- flow |>
  full_join(tibble(flow = "duplicate respondents (not available by API)", 
                   n_passed = panel_clean |> filter(is.na(q_duplicate_respondent)) |> nrow(),
                   n_failed = panel_clean |> filter(q_duplicate_respondent == "true") |> nrow())) |>
  print()

#remove duplicates
panel_clean <- panel_clean |> 
  filter(is.na(q_duplicate_respondent))
```

### Recaptcha score

- This variable is also missing from API pulls.
- We are keeping NA values (they took a captcha from the panel provider before hitting our survey) and values > .5
```{r}
flow <- flow |>
  full_join(tibble(flow = "captcha (not available by API)", 
                   n_passed = panel_clean |> filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5) |> nrow(),
                   n_failed = panel_clean |> filter(q_recaptcha_score <.5) |> nrow())) |>
  print()

#remove captcha fails
panel_clean <- panel_clean |> 
  filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5)


```

### Health Screener
```{r}
#add a summary variable
panel_clean <- panel_clean |> 
  mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) 

flow <- flow |>
  full_join(tibble(flow = "health screener", 
                   n_passed = panel_clean |> filter(eligible_health == "eligible") |> nrow(),
                   n_failed = panel_clean |> filter(eligible_health == "ineligible") |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(eligible_health == "eligible")

```

### AUDIT Screener
```{r}
flow <- flow |>
  full_join(tibble(flow = "AUDIT screener", 
                   n_passed = panel_clean |> filter(audit_score >= 8) |> nrow(),
                   n_failed = panel_clean |> filter(audit_score < 8) |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(audit_score >= 8)
```

### Consent

```{r}
flow <- flow |>
  full_join(tibble(flow = "consented", 
                   n_passed = panel_clean |> 
                     filter(consent_agree == "I consent to participate and wish to proceed to the survey.") |> nrow(),
                   n_failed = panel_clean |> 
                     filter(consent_agree == "I wish to exit the survey without providing consent.") |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(consent_agree == "I consent to participate and wish to proceed to the survey.") 
```

### Age

Has anyone got this far who was under 18 and screened out on demographics?
```{r}
flow <- flow |>
  full_join(tibble(flow = "over 18", 
                   n_passed = panel_clean |> 
                     filter(q1_age >=18) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(q1_age <18) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(q1_age >=18) 

```


### Per-block failures

Set up thresholds and pull our attention and timing variables
```{r}
#| echo: false

#get timing thresholds
timing <- tibble(block = c(
"tone", 
"1_hi", "1_hd", "1_li",
"2_hi", "2_hd", "2_li", 
"3_hi", "3_hd", "3_li", 
"4_hi", "4_hd", "4_li"),
threshold = c(
59,
101, 104, 94,
102, 104, 98,
102, 106, 98,
100, 105, 99),
max_100 = c(
235,
405, 417, 375,
406, 414, 393,
410, 422, 394,
400, 419, 397))

panel_integrity <- panel_clean |>
  select(response_id, contains((c("timing_2","attention"))), starts_with("block_order"), tone_order, survey_order, survey_version, block_1:block_4) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_2", replacement ="")) |>
  glimpse()
```

Block 1 fails (Timing only)
```{r}
block1 <- panel_integrity |>
  rowwise() |>
  mutate(block_1_timing = (panel_integrity |> 
           select(ends_with(block_1)) |> 
           filter(response_id == panel_integrity$response_id) |> pull()) ) |> 
  mutate(block_1_threshold = if_else(is.na(block_1), NA, timing$threshold[timing$block == block_1])) |> 
  mutate(block1_timing_fail = block_1_timing < block_1_threshold) |>
  glimpse()

block1 |> select(response_id, block1_timing_fail) |> glimpse()

flow <- flow |>
  full_join(tibble(flow = "block1 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block1 |> filter(!block1_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block1 |> filter(block1_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block1 |> filter(!block1_timing_fail) |> pull(response_id)))

```


Block 2 Timing:
```{r}
block2 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_2_timing = panel_integrity |> 
           select(ends_with(block_2)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_2_threshold = if_else(is.na(block_2), NA, timing$threshold[timing$block == block_2])) |> 
  mutate(block2_timing_fail = block_2_timing < block_2_threshold) |>
  mutate(block_2_attention = panel_integrity |> 
           select(starts_with(block_2) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block2 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block2_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id)))

```

Block 2 Attention: 
```{r}
flow <- flow |>
  full_join(tibble(flow = "block2 attention", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block_2_attention == "Strongly Disagree" || block_2_attention == "") |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block2 |> filter(block_2_attention != "Strongly Disagree" && !(block_2_attention == "")) |> pull(response_id)))  |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block2 |> filter(block_2_attention == "Strongly Disagree" || block_2_attention == "") |> pull(response_id)))
```



Block 3 Timing:
```{r}
block3 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_3_timing = panel_integrity |> 
           select(ends_with(block_3)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_3_threshold = if_else(is.na(block_3), NA, timing$threshold[timing$block == block_3])) |> 
  mutate(block3_timing_fail = block_3_timing < block_3_threshold) |>
  mutate(block_3_attention = panel_integrity |> 
           select(starts_with(block_3) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block3 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block3_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id)))

```

Block 3 Attention: 
```{r}
flow <- flow |>
  full_join(tibble(flow = "block3 attention", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block_3_attention == "Strongly Disagree" || block_3_attention == "") |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block3 |> filter(block_3_attention != "Strongly Disagree" && !(block_3_attention == "")) |> pull(response_id)))  |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block3 |> filter(block_3_attention == "Strongly Disagree" || block_3_attention == "") |> pull(response_id)))
```



Block 4 (Timing only)
```{r}
block4 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(block_4_timing = panel_integrity |> 
           select(ends_with(block_4)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_4_threshold = if_else(is.na(block_4), NA, timing$threshold[timing$block == block_4])) |> 
  mutate(block4_timing_fail = block_4_timing < block_4_threshold) |>
  glimpse()

flow <- flow |>
  full_join(tibble(flow = "block4 timing", 
                   n_passed = panel_clean |> 
                     filter(response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id))) |> nrow(),
                   n_failed = panel_clean |> 
                     filter(response_id %in% (block4 |> filter(block4_timing_fail) |> pull(response_id))) |> nrow()
                            )) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id)))

```

Write out clean sample
```{r}
panel_clean |> write_csv(file.path(path_processed, str_c("panel/panel_clean_", today(), ".csv")))
```



## SUSAN EDA: Check our final sample against qualtric's 
```{r}
qualtrics_completes <- panel_export |> filter(term == "") 
nrow(qualtrics_completes)

bad_qualtrics <- qualtrics_completes |> filter(!(response_id %in% panel_clean$response_id)) 


panel_export |>
  filter(response_id %in% bad_qualtrics$response_id) |>
  select(response_id, q_recaptcha_score, q_duplicate_respondent) |>
  print(n=Inf)

#Check the completes export
q_completes <- read_csv(tibble(path = list.files(path_panel, pattern = "completes_panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
    janitor::clean_names("snake")  |> 
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  select(response_id, q_recaptcha_score, q_duplicate_respondent)

bad_completes <- q_completes$response_id[which(!(q_completes$response_id %in% panel_clean$response_id ))] |> unique()

panel_export |> filter(response_id %in% bad_completes) |> glimpse()

```

* Qualtrics has still not filtered out all captcha fails and duplicate reponses. We need to regularly send them these response_ID_ids to be removed.

Ask them to remove:
* 2026_0227: R_3dxTxqxUzeApWSt, captcha = .4


### Location checks

Does the city/state that they reported match their current lat/long?

```{r}
#Check for errors
panel_clean$id_location_1_text
panel_clean$id_location_2_text

#Fix a misspelling first
panel_clean$id_location_1_text[panel_clean$id_location_1_text == "Tuscon"] <-  "Tucson"

# need tidygeocoder package this does take a while
panel_location <- panel_clean |> 
  select(response_id, actual_latitude = location_latitude, actual_longitude = location_longitude, 
         ip = ip_address, grocery_name = q12_grocer_1_text,
         grocery_location = q12_grocer_2_text, reported_city = id_location_1_text, reported_state = id_location_2_text) |>
  tidygeocoder::geocode(city = reported_city, state = reported_state, method = "osm") |>
  rename(reported_city_latitude = lat, reported_city_longitude = long) |>
  mutate(euclidian_dist = sqrt((actual_latitude - reported_city_latitude)^2 + (actual_longitude - reported_city_longitude)^2))
```

Plot euclidian distances in box and whisker plot

```{r}
ggplot(panel_location, aes(x = euclidian_dist)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Euclidean Distance",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Euclidean Distance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Let's do this by miles since lat/long are not intuitive units of measurement for people
Per Britannica, "the length of a degree of arc of latitude is approximately 111 km (69 miles), varying, because of the nonuniformity of Earth’s curvature
The distance per degree of longitude at the Equator is about 111.32 km (69.18 miles) and at the poles, 0."
Assuming the US is somewhere between the equator and the north pole, we can use the midpoint for longitude, which is 34 (surprisingly, changing this from 69 did not change much). 
```{r}
panel_location <- panel_location |>
  mutate(
    # Calculate distance in miles using 34 miles per degree for longitude and 69 for latitude
    lat_diff_miles = (actual_latitude - reported_city_latitude) * 69,
    lon_diff_miles = (actual_longitude - reported_city_longitude) * 34 * cos(mean(actual_latitude, na.rm = TRUE) * pi / 180),
    euclidian_dist_miles = sqrt(lat_diff_miles^2 + lon_diff_miles^2)
  )

ggplot(panel_location, aes(x = euclidian_dist_miles)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Distance in Miles",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Distance (Miles)") +
  theme_minimal()
```


Plot everyone's city and actual locations on a map
```{r}

panel_location <- panel_location |>
  rowwise() |>
  mutate(dist_miles = geosphere::distGeo(c(actual_longitude, actual_latitude), c(reported_city_longitude, reported_city_latitude))/1609.344) 

panel_location |> select(dist_miles) |> arrange(desc(dist_miles)) |> print(n=Inf)

```

Plot just the longer distances (10 people at > 50 miles)
```{r}
map_places <- panel_location |>
  filter(dist_miles > 50) |>
  select(response_id, actual_latitude, actual_longitude, reported_city_latitude, reported_city_longitude, dist_miles, reported_city, reported_state) |>
  rowwise() |> 
  tidygeocoder::reverse_geocode(lat=actual_latitude, long = actual_longitude) |>
  pivot_longer(c(actual_latitude, reported_city_latitude), names_to = "lat_type", values_to = "lat") |>
  pivot_longer(c(actual_longitude, reported_city_longitude), names_to = "lon_type", values_to = "lon") |>  
  rowwise() |>
  mutate(color = case_when(str_detect(lat_type, "actual") ~ "red",
                           str_detect(lat_type, "reported") ~ "blue"
                           )) |>
  ungroup() |>
  mutate(lat_type = str_extract(lat_type, "actual|reported")) |>
  mutate(lon_type = str_extract(lon_type, "actual|reported")) |>
  filter(lat_type == lon_type)

map_places |>  plot_places(color = "color", label_column = "response_id")
```

* The two most egregious are someone from Washington State in Las Vegas, and someone from Danbury CT in Raleigh, NC.
* One person in Los Angeles replicates the EXACT LOCATION issue we saw in Risk2 screening - their actual location shows up in a random park south of LA!
* Several people from near Lousiana are showing up in and around New Orleans - Mardi Gras?
* The others mostly seem reasonable - their actual location shows up in a major city near their reported location.


## EDA: Randomizers

Tone survey vs message survey randomizer
```{r}
panel_clean |> group_by(tone_order) |> tally()
```


Survey randomizer
```{r}
panel_clean |> group_by(survey_version) |> tally()
```


Block order randomizer
```{r}
panel_clean |> group_by(block_order_hi, block_order_hd, block_order_li) |> tally()
```

* It's not as equally randomized as I'd hope but I'm guessing that's due to the huge number of exclusions and that it will even out by the time we get the full sample


## Final summary of exclusions
```{r}
flow |> glimpse()
```

