---
title: "Panel EDA"
format: html
---

Colin: If you want to view all output as HTML, just render this using the render button or by going unto the terminal tab and entering `quarto render check_panel.qmd`

## Set up

```{r setup, warning=FALSE}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")

#source function file
# source("functions/fun_opt.R")

path_qualtrics <- format_path("optimize/data_raw/qualtrics")
path_panel <- format_path("optimize/data_raw/panel")
path_processed <- format_path("optimize/data_processed")
path_credentials <- format_path("other")
```


## Get credentials
```{r}
token_qualtrics <- 
  get_credentials("qualtrics", file.path(path_credentials, "credentials.csv")) |>
  pull(token)
```

Looks like I'm not getting all responses via API - check the exported version
```{r}
panel_export_raw <- read_csv(tibble(path = list.files(path_panel, pattern = "panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
  mutate(across(everything(), .fns = parse_guess)) |> #read_csv failed to correctly guess coltypes due to the two extra character headers, this re-guesses
  janitor::clean_names("snake") |>
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  glimpse()
```


Basic EDA
```{r}

panel_export <-  panel_export_raw

panel_complete <- panel_export |> filter(!is.na(id_location_2)) 
panel_export |> distinct(id_location_1)  #29 distinct + NA, which matches the above

panel_export |> nrow()

#Finished?
finished <- panel_export |> filter(finished == "TRUE") |> nrow() 
unfinished <- panel_export |> filter(finished == "FALSE") |> nrow() 

table(panel_export$finished) 

skimr::skim(panel_export$finished)

skimr::skim(panel_export$progress) # progress is another way to measure how far through they got
panel_export |> group_by(progress) |> tally()

```
1. With previous downloads, every survey is finished because any termination led to an end of survey block, now there are a few incompletes
2. As of `r today()` there are `r panel_export |> nrow()` responses, `r unfinished` are incomplete, `r finished` are finished
3. Of the incompletes, progress varies between 1% and 16%. 

To improve the EDA as we go along I'm going to remove responses that shouldn't be kept, as we find them.
```{r}
# remove incomplete submissions
panel_export <- panel_export |> filter(finished == "TRUE") 
```

# EDA - qualtrics variables

These variables were all added by Qualtrics before launch. What do they mean? What are their values? Which ones do we need to use to filter people out of a "clean" dataset
```{r}
qualtrics_vars <- panel_export |> select(response_id, opp:project_token, starts_with("q_")) |> glimpse()

qualtrics_vars |> skimr::skim()

# IMPORTANT VARIABLES
panel_export$term |> table() # seems to have a rule-out value for everyone who did not complete, is NA for those who did complete
panel_export$q_chl |> table() #distinguishes between preview surveys and regular - we need to exclude the previews
panel_export$q_recaptcha_score |> table() # info on cutoffs below, need to exclude on this
panel_export|> skimr::skim(q_duplicate_respondent) #duplicate respondents, need to exclude
panel_export$q_duplicate_respondent |> table()

panel_export$q_total_duration |> table() |> head(5) # (long output truncated)- duration will be important 
panel_export |> skimr::skim(q_total_duration)  # more info via skim
panel_export |> skimr::skim(duration_in_seconds) #identical to q_total_duration. This is the default variable, not sure why qualtrics added the other one instead of using this directly


# these will be important but are all NA right now
panel_export$q_quality_score |> table()
panel_export$q_ballot_box_stuffing |> table()
panel_export$q_quality_timestamp |> table()


```

Remove previews and duplicates
```{r}

panel_export <- panel_export |> 
  # remove preview submissions
  filter(q_chl != "preview") |> 
# remove duplicate respondents
  filter(is.na(q_duplicate_respondent)) 

```


More qualtrics variables:
```{r}

# These do not seem relevant to us

panel_export$opp |> table()  # seems to be the name of our study in their records
panel_export$q_url |> table() |> head(5) # (long output truncated) this seems to be the actual URLs used - guessing it sets many of the following values
panel_export$qpmid  |> table() # qualtrics panel ID - probably their internal number for our study
panel_export |> group_by(vendor) |> tally() #Kantar is a market research company - maybe who they are using to sample for us since NA for most

## These I can't guess at the meanings
panel_export$svid |> table()
panel_export$kid |> table() |> head(5) #  (long output truncated) 
panel_export$tg |> table()
panel_export$gc |> table()
panel_export$project_token_a |> table()
panel_export$project_token_b  |> table()
panel_export$supplier_id |> table()
panel_export$os_api_transaction_id|> table() |> head(5)  #  (long output truncated) 
panel_export$ps |> table()
panel_export$project_token |> table()




```

Another look at the panel_export$term (termination variable)
```{r}
panel_export |> group_by(term) |> tally()
```

1. 3 opted not to consent
2. 1233 were non-alcoholic by the health screener.
3. 19 selected all No's in the health survey
4. 107 failed on the audit score
5. `r panel_export |> group_by(term) |> tally() |> filter(str_detect(term, "survey")) |> pull(n) |> sum()` failed either the attention check or the timing variable in one of the 4 message surveys
6. 49 failed the speed check in the tone survey
7. 59 are NA, meaning not terminated for any other reason

# EDA - screening

```{r}
screening <- panel_export |> 
  select(response_id, term, q_recaptcha_score, starts_with(c("health", "audit"))) |>
  mutate(eligible_health = if_else(health_drink == "No" & !(all(3:7) == "No"), "eligible", "ineligible")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |> 
  glimpse()

screening |> skimr::skim(q_recaptcha_score)

#how many of those still finished the survey?
panel_export |> filter(is.na(q_recaptcha_score)) |> filter(!is.na(id_location_2)) # One!!

#how far did the others get? Use the qualtrics termination variable
screening |> filter(is.na(q_recaptcha_score)) |> select(term) |> table()

#How many passed captcha
screening |> filter(q_recaptcha_score > .5) |> nrow() / nrow(panel_export)
                                        
screening |> group_by(eligible_health) |> tally()
screening |> group_by(eligible_audit) |> tally()

# let's go a little deeper and see how people filter out at each level
screening <- screening |> 
  mutate(na_captcha = is.na(q_recaptcha_score),
         low_captcha = q_recaptcha_score < .5,
         all_no = all(3:7) == "No",
         no_drink = health_drink == "No",
         fail_audit = eligible_audit == "ineligible") |> 
  glimpse()

screening |> group_by(na_captcha, low_captcha, all_no, no_drink, fail_audit) |> tally()


#add the health screening eligiblity variable back into the main dataframe, for cleaning later
panel_export <- panel_export |>
  mutate(eligible_health = if_else(health_drink == "No" & !(all(3:7) == "No"), "eligible", "ineligible")) 

```

1. 73 of q_recaptcha score are NA. Of those, only one finished the survey. What do we do with these?
2. ~87% of recaptcha scores are over .5: See [this article](https://pmc.ncbi.nlm.nih.gov/articles/PMC10818231/) for interpretation: 
   * Q_RecaptchaScore returns a score between 0.0 and 1.0 that Qualtrics records as part of the survey response.  Recommended 0.5 score as the threshold for fraud, where a score under 0.5 is deemed likely to be a bot.
3. 550 people were eligible via the health survey
4. 414 of those were eligible via the AUDIT

Start a tibble showing participant flow
```{r}
flow <- tibble(total_submissions = nrow(panel_export),
               passed_captcha = nrow(panel_export |> filter(q_recaptcha_score > .5 | is.na(q_recaptcha_score))),
               passed_health_survey = nrow(panel_export |> filter(eligible_health == "eligible")),
               passed_audit = nrow(panel_export |> filter(audit_score > 7)),
               consented = nrow(panel_export |> filter((consent_agree == "I consent to participate and wish to proceed to the survey.")))) |> glimpse()
```


Look more at people marked Audit_score/not_alcoholic by the term variable

```{r}
alcohol_rule_out <-  panel_export |>
  select(response_id, term, starts_with(c("health", "audit"))) |>
  filter(term %in% c("audit_score", "not_alcoholic")) |>
  glimpse()

alcohol_rule_out |>
  filter(term == "not_alcoholic") |>
  group_by(health_drink) |>
  tally()
  
alcohol_rule_out |>  
  filter(term == "not_alcoholic") |>
  filter(health_drink == "No")

panel_export |> filter(term == "no_Selected") |>
  select(response_id, starts_with("health"))
  
```

* Most of the people who have a termination reason of "not alcoholic" indicated "Yes" to the alcohol question on the health survey
* However 7 answered all no's, but 19 people who did that too have "no_selected" as their termination reason. Maybe that was added later?
* Epidemiology: per [NIAAA](https://www.niaaa.nih.gov/alcohols-effects-health/alcohol-topics/alcohol-facts-and-statistics/alcohol-use-disorder-aud-united-states-age-groups-and-demographic-characteristics): As of 2024, 27.1 million adults ages 18 and older (10.3% in this age group) had AUD in the past year. We're looking at about 25% in this sample - 1600 passed captcha, 402 passed audit


# EDA - audit screener
```{r}
panel_audit <- panel_export |>
  select(response_id, starts_with("audit")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |>
  glimpse()

panel_audit |> group_by(eligible_audit) |> tally()

panel_audit |> filter(eligible_audit == "ineligible") |> glimpse()


panel_audit |> group_by(audit_1) |> tally()

panel_audit |> filter(audit_1 == "Never") |> nrow()


panel_audit |>
  filter(audit_1 == "Never") |>
  group_by(audit_9, audit_10) |>
  tally()

#skim all audit scores
panel_audit |> filter(!is.na(audit_score)) |> skimr::skim(audit_score)

#skim just those eligible
panel_audit |> filter(eligible_audit == "eligible") |> skimr::skim(audit_score)

#people with 40 scores

panel_export |> filter(audit_score >=35) |> group_by(term) |> tally()

```


1. Of the 40 people who never drank per audit_1, only one was eligible
2. Of 509 people who completed the audit, mean was 15.9, SD 7.76, range 0-40
3. Of the 402 eligible, mean was 19.2, SD 7.76, range 0-40
4. Only 1 person got a 40 on the audit, and they screened out for a different reason. Only 2 people who got over 35 on the audit, finished the survey.

# EDA - our data integrity variables
```{r}

#first set up a tibble with the actual cutoff thresholds we set for our timing variables
timing <- tibble(block = c(
"tone",
"1_hi",
"1_hd",
"1_li",
"2_hi",
"2_hd",
"2_li",
"3_hi",
"3_hd",
"3_li",
"4_hi",
"4_hd",
"4_li"),
threshold = c(
59,
101,
104,
94,
102,
104,
98,
102,
106,
98,
100,
105,
99),
max_100 = c(
235,
405,
417,
375,
406,
414,
393,
410,
422,
394,
400,
419,
397)
)



panel_integrity <- panel_export |>
  select(response_id, contains((c("last_click","attention")))) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_last_click", replacement ="")) |>
  rename_with(~ str_replace_all(.x, pattern = "x", replacement ="")) |>
  glimpse()

panel_integrity |> 
  skimr::skim()


#filter to the vars of interest and join with the timing values
timing_checks <- panel_integrity |> 
  skimr::skim() |>
  select(block=skim_variable, skim_type, complete_rate, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  select(-skim_type) |>
  filter(!str_detect(block, "attention")) |>
  full_join(timing) |>
  mutate() |>
  glimpse()
```

Colin:

* How many people failed the attention checks (DONE, pending review)
```{r}

# get people who answered the attention check
panel_attention <- panel_integrity |> 
  rowwise() |>
  mutate(
    attention_check = c_across(contains("attention")) |> 
      na.omit() |> 
      unique() |> 
      (\(x) if(length(x) > 1) "Multiple Values" else if(length(x) == 1) x else NA)() # shouldn't happen, coding error
  ) |>
  ungroup() |>
  filter(!is.na(attention_check)) |>
  # recode as factor
  mutate(attention_check = factor(attention_check, 
                                   levels = c("Strongly Agree", "Agree", "Somewhat Agree", 
                                             "Neutral", "Somewhat Disagree", "Disagree", 
                                             "Strongly Disagree", "Multiple Values"))) |>
  select(response_id, attention_check)

# get counts of those who answered the attention check
panel_attention |> count(attention_check)

# get counts of those who failed the attention check
attention_fail <- panel_attention |>
  filter(attention_check != "Strongly Disagree")

cat(nrow(attention_fail))

# get counts of those who passed the attention check
attention_pass <- panel_attention |>
  filter(attention_check == "Strongly Disagree")

cat(nrow(attention_pass))

# calculate proportion of fails
nrow(attention_fail) / nrow(panel_attention) 
```

* Use the timing_checks dataframe to figure out where the mean/median lie with respect to the threshold. It looks like we're being too aggressive and should raise our thresholds but until we can see how they go together more cleanly it's hard to tell (Done pending final review)

```{r}
timing_summary <- timing_checks |>
  select(block, mean, median, threshold) |>
  mutate(block = str_remove_all(block, "`")) |>
  filter(block != "tone" & !is.na(block) & block != "response_id") |>
  group_by(block) |>
  summarise(mean = mean(mean, na.rm = TRUE),
            median = mean(median, na.rm = TRUE),
            threshold = mean(threshold, na.rm = TRUE),
            .groups = "drop")

total_row <- tibble(block = "Total",
                    mean = sum(timing_summary$mean, na.rm = TRUE),
                    median = sum(timing_summary$median, na.rm = TRUE),
                    threshold = sum(timing_summary$threshold, na.rm = TRUE))

timing_summary <- bind_rows(timing_summary, total_row)

timing_summary |>
  knitr::kable(digits = 1, caption = "Mean, Median, and Threshold Comparison")
```

* for the people that failed the timing checks (especially those in the 2nd or 3rd message block), would we want to preserve them for partial analysis? (I think failing 1 message block is fine)

I think there's an order x block interaction effect with timing, let's look at that
```{r}
# block_order <- panel_export |>
#   select(response_id, tone_order, survey_version, block_order_hi, block_order_hd, block_order_li, contains((c("last_click","attention")))) |>
#   rename_with(~ str_replace_all(.x, pattern = "_timing_last_click", replacement ="")) |>
#   rename_with(~ str_replace_all(.x, pattern = "x", replacement ="")) |>
#   glimpse()
# 
# #difference in tone timing mean/sd by tone survey order
# block_order |> group_by(tone_order) |> skimr::skim(tone)
# 
# 
# # look at block order by survey
# survey_1 <- block_order |>
#   filter(survey_version == 1) |>
#   select(-c(starts_with(c("2", "3", "4")))) |>
#   mutate(block_1 = case_when(tone_order == 2 & block_order_hi == 1 ~ `1_hi`,
#                               tone_order == 2 &  block_order_hd == 1 ~ `1_hd`,
#                               tone_order == 2 &  block_order_hi == 1 ~ `1_hi`,
#                               tone_order == 1 ~ tone,
#                                .default = NA)) |>
#   mutate(block_2 = case_when(tone_order == 1 & block_order_hi == 1 ~ `1_hi`,
#                              tone_order == 1 &  block_order_hd == 1 ~ `1_hd`,
#                              tone_order == 1 &  block_order_hi == 1 ~ `1_hi`,
#                              tone_order == 2 & block_order_hi == 2 ~ `1_hi`,
#                              tone_order == 2 &  block_order_hd == 2 ~ `1_hd`,
#                              tone_order == 2 &  block_order_hi == 2 ~ `1_hi`,
#                                .default = NA)) |>
#   mutate(block_3 = case_when(tone_order == 1 & block_order_hi == 2 ~ `1_hi`,
#                              tone_order == 1 &  block_order_hd == 2 ~ `1_hd`,
#                              tone_order == 1 &  block_order_hi == 2 ~ `1_hi`,
#                              tone_order == 2 & block_order_hi == 3 ~ `1_hi`,
#                              tone_order == 2 & block_order_hd == 3 ~ `1_hd`,
#                              tone_order == 2 & block_order_hi == 3 ~ `1_hi`,
#                                .default = NA)) |>
#   mutate(block_4 = case_when(tone_order == 1 & block_order_hi == 3 ~ `1_hi`,
#                                tone_order == 1 & block_order_hd == 3 ~ `1_hd`,
#                                tone_order == 1 & block_order_hi == 3 ~ `1_hi`,
#                                tone_order == 2 ~ tone,
#                                .default = NA)) |>
#   
#   glimpse()
# 
# survey_2 <- block_order |>
#   filter(survey_version == 2) |>
#   select(-c(starts_with(c("1", "3", "4"))))
# 
# survey_3 <- block_order |>
#   filter(survey_version == 3) |>
#   select(-c(starts_with(c("1", "2", "4"))))
# 
# survey_4 <- block_order |>
#   filter(survey_version == 4) |>
#   select(-c(starts_with(c("1", "2", "3"))))
# 
# 
# block_order <- block_order |> 
#   rowwise() |>
#   mutate(block_1_timing = if_else(tone_order == 1, tone, if_else(, ,NA))) |>
#   mutate(block_4_timing = if_else(tone_order == 2, tone, NA)) |>
#   mutate(blc)
#   glimpse()
# 
# tone_first_order = block_order |> 
#   filter(tone_order == 1 & !is.na(survey_version)) |>
#   mutate(hi_block = if_else(!is.na(block_order_hi), str_c(survey_version, "_", block_order_hi), NA),
#          hd_block = if_else(!is.na(block_order_hd), str_c(survey_version, "_", block_order_hd), NA),
#          li_block = if_else(!is.na(block_order_li), str_c(survey_version, "_", block_order_li), NA)) |>
#   mutate(block_4_timing = if_else())
# 
# 
#   
# block_order |> select(response_id, tone_order, survey_version, block_order_hi, block_order_hd, block_order_li) |> View()
# 
# block_order |> select(response_id, tone_order, survey_version, block_order_hi, block_order_hd, block_order_li) |> 
#   mutate()
```



Update the flow variable
```{r}

```



Filter out exceptionally long durations and graph distributions, mean, median, and threshold
```{r}
#just timing, to graph. Remove outliers under 100wpm reading speed (beginning reader level)
panel_timing <- panel_integrity |>
  select(-contains("attention")) |> 
  mutate(tone = if_else(tone > timing$max_100[timing$block == "tone"], NA, tone),
         `1_hi` = if_else(`1_hi` > timing$max_100[timing$block == "1_hi"], NA, `1_hi`),
         `1_hd` = if_else(`1_hd` > timing$max_100[timing$block == "1_hd"], NA, `1_hd`),
         `1_li` = if_else(`1_li` > timing$max_100[timing$block == "1_li"], NA, `1_li`),
         `2_hi` = if_else(`2_hi` > timing$max_100[timing$block == "2_hi"], NA, `2_hi`),
         `2_hd` = if_else(`2_hd` > timing$max_100[timing$block == "2_hd"], NA, `2_hd`),
         `2_li` = if_else(`2_li` > timing$max_100[timing$block == "2_li"], NA, `2_li`),
         `3_hi` = if_else(`3_hi` > timing$max_100[timing$block == "3_hi"], NA, `3_hi`),
         `3_hd` = if_else(`3_hd` > timing$max_100[timing$block == "3_hd"], NA, `3_hd`),
         `3_li` = if_else(`3_li` > timing$max_100[timing$block == "3_li"], NA, `3_li`),
         `4_hi` = if_else(`4_hi` > timing$max_100[timing$block == "4_hi"], NA, `4_hi`),
         `4_hd` = if_else(`4_hd` > timing$max_100[timing$block == "4_hd"], NA, `4_hd`),
         `4_li` = if_else(`4_li` > timing$max_100[timing$block == "4_li"], NA, `4_li`), )|>
  glimpse()

skimr::skim(panel_timing)

timing_checks2 <- panel_timing |> 
  skimr::skim() |>
  select(block=skim_variable, skim_type, complete_rate, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  select(-skim_type) |>
  full_join(timing) |>
  mutate() |>
  glimpse()
```

Generate the plots
```{r}
ptone <- ggplot(panel_timing, aes(tone))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "tone"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "tone"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "tone"], linetype = 1, color = "red")
p_1_hi <- ggplot(panel_timing, aes(`1_hi`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "1_hi"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "1_hi"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "1_hi"], linetype = 1, color = "red")
p_1_hd <- ggplot(panel_timing, aes(`1_hd`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "1_hd"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "1_hd"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "1_hd"], linetype = 1, color = "red")
p_1_li <- ggplot(panel_timing, aes(`1_li`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "1_li"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "1_li"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "1_li"], linetype = 1, color = "red")
p_2_hi <- ggplot(panel_timing, aes(`2_hi`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "2_hi"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "2_hi"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "2_hi"], linetype = 1, color = "red")
p_2_hd <- ggplot(panel_timing, aes(`2_hd`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "2_hd"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "2_hd"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "2_hd"], linetype = 1, color = "red")
p_2_li <- ggplot(panel_timing, aes(`2_li`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "2_li"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "2_li"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "2_li"], linetype = 1, color = "red")
p_3_hi <- ggplot(panel_timing, aes(`3_hi`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "3_hi"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "3_hi"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "3_hi"], linetype = 1, color = "red")
p_3_hd <- ggplot(panel_timing, aes(`3_hd`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "3_hd"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "3_hd"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "3_hd"], linetype = 1, color = "red")
p_3_li <- ggplot(panel_timing, aes(`3_li`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "3_li"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "3_li"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "3_li"], linetype = 1, color = "red")
p_4_hi <- ggplot(panel_timing, aes(`4_hi`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "4_hi"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "4_hi"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "4_hi"], linetype = 1, color = "red")
p_4_hd <- ggplot(panel_timing, aes(`4_hd`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "4_hd"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "4_hd"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "4_hd"], linetype = 1, color = "red")
p_4_li <- ggplot(panel_timing, aes(`4_li`))+geom_density() + 
 geom_vline(xintercept = timing_checks2$mean[timing_checks2$block == "4_li"], linetype = 1, color = "green") +
 geom_vline(xintercept = timing_checks2$median[timing_checks2$block == "4_li"], linetype = 1, color = "blue") +
 geom_vline(xintercept = timing_checks2$threshold[timing_checks2$block == "4_li"], linetype = 1, color = "red")
```

Display in a grid
```{r}
gridExtra::grid.arrange(p_1_hi,
                        p_1_hd,
                        p_1_li,
                        p_2_hi,
                        p_2_hd,
                        p_2_li,
                        p_3_hi,
                        p_3_hd,
                        p_3_li,
                        p_4_hi,
                        p_4_hd,
                        p_4_li,
                        ptone, ncol = 3)

```



# Cleaning the dataset

Using what we found above, filter out responses that were ineligible

Note: if preferred, you could do this step by step in the EDA above

```{r}
panel_clean <- panel_export |>
  filter(q_chl == "anonymous") |> #filter out previews
  filter(finished) |> # keep only finished
  filter(progress == 100) |> # eliminate people not at 100% complete, in case that's different
  filter(q_recaptcha_score > .5) |> # keep only captcha score > .5
  filter(eligible_health == "eligible") |> #remove people who failed the health survey
  filter(audit_score > 7) |> # remove people who failed the AUDIT
  filter(consent_agree == "I consent to participate and wish to proceed to the survey.") |> # only those who consented to survey
  filter(is.na(q_duplicate_respondent)) |> # remove duplicate respondent field
  inner_join(panel_attention, by = "response_id") |> # keep only those who passed attention check
  filter(attention_check == "Strongly Disagree") |>
  filter()

# write_csv(panel_clean, file.path(path_processed, "panel_clean.csv"))
```

Colin: finish filtering out ineligible- you might be able to do this more simply by filtering to is.na(term)

Once the dataset is clean you can set up the code to do basic EDA on our variables of interest - ie, does tone/style survey preference match the message ratings. 



## API version

Get survey by API & save out to data_raw (for now)
For now, must be raw=TRUE so no columns are stripped

```{r}
# panel_api <- tidy_qualtrics("panel", token_qualtrics, raw=TRUE) |>
#   janitor::clean_names("snake") |>
#   # filter(is.na(practice)) |>
#   select(-c(ip_address, recipient_last_name:external_data_reference, description, intro_1, audit_inst, intro_context, intro_tone, status,location_latitude:location_accuracy)) |>
#   glimpse()
```


```{r}
# write_csv(panel, "W:/irb/optimize/panel/change_2026_01/wpm/test_responses.csv")

```



# Prelaunch
Verify new question labels match style/tone combo
```{r}
# 
# new_q_labels <- readxl::read_xlsx(file.path("W:/irb/optimize/panel/change_2026_01/wpm/timing calcs.xlsx"), sheet="question_by_tone") |>
#   arrange(survey, user_index, q_number) |>
#   select(-c(`...9`,`...10`)) |>
#   glimpse()
# 
# panel_data_raw <- read_csv(file.path("W:/irb/optimize/panel/change_2026_01/wpm/panel_study_messages_combined_January+23,+2026_21.32.csv")) |> 
#   head(1) |>
#   select(contains(c("_hi_", "_hd_", "_li_"))) |>
#   select(-contains(c("timing", "attention"))) |>
#   mutate(across(everything(), ~ str_remove_all(.x, "- I found this message to be helpful."))) |>
#   mutate(across(everything(), ~ str_remove_all(.x, "\\\""))) |>
#   mutate(across(everything(), ~ str_trim(.x, "both"))) |>
#   pivot_longer(everything()) |>
#   rename(online_q_label = name, generated_message = value) |>
#   glimpse()
# 
# 
# full_join(new_q_labels, panel_data_raw) |> 
#   mutate(match = str_detect(online_q_label, new_q_label)) |>
#   View()

```

