---
title: "Panel EDA"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false

---

The purpose of this EDA to decide if there's anything WE need to change so qualtrics can launch again, or anything we need to tell qualtrics to change:


* CAPTCHA fails
* Healthy screen fails
* AUDIT fails 
* Attention check fails 
* Timing check fails 
* Exceptionally long duration surveys (since these are skewing the mean/median which we need to evaluate our timing checks)


## Set up

```{r setup, warning=FALSE}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/download_qualtrics.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")

#source function file
# source("functions/fun_opt.R")

path_qualtrics <- format_path("optimize/data_raw/qualtrics")
path_panel <- format_path("optimize/data_raw/panel")
path_processed <- format_path("optimize/data_processed")
path_credentials <- format_path("other")
```


 Get credentials
```{r}
token_qualtrics <- 
  get_credentials("qualtrics", file.path(path_credentials, "credentials.csv")) |>
  pull(token)
```

Looks like I'm not getting all responses via API - check the exported version
```{r}
panel_export_raw <- read_csv(tibble(path = list.files(path_panel, pattern = "panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
  mutate(across(everything(), .fns = parse_guess)) |> #read_csv failed to correctly guess coltypes due to the two extra character headers, this re-guesses
  janitor::clean_names("snake") |>
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  glimpse()
```

However the randomizer variables seem to only be available through API? 

Get them and add back into the raw dataframe
```{r}
# source("../proj_optimize/functions/fun_opt.R")
# FL_99 = tone/message randomizer
    # FL_146 = tone survey group
    # FL_98 = message survey group
# FL_12 = survey version randomizer
    # 81, 82, 83, 84 are surveys 1-4
# Survey 1 randomizer: ro_br_fl_85
    # 86,87,88 are hi, hd, li
# Survey 2 randomizer:  ro_br_fl_23 
    # 70,71,72 are hi, hd, li
# Survey 3 randomizer: ro_br_fl_35 
    # 59,60,61 are hi, hd, li 
# Survey 4 randomizer: ro_br_fl_47 
    # 48, 49. 50 are hi, hd, li

# Add variables to make it clearer what order the survey elements were presented in
panel_api <- download_qualtrics(survey_id = "SV_dbAKSR75ATWSo2q", api_token = token_qualtrics,
                             display_progress = FALSE) |>
  janitor::clean_names("snake")  |> 
  select(response_id, starts_with("ro_"), starts_with("block_order"))


randomizer_vars <- panel_api |>
  rename(tone_message_ro = ro_br_fl_99,
         survey_version_ro = ro_br_fl_12,
         survey1_block_ro = ro_br_fl_85,
         survey2_block_ro = ro_br_fl_23,
         survey3_block_ro = ro_br_fl_35,
         survey4_block_ro = ro_br_fl_47) |>
  mutate(tone_message_ro = if_else(tone_message_ro == "FL_146|FL_98", "tone first", "messages first")) |>
  mutate(survey_version_ro = case_when(survey_version_ro == "FL_81" ~ 1,
                                       survey_version_ro == "FL_82" ~ 2,
                                       survey_version_ro == "FL_83" ~ 3,
                                       survey_version_ro == "FL_84" ~ 4)) |>
  mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_86|FL_70|FL_59|FL_48",
                                                                        replacement = "hi"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_87|FL_71|FL_60|FL_49",
                                                                        replacement = "hd"))) |> 
    mutate(across(survey1_block_ro:survey4_block_ro, ~ str_replace_all(string = .x,
                                                                        pattern = "FL_88|FL_72|FL_61|FL_50",
                                                                        replacement = "li"))) |> 
   unite(context_order, survey1_block_ro:survey4_block_ro, sep = "") |>  
   mutate(block_1 = case_when(tone_message_ro == "tone first" ~ "tone",
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                             .default = "")) |>
   mutate(block_2= case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 1,2)),
                               tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                             .default = "")) |>
   mutate(block_3 = case_when(tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, 4,5)),
                              tone_message_ro == "messages first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>        
   mutate(block_4 = case_when(tone_message_ro == "messages first" ~ "tone",
                              tone_message_ro == "tone first" ~ str_c(survey_version_ro, "_", str_sub(context_order, -2)),
                             .default = "")) |>  
            glimpse()

# rejoin to main dataframe
panel_export_raw <- panel_export_raw |>
  left_join(randomizer_vars )

```



## Basic cleaning & EDA
```{r}
#remove the leading X and trailing _1 from varnames
panel_export <-  panel_export_raw |>
    rename_with(~ str_replace_all(.x, pattern = "x", replacement ="")) |>
    rename_with(~ str_replace_all(.x, pattern = "_1$", replacement ="")) |>
    rename(id_location_1 = id_location,
           audit_1 = audit,
           block_1 = block)
# 
# panel_complete <- panel_export |> filter(!is.na(id_location_2)) 
# panel_export |> distinct(id_location_1)  #29 distinct + NA, which matches the above
# 
# panel_export |> nrow()

#Finished?
finished <- panel_export |> filter(finished == "TRUE") |> nrow() 
unfinished <- panel_export |> filter(finished == "FALSE") |> nrow() 

table(panel_export$finished) 

skimr::skim(panel_export$finished)

skimr::skim(panel_export$progress) # progress is another way to measure how far through they got
panel_export |> group_by(progress) |> tally()

```
1. With previous downloads, every survey is finished because any termination led to an end of survey block, now there are a few incompletes
2. As of `r today()` there are `r panel_export |> nrow()` responses, `r unfinished` are incomplete, `r finished` are finished
3. Of the incompletes, progress varies between 1% and 16%. 

To improve the EDA as we go along I'm going to remove responses that shouldn't be kept, as we find them.
```{r}
# remove incomplete submissions
panel_export <- panel_export |> filter(finished == "TRUE") 

```


### Previews
```{r}
panel_export$q_chl |> table() #distinguishes between preview surveys and regular - we need to exclude the previews

#remove previews
panel_export <- panel_export |> 
  filter(q_chl != "preview") 
```

### Duplicate responses
```{r}
panel_export$q_duplicate_respondent |> table()

```
* `r panel_export |> filter(q_duplicate_respondent) |> nrow()` duplicate responses - I'll remove these for now, but qualtrics will have to confirm that one of any duplicate was not retained

Filter those out
```{r}
panel_export <- panel_export |> 
  filter(is.na(q_duplicate_respondent))
```


Start a tibble to track participant flow now that we've removed the most basic non-real responses
```{r}
flow <- tibble(total_submissions = nrow(panel_export)) |> print()
```


### Recaptcha score
```{r}
panel_export$q_recaptcha_score |> table() 

panel_export |> skimr::skim(q_recaptcha_score)

#how many of those still finish the survey?
panel_export |> filter(is.na(q_recaptcha_score)) |> filter(!is.na(id_location_2)) # One!!

#how far did the others get? Use the qualtrics termination variable
panel_export |> filter(is.na(q_recaptcha_score)) |> select(term) |> table()

#How many passed captcha
panel_export |> filter(q_recaptcha_score >= .5) |> nrow() / nrow(panel_export)

# filter out fails under .5 
panel_export <- panel_export |> 
  filter(q_recaptcha_score >= .5) 
                                    
```
1. 73 of q_recaptcha score are NA. What do we do with these?
   * Of those, only one finished the survey. 
2. ~87% of recaptcha scores are over .5; 90% are .5 and over. See [this article](https://pmc.ncbi.nlm.nih.gov/articles/PMC10818231/) for interpretation:    
   * Q_RecaptchaScore returns a score between 0.0 and 1.0 that Qualtrics records as part of the survey response.  Recommended 0.5 score as the threshold for fraud, where a score under 0.5 is deemed likely to be a bot.

Update flow
```{r}
flow <- flow |>
  mutate(passed_captcha = nrow(panel_export)) |> print()
```



### Qualtrics quality variables. 
These will be important but are all NA right now
```{r}
panel_export$q_quality_score |> table()
panel_export$q_ballot_box_stuffing |> table()
panel_export$q_quality_timestamp |> table()

```

### More qualtrics variables
These do not seem relevant to us, disregard for now
```{r}
#| echo: false
#| evaluate: false

panel_export$opp |> table()  # seems to be the name of our study in their records
panel_export$q_url |> table() |> head(5) # (long output truncated) this seems to be the actual URLs used - guessing it sets many of the following values
panel_export$qpmid  |> table() # qualtrics panel ID - probably their internal number for our study
panel_export |> group_by(vendor) |> tally() #Kantar is a market research company - maybe who they are using to sample for us since NA for most

## These I can't guess at the meanings
panel_export$svid |> table()
panel_export$kid |> table() |> head(5) #  (long output truncated) 
panel_export$tg |> table()
panel_export$gc |> table()
panel_export$project_token_a |> table()
panel_export$project_token_b  |> table()
panel_export$supplier_id |> table()
panel_export$os_api_transaction_id|> table() |> head(5)  #  (long output truncated) 
panel_export$ps |> table()
panel_export$project_token |> table()

```

## EDA - screening surveys

### Health Screener
```{r}
screening <- panel_export |> 
  select(response_id, term, starts_with(c("health", "audit"))) |>
  mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |> 
  glimpse()

screening |> group_by(eligible_health) |> tally()
screening |> group_by(eligible_audit) |> tally()

# let's go a little deeper and see how people filter out at each level
screening |> group_by(all_no) |> tally()
screening |> filter(term == "no_Selected") |> nrow()
screening |> filter(all_no) |> pull(term)

screening |> group_by(eligible_health) |> tally()
screening |> filter(term == "not_alcoholic" | term == "no_Selected") |> nrow()
screening |> filter(eligible_health == "eligible") |> group_by(term) |> tally()


```
* There is a discrepancy between the number of people who selected all No's on the health screener, by our count and by qualtrics' count. They counted seven of these people under "not_alcoholic"
* However, our total counts agree on who failed the health screener.
* Per [NIAAA](https://www.niaaa.nih.gov/alcohols-effects-health/alcohol-topics/alcohol-facts-and-statistics/alcohol-use-disorder-aud-united-states-age-groups-and-demographic-characteristics), 21.7% over 18 in the US reported binge drinking in the past month. We're looking at `r scales::percent(nrow(screening |> filter(eligible_health == "eligible"))/nrow(screening))` passing the health screener so that's still a little high as we discussed.

Add the screening eligiblity variables back into the main dataframe, for cleaning later, and remove those who failed the health screener
```{r}
panel_export <- panel_export |>
mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |> 
  filter(eligible_health == "eligible")

```

Update flow
```{r}
flow <- flow |>
  mutate(passed_health_screen = nrow(panel_export)) |> print()
```

### AUDIT Screener
```{r}
panel_audit <- panel_export |>
  select(response_id, starts_with("audit"), eligible_audit) |>
  glimpse()

panel_audit |> group_by(eligible_audit) |> tally()

#stats on audit score by eligibility
skim_audit <- panel_audit |> group_by(eligible_audit) |> skimr::skim(audit_score) |>
  select(eligible_audit, skim_type, complete_rate, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  ungroup() 

panel_audit |> group_by(audit_1) |> tally()


#how many people answering "Never" on audit_1 ended up eligible?
panel_audit |>
  filter(audit_1 == "Never") |>
  group_by(audit_9, audit_10) |>
  tally()

# look at people with audit scores of 40

panel_export |> filter(audit_score == 40) |> group_by(term) |> tally()
panel_export |> filter(audit_score >= 30) |> group_by(term) |> tally()

```
1. 361 people passed the audit
2. Of the 37 people who never drank per audit_1, only one was eligible
3. Only 1 person got a 40 on the audit, and they screened out for a different reason. Of 48 people who got over 30 on the audit, 4 finished the survey.

Graph audit scores
```{r}
#| echo: false
#| fig-asp: 1
#| out-width: 100%
#| fig-width: 10


panel_audit |>
  ggplot(aes(x = audit_score, fill = eligible_audit)) +
  ggtitle("AUDIT scores, by eligiblity, with means") +
  geom_histogram(alpha=0.5, position="identity", binwidth = 4) +
  geom_vline(xintercept = skim_audit$mean[skim_audit$eligible_audit == "eligible"], linetype = 1, color = "red") +
  geom_vline(xintercept = skim_audit$mean[skim_audit$eligible_audit == "ineligible"], linetype = 1, color = "blue") 
```

Filter out AUDIT ineligible and update flow
```{r}
panel_export <- panel_export |> 
  filter(eligible_audit == "eligible")

flow <- flow |> 
  mutate(passed_audit = nrow(panel_export)) |> print()
```

### Consent
* 3 opted not to consent - Filter out and update flow
```{r}
panel_export |> filter(term == "consent") 
panel_export |> group_by(consent_agree) |> tally()

panel_export <- panel_export |> 
  filter(consent_agree != "I wish to exit the survey without providing consent.")

flow <- flow |> 
  mutate(consented = nrow(panel_export)) |> print()
```


## EDA - our data integrity variables

First look at the remaining qualtrics termination reasons
```{r}
panel_export |> group_by(term) |> tally()
```

1. `r panel_export |> group_by(term) |> tally() |> filter(str_detect(term, "survey")) |> pull(n) |> sum()` failed either the attention check OR the timing variable in one of the 4 message surveys
2. 44 failed the speed check in the tone survey
3. 54 are NA, meaning not terminated for any other reason

We won't do anything with this yet, but will instead look in more detail at our own variables.


We want to look at drop outs PER BLOCK on timing & attention checks.


```{r}
#| echo: false

#get timing thresholds
timing <- tibble(block = c(
"tone", 
"1_hi", "1_hd", "1_li",
"2_hi", "2_hd", "2_li", 
"3_hi", "3_hd", "3_li", 
"4_hi", "4_hd", "4_li"),
threshold = c(
59,
101, 104, 94,
102, 104, 98,
102, 106, 98,
100, 105, 99),
max_100 = c(
235,
405, 417, 375,
406, 414, 393,
410, 422, 394,
400, 419, 397))
```

Pull our attention and timing variables
```{r}
panel_integrity <- panel_export |>
  select(response_id, contains((c("last_click","attention"))), starts_with("block_order"), tone_order, survey_order, survey_version, block_1:block_4) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_last_click", replacement ="")) |>
  glimpse()
```

### Block 1 fails
Timing only
```{r}
block1 <- panel_integrity |>
  rowwise() |>
  mutate(block_1_timing = panel_integrity |> 
           select(ends_with(block_1)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_1_threshold = if_else(is.na(block_1), NA, timing$threshold[timing$block == block_1])) |> 
  mutate(block1_timing_fail = block_1_timing < block_1_threshold) |>
  glimpse()

block1 |> group_by(block_1, block1_timing_fail) |> 
  summarise(n = n()) |>
  mutate(prop_failed = scales::percent(n / sum(n))) |> 
  filter(block1_timing_fail == TRUE) |>
  select(block_1, prop_failed)


block1 |> group_by(block1_timing_fail) |> tally()

```
There's considerable variation between block in the percent of people who failed the block 1 timing check.
* tone as block 1 had the lowest amount of fails
* Survey 3, low-increasig had the highest
* Overall of `r flow$consented` consented, `r block1 |> filter(!block1_timing_fail) |> nrow()` (`r scales::percent(block1 |> filter(!block1_timing_fail) |> nrow() / flow$consented)`) passed block 1


Filter out people who failed at block1 and update flow
```{r}
panel_export <- panel_export |>
  filter(response_id %in% (block1 |> filter(!block1_timing_fail) |> pull(response_id)))

flow <- flow |>
  mutate(passed_block1 = nrow(panel_export)) |> glimpse()
  
```


### Block 2 fails
This block had both timing and attention for at least some people
```{r}
block2 <- panel_integrity |>
  filter(response_id %in% panel_export$response_id) |>
  rowwise() |>
  mutate(block_2_timing = panel_integrity |> 
           select(ends_with(block_2)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_2_threshold = if_else(is.na(block_2), NA, timing$threshold[timing$block == block_2])) |> 
  mutate(block2_timing_fail = block_2_timing < block_2_threshold) |>
  mutate(block_2_attention = panel_integrity |> 
           select(starts_with(block_2) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

#timing:
block2 |> group_by(block_2, block2_timing_fail) |> 
  summarise(n = n()) |>
  mutate(prop_failed = scales::percent(n / sum(n))) |> 
  filter(block2_timing_fail == TRUE) |>
  select(block_2, prop_failed)

#attention:
block2 |> 
  filter(!is.na(block_2_attention)) |> nrow()

block2 |> 
  filter(!is.na(block_2_attention)) |>
  filter(block_2_attention != "Strongly Disagree") |> nrow()

#who failed both?
block2 |> filter(block_2_attention != "Strongly Disagree" & block2_timing_fail) |> nrow()

```
* Again there is variability between surveys and contexts for how many people failed the timing check in their second block.
   * In total, `r block2 |> filter(block2_timing_fail) |> nrow()` or `r scales::percent(block2 |> filter(block2_timing_fail) |> nrow() / block2 |> nrow())` failed the timing check 
* Only `r block2 |> filter(!is.na(block_2_attention)) |> nrow()` people had an attention check in block 2 (those for whom the tone survey came second)
   * `r block2 |> filter(!is.na(block_2_attention)) |> filter(block_2_attention != "Strongly Disagree") |> nrow()` of those (`r scales:: percent(block2 |> filter(!is.na(block_2_attention)) |> filter(block_2_attention != "Strongly Disagree") |> nrow()/block2 |> filter(!is.na(block_2_attention)) |> nrow())`) failed the attention check
   * Only `r block2 |> filter(block_2_attention != "Strongly Disagree" & block2_timing_fail) |> nrow()` failed both   


Filter out people who failed at block2 and update flow
```{r}
panel_export <- panel_export |>
  filter(response_id %in% (block2 |> filter(is.na(block_2_attention) | block_2_attention == "Strongly Disagree") |> pull(response_id)))


flow <- flow |>
  mutate(passed_block2_attention = nrow(panel_export)) |> glimpse()

panel_export <- panel_export |>
  filter(response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id))) 

flow <- flow |>
  mutate(passed_block2_timing = nrow(panel_export)) |> glimpse()
  


```


### Block 3 fails
This block had both timing and attention for at least some people
```{r}
block3 <- panel_integrity |>
  filter(response_id %in% panel_export$response_id) |>
  rowwise() |>
  mutate(block_3_timing = panel_integrity |> 
           select(ends_with(block_3)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_3_threshold = if_else(is.na(block_3), NA, timing$threshold[timing$block == block_3])) |> 
  mutate(block3_timing_fail = block_3_timing < block_3_threshold) |>
  mutate(block_3_attention = panel_integrity |> 
           select(starts_with(block_3) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  glimpse()

#timing:
block3 |> group_by(block_3, block3_timing_fail) |> 
  summarise(n = n()) |>
  mutate(prop_failed = scales::percent(n / sum(n))) |> 
  filter(block3_timing_fail == TRUE) |>
  select(block_3, prop_failed)

#attention:
block3 |> 
  filter(!is.na(block_3_attention)) |> nrow()


block3 |> 
  filter(!is.na(block_3_attention)) |>
  filter(block_3_attention != "Strongly Disagree") |> nrow()

```
* Proportions failing the timing check in the third block continue to dwindle.
   * In total, `r block3 |> filter(block3_timing_fail) |> nrow()` or `r scales::percent(block3 |> filter(block3_timing_fail) |> nrow() / block3 |> nrow())` failed the timing check 
* `r block3 |> filter(!is.na(block_3_attention)) |> nrow()` people had an attention check in block 3 (those for whom the tone survey came first)
   * `r block3 |> filter(!is.na(block_3_attention)) |> filter(block_3_attention != "Strongly Disagree") |> nrow()` of those (`r scales:: percent(block3 |> filter(!is.na(block_3_attention)) |> filter(block_3_attention != "Strongly Disagree") |> nrow()/block3 |> filter(!is.na(block_3_attention)) |> nrow())`) failed the attention check
   * `r block3 |> filter(block_3_attention != "Strongly Disagree" & block3_timing_fail) |> nrow()` failed both   



Filter out people who failed at block3 and update flow
```{r}
panel_export <- panel_export |>
  filter(response_id %in% (block3 |> filter(is.na(block_3_attention) | block_3_attention == "Strongly Disagree") |> pull(response_id)))


flow <- flow |>
  mutate(passed_block3_attention = nrow(panel_export)) |> glimpse()

panel_export <- panel_export |>
  filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id))) 

flow <- flow |>
  mutate(passed_block3_timing = nrow(panel_export)) |> glimpse()
```


### Block 4 fails
This block had only timing checks
```{r}
block4 <- panel_integrity |>
  filter(response_id %in% panel_export$response_id) |>
  rowwise() |>
  mutate(block_4_timing = panel_integrity |> 
           select(ends_with(block_4)) |> 
           filter(response_id == panel_integrity$response_id) |> pull() ) |> 
  mutate(block_4_threshold = if_else(is.na(block_4), NA, timing$threshold[timing$block == block_4])) |> 
  mutate(block4_timing_fail = block_4_timing < block_4_threshold) |>
  glimpse()

#timing:
block4 |> group_by(block_4, block4_timing_fail) |> 
  summarise(n = n()) |>
  mutate(prop_failed = scales::percent(n / sum(n))) |> 
  filter(block4_timing_fail == TRUE) |>
  select(block_4, prop_failed)


```
* Proportions failing the timing check in the third block continue to dwindle.
   * In total, `r block3 |> filter(block3_timing_fail) |> nrow()` or `r scales::percent(block3 |> filter(block3_timing_fail) |> nrow() / block3 |> nrow())` failed the timing check 

Filter out people who failed at block 4 and update flow. This should be the final clean sample!
```{r}

panel_export <- panel_export |>
  filter(response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id))) 

flow <- flow |>
  mutate(passed_block4 = nrow(panel_export)) |> glimpse()
  


```


### Check our final sample against qualtric's
```{r}
panel_export_raw |> group_by(term) |> tally()

panel_export |> nrow()

qualtrics_final <- panel_export_raw |> filter(is.na(term)) 
```

* qualtrics termination variable says 69 people passed. Why the discrepancy?

```{r}
#are all finished?
qualtrics_final |> filter(!finished) |> nrow()

# any previews?
qualtrics_final |>filter(q_chl == "preview") 

```
* No previews, but they didnt mark unfinished as having a termination reason. That's fine, take them out.

Next check the people who they say finished who weren't in our final sample
```{r}
qualtrics_final <- qualtrics_final |> filter(finished)

q_why <- qualtrics_final |> filter(!(response_id %in% panel_export$response_id)) |> glimpse()

screening |> filter(response_id %in% q_why$response_id)

q_why$term
q_why$finished
q_why$q_recaptcha_score

```
* All 6 were removed by us before the screening checks
* One had a captcha score of 1, one was NA

### Location checks

Are all the locations in the US?
```{r}

panel_export |>
  select(response_id, lat = location_latitude, lon = location_longitude) |>
  filter(!is.na(lat) & !is.na(lon)) |>
  plot_places() 


```

Does the city/state that they reported match their current lat/long?

```{r}
#Fix a misspelling first
panel_clean$id_location_1[panel_clean$id_location_1 == "Tuscon"] <-  "Tucson"

# need tidygeocoder package this does take a while
panel_location <- panel_clean |> 
  select(response_id, actual_latitude = location_latitude, actual_longitude = location_longitude, 
         ip = ip_address, grocery_name = q12_grocer,
         grocery_location = q12_grocer_2, reported_city = id_location_1, reported_state = id_location_2) |>
  tidygeocoder::geocode(city = reported_city, state = reported_state, method = "osm") |>
  rename(reported_city_latitude = lat, reported_city_longitude = long) |>
  mutate(euclidian_dist = sqrt((actual_latitude - reported_city_latitude)^2 + (actual_longitude - reported_city_longitude)^2))
```

Plot euclidian distances in box and whisker plot

```{r}
ggplot(panel_location, aes(x = euclidian_dist)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Euclidean Distance",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Euclidean Distance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Let's do this by miles since lat/long are not intuitive units of measurement for people
Per Britannica, "the length of a degree of arc of latitude is approximately 111 km (69 miles), varying, because of the nonuniformity of Earth’s curvature
The distance per degree of longitude at the Equator is about 111.32 km (69.18 miles) and at the poles, 0."
Assuming the US is somewhere between the equator and the north pole, we can use the midpoint for longitude, which is 34 (surprisingly, changing this from 69 did not change much). 
```{r}
panel_location <- panel_location |>
  mutate(
    # Calculate distance in miles using 34 miles per degree for longitude and 69 for latitude
    lat_diff_miles = (actual_latitude - reported_city_latitude) * 69,
    lon_diff_miles = (actual_longitude - reported_city_longitude) * 34 * cos(mean(actual_latitude, na.rm = TRUE) * pi / 180),
    euclidian_dist_miles = sqrt(lat_diff_miles^2 + lon_diff_miles^2)
  )

ggplot(panel_location, aes(x = euclidian_dist_miles)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Distance in Miles",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Distance (Miles)") +
  theme_minimal()
```

## EDA: Randomizers

Tone survey vs message survey randomizer
```{r}
panel_clean |> group_by(tone_order) |> tally()
```


Survey randomizer
```{r}
panel_clean |> group_by(survey_version) |> tally()
```


Block order randomizer
```{r}
panel_clean |> group_by(block_order_hi, block_order_hd, block_order_li) |> tally()
```
