---
title: "Panel EDA"
format: 
  html:
    page-layout: full
    self-contained: true
execute: 
  warning: false
---

The purpose of this EDA to decide if there's anything WE need to change so qualtrics can launch again, or anything we need to tell qualtrics to change:


* CAPTCHA fails
* Healthy screen fails
* AUDIT fails 
* Attention check fails 
* Timing check fails 
* Exceptionally long duration surveys (since these are skewing the mean/median which we need to evaluate our timing checks)


## Set up

```{r setup, warning=FALSE}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse) 

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")

#source function file
# source("functions/fun_opt.R")

path_qualtrics <- format_path("optimize/data_raw/qualtrics")
path_panel <- format_path("optimize/data_raw/panel")
path_processed <- format_path("optimize/data_processed")
path_credentials <- format_path("other")
```


## Get credentials
```{r}
token_qualtrics <- 
  get_credentials("qualtrics", file.path(path_credentials, "credentials.csv")) |>
  pull(token)
```

Looks like I'm not getting all responses via API - check the exported version
```{r}
panel_export_raw <- read_csv(tibble(path = list.files(path_panel, pattern = "panel_2026", full.names = TRUE)) |> mutate(mdate = file.mtime(path)) |> filter(mdate == max(mdate)) |> pull(path)) |>
  tail(-2) |> 
  mutate(across(everything(), .fns = parse_guess)) |> #read_csv failed to correctly guess coltypes due to the two extra character headers, this re-guesses
  janitor::clean_names("snake") |>
  # something happened to the naming with the health survey variables - rename them appropriately
  rename(health_brush = health_floss,
         health_drink = x47280739) |>
  glimpse()
```


Basic EDA
```{r}
#remove the leading X and trailing _1 from varnames
panel_export <-  panel_export_raw |>
    rename_with(~ str_replace_all(.x, pattern = "x", replacement ="")) |>
    rename_with(~ str_replace_all(.x, pattern = "_1$", replacement ="")) |>
    rename(id_location_1 = id_location,
           audit_1 = audit)
# 
# panel_complete <- panel_export |> filter(!is.na(id_location_2)) 
# panel_export |> distinct(id_location_1)  #29 distinct + NA, which matches the above
# 
# panel_export |> nrow()

#Finished?
finished <- panel_export |> filter(finished == "TRUE") |> nrow() 
unfinished <- panel_export |> filter(finished == "FALSE") |> nrow() 

table(panel_export$finished) 

skimr::skim(panel_export$finished)

skimr::skim(panel_export$progress) # progress is another way to measure how far through they got
panel_export |> group_by(progress) |> tally()

```
1. With previous downloads, every survey is finished because any termination led to an end of survey block, now there are a few incompletes
2. As of `r today()` there are `r panel_export |> nrow()` responses, `r unfinished` are incomplete, `r finished` are finished
3. Of the incompletes, progress varies between 1% and 16%. 

To improve the EDA as we go along I'm going to remove responses that shouldn't be kept, as we find them.
```{r}
# remove incomplete submissions
panel_export <- panel_export |> filter(finished == "TRUE") 

```

## EDA - qualtrics variables

These variables were all added by Qualtrics before launch. What do they mean? What are their values? Which ones do we need to use to filter people out of a "clean" dataset
```{r}
qualtrics_vars <- panel_export |> select(response_id, opp:project_token, starts_with("q_")) |> glimpse()

qualtrics_vars |> skimr::skim()

panel_export$term |> table() # seems to have a rule-out value for everyone who did not complete, is NA for those who did complete

```

Previews
```{r}

panel_export$q_chl |> table() #distinguishes between preview surveys and regular - we need to exclude the previews

#remove previews
panel_export <- panel_export |> 
  filter(q_chl != "preview") 
```

Duplicate responses
```{r}
panel_export$q_duplicate_respondent |> table()

panel_export <- panel_export |> 
  filter(is.na(q_duplicate_respondent))
```
* 41 duplicate responses - I'll remove these for now, but qualtrics will have to confirm that one of any duplicate was not retained

Start a tibble to track participant flow now that we've removed non-real responses
```{r}
flow <- tibble(total_submissions = nrow(panel_export))
```


Recaptcha score
```{r}
panel_export$q_recaptcha_score |> table() 

panel_export |> skimr::skim(q_recaptcha_score)

#how many of those still finished the survey?
panel_export |> filter(is.na(q_recaptcha_score)) |> filter(!is.na(id_location_2)) # One!!

#how far did the others get? Use the qualtrics termination variable
panel_export |> filter(is.na(q_recaptcha_score)) |> select(term) |> table()

#How many passed captcha
panel_export |> filter(q_recaptcha_score >= .5) |> nrow() / nrow(panel_export)

# filter out fails under .5 
panel_export <- panel_export |> 
  filter(q_recaptcha_score >= .5) 
                                    
```
1. 73 of q_recaptcha score are NA. What do we do with these?
   * Of those, only one finished the survey. 
2. ~87% of recaptcha scores are over .5; 90% are .5 and over. See [this article](https://pmc.ncbi.nlm.nih.gov/articles/PMC10818231/) for interpretation:    
   * Q_RecaptchaScore returns a score between 0.0 and 1.0 that Qualtrics records as part of the survey response.  Recommended 0.5 score as the threshold for fraud, where a score under 0.5 is deemed likely to be a bot.

Update flow
```{r}
flow <- flow |>
  mutate(passed_captcha = nrow(panel_export))
```



Qualtrics quality variables. these will be important but are all NA right now
```{r}
panel_export$q_quality_score |> table()
panel_export$q_ballot_box_stuffing |> table()
panel_export$q_quality_timestamp |> table()

```

More qualtrics variables: These do not seem relevant to us
```{r}
panel_export$opp |> table()  # seems to be the name of our study in their records
panel_export$q_url |> table() |> head(5) # (long output truncated) this seems to be the actual URLs used - guessing it sets many of the following values
panel_export$qpmid  |> table() # qualtrics panel ID - probably their internal number for our study
panel_export |> group_by(vendor) |> tally() #Kantar is a market research company - maybe who they are using to sample for us since NA for most

## These I can't guess at the meanings
panel_export$svid |> table()
panel_export$kid |> table() |> head(5) #  (long output truncated) 
panel_export$tg |> table()
panel_export$gc |> table()
panel_export$project_token_a |> table()
panel_export$project_token_b  |> table()
panel_export$supplier_id |> table()
panel_export$os_api_transaction_id|> table() |> head(5)  #  (long output truncated) 
panel_export$ps |> table()
panel_export$project_token |> table()

```

## EDA - screening surveys

Health Screener
```{r}
screening <- panel_export |> 
  select(response_id, term, starts_with(c("health", "audit"))) |>
  mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |> 
  glimpse()

screening |> group_by(eligible_health) |> tally()
screening |> group_by(eligible_audit) |> tally()

# let's go a little deeper and see how people filter out at each level
screening |> group_by(all_no) |> tally()
screening |> filter(term == "no_Selected") |> nrow()
screening |> filter(all_no) |> pull(term)

screening |> group_by(eligible_health) |> tally()
screening |> filter(term == "not_alcoholic" | term == "no_Selected") |> nrow()
screening |> filter(eligible_health == "eligible") |> group_by(term) |> tally()


```
* There is a discrepancy between the number of people who selected all No's on the health screener, by our count and by qualtrics' count. They counted seven of these people under "not_alcoholic"
* However, our total counts agree on who failed the health screener.
* Per [NIAAA](https://www.niaaa.nih.gov/alcohols-effects-health/alcohol-topics/alcohol-facts-and-statistics/alcohol-use-disorder-aud-united-states-age-groups-and-demographic-characteristics), 21.7% over 18 in the US reported binge drinking in the past month. We're looking at `r scales::percent(nrow(screening |> filter(eligible_health == "eligible"))/nrow(screening))` passing the health screener so that's still a little high as we discussed.

Add the screening eligiblity variables back into the main dataframe, for cleaning later, and remove those who failed the health screener
```{r}
panel_export <- panel_export |>
mutate(all_no = health_food == "No" & health_brush == "No" & health_sleep == "No" & health_drink == "No" & health_water == "No") |>
  mutate(eligible_health = if_else(health_drink == "No" & !all_no, "eligible", "ineligible")) |>
  mutate(eligible_audit = if_else(audit_score > 7, "eligible", "ineligible")) |> 
  filter(eligible_health == "eligible")

```

Update flow
```{r}
flow <- flow |>
  mutate(passed_health_screen = nrow(panel_export))
```

AUDIT Screener
```{r}
panel_audit <- panel_export |>
  select(response_id, starts_with("audit"), eligible_audit) |>
  glimpse()

panel_audit |> group_by(eligible_audit) |> tally()

#stats on audit score by eligibility
skim_audit <- panel_audit |> group_by(eligible_audit) |> skimr::skim(audit_score) |>
  select(eligible_audit, skim_type, complete_rate, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  ungroup() 

panel_audit |> group_by(audit_1) |> tally()


#how many people answering "Never" on audit_1 ended up eligible?
panel_audit |>
  filter(audit_1 == "Never") |>
  group_by(audit_9, audit_10) |>
  tally()

# look at people with audit scores of 40

panel_export |> filter(audit_score == 40) |> group_by(term) |> tally()
panel_export |> filter(audit_score >= 30) |> group_by(term) |> tally()

```
1. 361 people passed the audit
2. Of the 37 people who never drank per audit_1, only one was eligible
3. Only 1 person got a 40 on the audit, and they screened out for a different reason. Of 48 people who got over 30 on the audit, 4 finished the survey.

Graph audit scores
```{r}
#| echo: false
#| fig-asp: 1
#| out-width: 100%
#| fig-width: 10


panel_audit |>
  ggplot(aes(x = audit_score, fill = eligible_audit)) +
  ggtitle("AUDIT scores, by eligiblity, with means") +
  geom_histogram(alpha=0.5, position="identity", binwidth = 4) +
  geom_vline(xintercept = skim_audit$mean[skim_audit$eligible_audit == "eligible"], linetype = 1, color = "red") +
  geom_vline(xintercept = skim_audit$mean[skim_audit$eligible_audit == "ineligible"], linetype = 1, color = "blue") 
```

Filter out AUDIT ineligible and update flow
```{r}
panel_export <- panel_export |> 
  filter(eligible_audit == "eligible")

flow <- flow |> 
  mutate(passed_audit = nrow(panel_export))
```

Consent
```{r}
panel_export |> filter(term == "consent") 
panel_export |> group_by(consent_agree) |> tally()
```

* 3 opted not to consent

Filter out  and update flow
```{r}
panel_export <- panel_export |> 
  filter(consent_agree != "I wish to exit the survey without providing consent.")

flow <- flow |> 
  mutate(consented = nrow(panel_export))
```





#can't look at total duration till we've excluded everyone who dropped out.
# panel_export |> skimr::skim(q_total_duration)  # more info via skim
# panel_export |> skimr::skim(duration_in_seconds) #identical to q_total_duration. This is the default variable, not sure why qualtrics added the other one instead of using this directly




## EDA - our data integrity variables

First look at the remaining qualtrics termination reasons
```{r}
panel_export |> group_by(term) |> tally()
```

1. `r panel_export |> group_by(term) |> tally() |> filter(str_detect(term, "survey")) |> pull(n) |> sum()` failed either the attention check OR the timing variable in one of the 4 message surveys
2. 44 failed the speed check in the tone survey
3. 54 are NA, meaning not terminated for any other reason

We won't do anything with this yet, but will instead look in more detail at our own variables:


First set up a tibble with the actual cutoff thresholds we set for our timing variables
```{r}
#| echo: false

timing <- tibble(block = c(
"tone",
"1_hi",
"1_hd",
"1_li",
"2_hi",
"2_hd",
"2_li",
"3_hi",
"3_hd",
"3_li",
"4_hi",
"4_hd",
"4_li"),
threshold = c(
59,
101,
104,
94,
102,
104,
98,
102,
106,
98,
100,
105,
99),
max_100 = c(
235,
405,
417,
375,
406,
414,
393,
410,
422,
394,
400,
419,
397)
)
```

Pull our attention and timing variables
```{r}
panel_integrity <- panel_export |>
  select(response_id, contains((c("last_click","attention"))), starts_with("block_order"), tone_order) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_last_click", replacement ="")) |>
  glimpse()

panel_integrity |> 
  skimr::skim()


#filter to the vars of interest and join with the timing values
timing_checks <- panel_integrity |> 
  skimr::skim() |>
  select(block=skim_variable, skim_type, complete_rate, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  select(-skim_type) |>
  filter(!str_detect(block, "attention")) |>
  full_join(timing) |>
  mutate() |>
  glimpse()
```

How many people failed the attention checks?
```{r}

# get people who answered the attention check
panel_attention <- panel_integrity |> 
  rowwise() |>
  mutate(
    attention_check = c_across(contains("attention")) |> 
      na.omit() |> 
      unique() |> 
      (\(x) if(length(x) > 1) "Multiple Values" else if(length(x) == 1) x else NA)() # shouldn't happen, coding error
  ) |>
  ungroup() |>
  filter(!is.na(attention_check)) |>
  # recode as factor
  mutate(attention_check = factor(attention_check, 
                                   levels = c("Strongly Agree", "Agree", "Somewhat Agree", 
                                             "Neutral", "Somewhat Disagree", "Disagree", 
                                             "Strongly Disagree", "Multiple Values"))) |>
  select(response_id, attention_check)

# get counts of those who answered the attention check
panel_attention |> count(attention_check)

# get counts of those who failed the attention check
attention_fail <- panel_attention |>
  filter(attention_check != "Strongly Disagree")

cat(nrow(attention_fail))

# get counts of those who passed the attention check
attention_pass <- panel_attention |>
  filter(attention_check == "Strongly Disagree")

cat(nrow(attention_pass))

#% who passed
nrow(attention_pass)/ nrow(panel_integrity) 

# calculate proportion of fails
nrow(attention_fail) / nrow(panel_integrity) 
```
1. Only 78 people out of 358 passed an attention check


* Use the timing_checks dataframe to figure out where the mean/median lie with respect to the threshold. It looks like we're being too aggressive and should raise our thresholds but until we can see how they go together more cleanly it's hard to tell (Done pending final review)

```{r}
timing_summary <- timing_checks |>
  select(block, mean, median, threshold) |>
  mutate(block = str_remove_all(block, "`")) |>
  filter(block != "tone" & !is.na(block) & block != "response_id") |>
  group_by(block) |>
  summarise(mean = mean(mean, na.rm = TRUE),
            median = mean(median, na.rm = TRUE),
            threshold = mean(threshold, na.rm = TRUE),
            .groups = "drop")

total_row <- tibble(block = "Total",
                    mean = sum(timing_summary$mean, na.rm = TRUE),
                    median = sum(timing_summary$median, na.rm = TRUE),
                    threshold = sum(timing_summary$threshold, na.rm = TRUE))

timing_summary <- bind_rows(timing_summary, total_row)

timing_summary |>
  knitr::kable(digits = 1, caption = "Mean, Median, and Threshold Comparison")
```

* for the people that failed the timing checks (especially those in the 2nd or 3rd message block), would we want to preserve them for partial analysis? (I think failing 1 message block is fine)


Update the flow variable -just use the termination variable since it handles all the timing & attention vars

```{r}
flow <- flow |> mutate(passed_time_attention = panel_export |> filter(is.na(term)) |> nrow())
```
* S NOTE: Recalculate this to make sure their use of term is correct.

panel_export |> group_by(term) |> tally()



I think there's an order x block interaction effect with timing, let's look at that
```{r}
block_timing <- panel_integrity |> 
  select(-contains("attention"), -response_id, -contains("block_order")) |> 
  janitor::remove_empty(which = "rows") |> 
  mutate(tone_order = if_else(is.na(tone_order), 2, tone_order))  #if tone order is blank but one of the message timing vars is not, it means tone was 2nd but they were eliminated prior to that

block_timing |>
  group_by(tone_order) |>
  skimr::skim()

overlap_timing <- block_timing |> 
  group_by(tone_order) |>
  skimr::skim() |>
  select(block=skim_variable, skim_type, tone_order, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  select(-skim_type) |>
  full_join(timing) |>
  mutate() |>
  glimpse()

```



# Cleaning the dataset

Using what we found above, filter out responses that were ineligible

Note: if preferred, you could do this step by step in the EDA above

```{r}
panel_clean <- panel_export |>
  filter(q_chl == "anonymous") |> #filter out previews
  filter(finished) |> # keep only finished
  filter(progress == 100) |> # eliminate people not at 100% complete, in case that's different
  filter(q_recaptcha_score > .5) |> # keep only captcha score > .5
  filter(eligible_health == "eligible") |> #remove people who failed the health survey
  filter(audit_score > 7) |> # remove people who failed the AUDIT
  filter(consent_agree == "I consent to participate and wish to proceed to the survey.") |> # only those who consented to survey
  filter(is.na(q_duplicate_respondent)) |> # remove duplicate respondent field
  inner_join(panel_attention, by = "response_id") |> # keep only those who passed attention check
  filter(attention_check == "Strongly Disagree") |>
  filter(is.na(term))

# write_csv(panel_clean, file.path(path_processed, "panel_clean.csv"))
```



Check timing for clean results
```{r}
#| echo: false

 
 
clean_timing <- panel_clean |> 
  select(response_id, contains((c("last_click"))), starts_with("block_order"), tone_order, survey_version) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_last_click", replacement ="")) |>
  pivot_longer(cols = c(`1_hi`,`2_hi`,`3_hi`,`4_hi`), names_to="block_id_hi", values_to = "hi_timing") |>
  pivot_longer(cols = c(`1_hd`,`2_hd`,`3_hd`,`4_hd`), names_to="block_id_hd", values_to = "hd_timing") |>
  pivot_longer(cols = c(`1_li`,`2_li`,`3_li`,`4_li`), names_to="block_id_li", values_to = "li_timing") |>
  select(-c(starts_with("block_id"))) |> 
  filter(!is.na(hi_timing) & !is.na(hd_timing) & !is.na(li_timing) ) |>
  mutate(block_1 = case_when(block_order_hi == 1 ~ hi_timing,
                             block_order_hd == 1 ~ hd_timing,
                             block_order_li == 1 ~ li_timing,
                             .default = NA),
         block_2 = case_when(block_order_hi == 2 ~ hi_timing,
                             block_order_hd == 2 ~ hd_timing,
                             block_order_li == 2 ~ li_timing,
                             .default = NA),
         block_3 = case_when(block_order_hi == 3 ~ hi_timing,
                             block_order_hd == 3 ~ hd_timing,
                             block_order_li == 3 ~ li_timing,
                             .default = NA)) |>
  select(-c(hi_timing, hd_timing,li_timing) ) |>
  glimpse()

#check timing for just this group
clean_timing |> group_by(tone_order) |>skimr::skim()

#there are some very long durations, look in detail
clean_timing |> filter(tone > 300)

clean_timing |> group_by(survey_version) |> tally()


# 
# #3 really long values. lets bring them back to the mean by making them equal to the lowest of that value
# clean_timing <- clean_timing |>
#   mutate(tone = if_else(tone > 600, 624, tone))

clean_timing_skim <- clean_timing |>
  skimr::skim() |>
  select(block=skim_variable, skim_type, mean = numeric.mean, median = numeric.p50, sd = numeric.sd, min = numeric.p0, max = numeric.p100) |> 
  select(-skim_type) |>
  full_join(timing) |>
  mutate() |>
  glimpse()

```

Graph the timing variables by block and tone order
```{r}
#| echo: false

tone_clean <- clean_timing |>
  ggplot(aes(x = tone)) +
  geom_histogram() +
  geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "tone"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "tone"], linetype = 2, color = "darkred") +
   geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "tone"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )

block1_clean <- clean_timing |>
  ggplot(aes(x = block_1)) +
  geom_histogram() +
  geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "block_1"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "block_1"], linetype = 2, color = "darkred") +
  # geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "tone"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )

block_2_clean <- clean_timing |>
  ggplot(aes(x = block_2)) +
  geom_histogram() +
  geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "block_2"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "block_2"], linetype = 2, color = "darkred") +
  # geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "tone"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )

block_3_clean <- clean_timing |>
  ggplot(aes(x = block_3)) +
  geom_histogram() +
  geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "block_3"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "block_3"], linetype = 2, color = "darkred") +
  # geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "tone"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )

hi1_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `1_hi`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "1_hi"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "1_hi"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "1_hi"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


hd1_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `1_hd`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "1_hd"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "1_hd"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "1_hd"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


li1_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `1_li`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "1_li"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "1_li"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "1_li"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )



hi2_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `2_hi`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "2_hi"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "2_hi"], linetype = 2, color = "darkred") +
   geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "2_hi"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


hd2_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `2_hd`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "2_hd"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "2_hd"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "2_hd"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


li2_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `2_li`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "2_li"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "2_li"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "2_li"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )



hi3_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `3_hi`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "3_hi"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "3_hi"], linetype = 2, color = "darkred") +
   geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "3_hi"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


hd3_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `3_hd`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "3_hd"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "3_hd"], linetype = 2, color = "darkred") +
   geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "3_hd"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


li3_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `3_li`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "3_li"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "3_li"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "3_li"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )



hi4_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `4_hi`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "4_hi"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "4_hi"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "4_hi"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


hd4_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `4_hd`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "4_hd"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "4_hd"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "4_hd"], linetype = 1, color = "green") +
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )


li4_clean <- clean_timing |>
  mutate(tone_order = as.factor(tone_order)) |>
  ggplot(aes(x = `4_li`)) +
  geom_histogram() +
    geom_vline(xintercept = clean_timing_skim$mean[clean_timing_skim$block == "4_li"], linetype = 1, color = "red") +
  geom_vline(xintercept = clean_timing_skim$median[clean_timing_skim$block == "4_li"], linetype = 2, color = "darkred") +
  geom_vline(xintercept = clean_timing_skim$threshold[clean_timing_skim$block == "4_li"], linetype = 1, color = "green")+
  theme(axis.text.y=element_blank(),
        axis.ticks.y=element_blank() 
        )
```


```{r}
#| fig-asp: 1
#| out-width: 100%
#| fig-width: 15

gridExtra::grid.arrange(hi1_clean,
                        hd1_clean,
                        li1_clean,
                        hi2_clean,
                        hd2_clean,
                        li2_clean,
                        hi3_clean,
                        hd3_clean,
                        li3_clean,
                        hi4_clean,
                        hd4_clean,
                        li4_clean,
                        tone_clean, ncol = 3)

```





#Location check - are all the locations in the US?
```{r}
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")

panel_clean |>
  select(response_id, lat = location_latitude, lon = location_longitude) |>
  filter(!is.na(lat) & !is.na(lon)) |>
  plot_places() 


```

# location check 2 - does the city/state that they reported match their current lat/long?
one person spelled tucson, arizona wrong (as tuscon). not sure how to handle this.
```{r}
# need tidygeocoder package this does take a while

panel_location <- panel_clean |> 
  select(response_id, actual_latitude = location_latitude, actual_longitude = location_longitude, 
         ip = ip_address, grocery_name = q12_grocer,
         grocery_location = q12_grocer_2, reported_city = id_location_1, reported_state = id_location_2) |>
  tidygeocoder::geocode(city = reported_city, state = reported_state, method = "osm") |>
  rename(reported_city_latitude = lat, reported_city_longitude = long) |>
  mutate(euclidian_dist = sqrt((actual_latitude - reported_city_latitude)^2 + (actual_longitude - reported_city_longitude)^2))
```

plot euclidian distances in box and whisker plot
note that the person who spelled tucson, arizona wrong is not included
```{r}
ggplot(panel_location, aes(x = euclidian_dist)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Euclidean Distance",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Euclidean Distance") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

Let's do this by miles since lat/long are not intuitive units of measurement for people
Per Britannica, "the length of a degree of arc of latitude is approximately 111 km (69 miles), varying, because of the nonuniformity of Earth’s curvature
The distance per degree of longitude at the Equator is about 111.32 km (69.18 miles) and at the poles, 0."
Assuming the US is somewhere between the equator and the north pole, we can use the midpoint for longitude, which is 34 (surprisingly, changing this from 69 did not change much). 
```{r}
panel_location <- panel_location |>
  mutate(
    # Calculate distance in miles using 34 miles per degree for longitude and 69 for latitude
    lat_diff_miles = (actual_latitude - reported_city_latitude) * 69,
    lon_diff_miles = (actual_longitude - reported_city_longitude) * 34 * cos(mean(actual_latitude, na.rm = TRUE) * pi / 180),
    euclidian_dist_miles = sqrt(lat_diff_miles^2 + lon_diff_miles^2)
  )

ggplot(panel_location, aes(x = euclidian_dist_miles)) +
  geom_boxplot(fill = "steelblue", alpha = 0.7) +
  labs(title = "Distribution of Distance in Miles",
       subtitle = "Distance between reported city location and actual GPS coordinates",
       x = "Distance (Miles)") +
  theme_minimal()
```


## API version

Get survey by API & save out to data_raw (for now)
For now, must be raw=TRUE so no columns are stripped

```{r}
# panel_api <- tidy_qualtrics("panel", token_qualtrics, raw=TRUE) |>
#   janitor::clean_names("snake") |>
#   # filter(is.na(practice)) |>
#   select(-c(ip_address, recipient_last_name:external_data_reference, description, intro_1, audit_inst, intro_context, intro_tone, status,location_latitude:location_accuracy)) |>
#   glimpse()
```


```{r}
# write_csv(panel, "W:/irb/optimize/panel/change_2026_01/wpm/test_responses.csv")

```



# Prelaunch
Verify new question labels match style/tone combo
```{r}
# 
# new_q_labels <- readxl::read_xlsx(file.path("W:/irb/optimize/panel/change_2026_01/wpm/timing calcs.xlsx"), sheet="question_by_tone") |>
#   arrange(survey, user_index, q_number) |>
#   select(-c(`...9`,`...10`)) |>
#   glimpse()
# 
# panel_data_raw <- read_csv(file.path("W:/irb/optimize/panel/change_2026_01/wpm/panel_study_messages_combined_January+23,+2026_21.32.csv")) |> 
#   head(1) |>
#   select(contains(c("_hi_", "_hd_", "_li_"))) |>
#   select(-contains(c("timing", "attention"))) |>
#   mutate(across(everything(), ~ str_remove_all(.x, "- I found this message to be helpful."))) |>
#   mutate(across(everything(), ~ str_remove_all(.x, "\\\""))) |>
#   mutate(across(everything(), ~ str_trim(.x, "both"))) |>
#   pivot_longer(everything()) |>
#   rename(online_q_label = name, generated_message = value) |>
#   glimpse()
# 
# 
# full_join(new_q_labels, panel_data_raw) |> 
#   mutate(match = str_detect(online_q_label, new_q_label)) |>
#   View()

```

