---
title: "Suspicion Index for llmpanel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In Progress

## Purpose

This script is used to conduct thorough EDA of the final 510 survey respondents, and to further investigate respondents for fraudulent or otherwise untrustworthy behavior questioning the validity of the sample. Objectives include:

- Build the suspicion index to inform a decision about excluding additonal respondents from the final sample

- Modelling EDA to inform recipe-building and feature-engineering

- Overwrite panel.csv in long format

```{r}
library(tidyverse) 
library(kableExtra, exclude = "group_rows")
library(cowplot, include.only = c("plot_grid", "theme_half_open"))
library(corrplot, include.only = "corrplot.mixed")
library(geosphere)

devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
devtools::source_url("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")

path_panel <- format_path("llmpanel/data_raw/panel")
path_processed <- format_path("llmpanel/data_processed")
```

```{r}
panel <- read_csv(here::here(path_processed, "panel.csv"), show_col_types = FALSE)
```

## Suspicion Index

Before modelling EDA, we should fully consider any further exclusions from our final pool of 510 respondents. There are a variety of 'variables of concern' which this section will use to build a 'suspicion index', which is a quantified measure of how concerned we are about the authenticity of each respondent's data. The primary factors that this index will attempt to capture are:

1. Botting - Synthetic responses from malicious actors attempting to mine compensation from paid surveys online. We DO NOT want this data anywhere in our sample. It's not just low quality, it's fake.

2. Disengaged participants - Respondents who may have been genuinely human, but still speed through surveys without giving them the proper time and attention to provide meaningful responses. It is the manual, inefficient way to mine compensation as quickly and carelessly as possible. This is arguably just as bad as botting and equally unusable if we know that a respondent did not take the survey seriously.

### Building _sus variables

We will need to engineer many of our component variables for the suspicion index. This section will walk through the reasoning behind each component.

#### *Survey completion time*
```{r}
plot_hist(panel, x = "q_total_duration", bins = 10)

sort(panel$q_total_duration)
```

Rapid survey completion is a common indicator of botting. Protective measures were taking with hard timing checks required for a respondent to remain eligible during the survey, at a maximum allowable reading speed of 400wpm given the length of all survey questions in each block. Incorporating this variable back into the suspicion index will hopefully help identify the disengaged human respondents who managed to be slow enough to qualify, but were likely skimming and not providing thoughtful responses.

There are also outliers with very long completion times. These are currently not being considered suspicious. If anything, long completion time is an indicator that a respondent took breaks throughout the day to go through the survey, and is likely a sign of giving a large amount of thought and energy into responses.

For these reasons, the duration_sus feature will measure the standardized distance below median completion time. Any respondent at or above the median duration will receive a value of 0, meaning 'not suspicious at all'. Many of our _sus features will follow similar logic.

*Construct duration_sus*
```{r}
panel <- panel |> 
  mutate(duration_std = (q_total_duration - median(q_total_duration)) / mad(q_total_duration),
         duration_sus = if_else(duration_std < 0, abs(duration_std), 0)
         )

panel$duration_sus |> sort(decreasing = TRUE) |> head(10)
plot_hist(panel, x = "duration_sus", bins = 10)
```

#### *ReCaptcha Score*

```{r}
plot_hist(panel, x = "q_recaptcha_score", bins = 5)
sort(panel$q_recaptcha_score)
panel |> filter(q_recaptcha_score == 0.5) |> count() 
panel |> filter(is.na(q_recaptcha_score)) |> count() 
```

ReCaptcha scores are a probability measure that each respondent is human. Any scores below 0.5 (more likely bot than human) were automatically rejected from the survey. We still have many respondents that captcha was not confident about, however, for example with 17 respondents having a score of 0.5 = equal probability of bot or human. Given the nature of this variable, captcha_sus will measure standardized distance below 1.0 (max value).

There are also 4 respondents with NA values, which Qualtrics has identified as respondents who apparently took a captcha through a 3rd party provider before being forwarded to the survey . . . they will receive a conservative imputed value of 0.5.

*Construct captcha_sus*
```{r}
panel <- panel |> mutate(
  q_recaptcha_score = if_else(is.na(q_recaptcha_score), 0.5, q_recaptcha_score),
  captcha_std = (q_recaptcha_score - mean(q_recaptcha_score)) / sd(q_recaptcha_score),
  captcha_sus = abs(captcha_std - max(captcha_std))
)

panel$captcha_sus |> sort(decreasing = TRUE) |> head(10)
plot_hist(panel, x = "captcha_sus", bins = 10)
```

#### *Audit Score*

```{r}
panel$audit_score |> sort(decreasing = TRUE)
plot_hist(panel, x = 'audit_score', bins = 10)
```

We have some very high audit results up to *perfect* scores of 40 in the sample (2 participants), which is concerning that respondents may have intuited our criteria of AUD symptoms and fraudulently reported the most concerning behaviors possible.

Values below or somewhat above the mean would not be suspicious, however. For now, audit_sus will simply flag those 2 perfect score respondents.

*Construct audit_sus*
```{r}
panel <- panel |> 
  mutate(
    audit_sus = if_else(audit_score == 40, TRUE, FALSE)
  )
```

#### *Variability in tone survey*

```{r}
panel |>
  rowwise() |>
  filter(n_distinct(c_across(q1_legitimizing_1:q5_norms_1)) == 1) |>
  nrow()

panel <- panel |>
  mutate(
    across(
      q1_legitimizing_1:q5_norms_1,
      ~ case_when(
        .x == "strongly_disagree" ~ -3,
        .x == "disagree"          ~ -2,
        .x == "somewhat_disagree" ~ -1,
        .x == "neutral"           ~  0,
        .x == "somewhat_agree"    ~  1,
        .x == "agree"             ~  2,
        .x == "strongly_agree"    ~  3
      ),
      .names = "{.col}_num"),
  ) |>
  rowwise() |>
  mutate(
    tone_sd  = sd(c_across(q1_legitimizing_1_num:q5_norms_1_num)),
    tone_sus = tone_sd == 0
  ) |>
  ungroup()

plot_hist(panel, x = 'tone_sd', bins = 10)
```

We have 103 responded who straight-lined across the tone survey, meaning they put the same rating for each of the 5 tones with 0 variability.

#### *Variability in message ratings*

```{r}
msg_prefixes <- c(
  "x1_hi", "x1_hd", "x1_li",
  "x2_hi", "x2_hd", "x2_li",
  "x3_hi", "x3_hd", "x3_li",
  "x4_hi", "x4_hd", "x4_li"
)

# Count respondents who straight-lined across all answered message columns
panel |>
  rowwise() |>
  filter({
    vals <- c_across(matches("^x[1-4]_(hi|hd|li)_\\d+_") & ends_with("_num"))
    vals <- vals[!is.na(vals)]
    length(vals) > 0 && n_distinct(vals) == 1
  }) |>
  ungroup() |>
  nrow()

# Numericize
likert_to_num <- function(x) {
  case_when(
    x == "strongly_disagree" ~ -3,
    x == "disagree"          ~ -2,
    x == "somewhat_disagree" ~ -1,
    x == "neutral"           ~  0,
    x == "somewhat_agree"    ~  1,
    x == "agree"             ~  2,
    x == "strongly_agree"    ~  3
  )
}

panel <- panel |>
  mutate(across(matches("^x[1-4]_(hi|hd|li)_"), likert_to_num, .names = "{.col}_num"))

# Row-wise SDs
panel <- panel |>
  rowwise() |>
  mutate(
    msg_sd      = sd(c_across(matches("^x[1-4]_(hi|hd|li)_\\d+_") & ends_with("_num")), na.rm = TRUE),
    rating_sus  = msg_sd == 0
  ) |>
  ungroup()

plot_hist(panel, x = 'msg_sd', bins = 10)
```

We have 23 respondents who straight-lined across all message ratings with no variability. *This is strongest single criterion to consider for another hard exclusion.*

#### *GPS data*

##### *Device location vs city lat/long*

We use two sets of coordinates for this feature: first is the device-level location collected by Qualtrics, and the second is a geocoded lat/long based in the city a respondent reported they live in.

```{r}
panel <- panel |> 
  mutate(
    gps_diff = distHaversine(p1 = cbind(location_longitude, location_latitude),
                             p2 = cbind(city_longitude, city_latitude)) / 1000 # Set to KM
  )

plot_hist(panel, x = "gps_diff", bins = 10)
sort(panel$gps_diff, decreasing = TRUE) |> head(10)
panel |> filter(gps_diff > 1000) |> count()
```

While most respondents appear close to home (as they are expected to be), many are quite far. 22 are over 1000km = 621 miles away, which is already much further than anyone would reasonably commute for groceries. Some considerations:

- Many people use VPNs as an everyday protection measure against being tracked online. Many newer phones today have a form of VPN built in for users as well, meaning it doesn't even need to be intentionally set up. Some of these large differences could be a VPN projecting a distance further from where the respondent lives, intentionally or not. If we knew it was intentional, it would be of greater concern for an individual pretending to be in the United States to qualify for the survey despite living or being a bot overseas.

*If this was the case, however, practically every major VPN service allows you to choose the location you are spoofing. Meaning that if I live in Canada, I can set my VPN to a server in Chicago, LA, etc. very precisely. It wouldn't make sense for me to pick a city for my VPN and then provide a response on the survey that is 1000s of KMs away.

*If you are smart enough to fake your location for a survey, you would likely also be smart enough to report the same location as where you live*

*Captcha should also be attempting to catch known VPN server IP addresses, so many of these attempts would have never made it into our list of survey completions.

- People may be taking the survey while they are travelling. Or they are have a temporary residence for work or school yet reported their home city.

All of this to say, anomalies in location distance should be taken with grains of salt. The gps_sus feature will measure standardized distance above the median.

```{r}
panel <- panel |> 
  mutate(gps_std = (gps_diff - median(gps_diff)) / mad(gps_diff),
         gps_sus = if_else(gps_std > 0, abs(gps_std), 0)
         )

panel$gps_sus |> sort(decreasing = TRUE) |> head(10)
plot_hist(panel, x = "gps_sus", bins = 5)
```

##### *Grocery store anomalies*

```{r}
panel |> count(grocer_code) |> arrange(desc(n))
```

### Index Calculation

```{r}
build_suspicion_index <- function(data,
                                  numeric_high = NULL,
                                  numeric_med  = NULL,
                                  numeric_low  = NULL,
                                  flag_high    = NULL,
                                  flag_med     = NULL,
                                  flag_low     = NULL,
                                  numeric_weights = c(high = 3, med = 2, low = 1),
                                  flag_values    = c(high = 3, med = 2, low = 1)) {

  score <- rep(0, nrow(data))

  # Weighted standardized numeric variables
  for (priority in c("high", "med", "low")) {
    vars <- switch(priority, high = numeric_high, med = numeric_med, low = numeric_low)
    if (!is.null(vars)) {
      score <- score + rowSums(data[vars] * numeric_weights[[priority]], na.rm = TRUE)
    }
  }

  # Fixed-value flag variables
  for (priority in c("high", "med", "low")) {
    vars <- switch(priority, high = flag_high, med = flag_med, low = flag_low)
    if (!is.null(vars)) {
      score <- score + rowSums(data[vars] * flag_values[[priority]], na.rm = TRUE)
    }
  }

  data |> mutate(suspicion_index = score)
}
```

*List of suspicion variables to work with*
```{r}
panel |> select(contains("sus")) |> names()
```

```{r}
panel <- panel |> build_suspicion_index(numeric_high = c('duration_sus', 'captcha_sus', 'gps_sus'),
                                        flag_high = c('audit_sus', 'tone_sus', 'rating_sus'))
```

```{r}
plot_hist(panel, x = "suspicion_index", bins = 10)
```

```{r}
panel |> select(contains("sus")) |> names()

panel <- panel |>
  mutate(suspicion_index = rowMeans(pick(contains("_sus")), na.rm = TRUE))

panel |>
  select(response_id, suspicion_index) |>
  arrange(desc(suspicion_index))

plot_hist(panel, x = 'suspicion_index')
```



```{r}
tibble(cutoff = c("90th", "80th", "70th", "60th", "50th"),
       pct    = c(90, 80, 70, 60, 50)) |>
  mutate(
    suspicion_index = quantile(panel$suspicion_index, pct / 100, na.rm = TRUE),
    n_retained      = map_int(suspicion_index, \(t) sum(panel$suspicion_index < t, na.rm = TRUE))
  ) |>
  select(cutoff, suspicion_index, n_retained)
```


