---
title: "Panel EDA"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

# Univariate Demographics

*General Demographics*

```{r}
panel |> 
  select(dem_sex, dem_identity,
         dem_income, dem_marital_status) |>
  names() |>
  map(\(name) plot_bar(df = panel, x = name)) |>
  plot_grid(plotlist = _, ncol = 2)
```

> Most notable is the mild imbalances in sex/gender.

```{r}
panel |> 
  select(dem_orientation, dem_education) |>
  names() |>
  map(\(name) plot_bar(df = panel, x = name)) |>
  plot_grid(plotlist = _, ncol = 2)
```

> Large imbalance in sexual orientation with predominantly 'straight' respondents.

*Race/Ethnicity*

```{r}
panel |>
  select(starts_with("dem_race_"), -dem_race_other_text) |>
  pivot_longer(everything(), names_to = "group", values_to = "response") |>
  filter(response == "yes") |>
  count(group) |>
  mutate(group = group |>
    str_remove("^dem_race_") |>
    str_replace_all("_", " ") |>
    str_to_title()) |>
  ggplot(aes(x = n, y = reorder(group, n))) +
  geom_col() +
  labs(x = "Count", y = NULL, title = "Race/Ethnicity")
```

> Another pronounced imbalance with predominantly white respondents.

*Age*

```{r}
plot_hist(panel, x = "dem_age", bins = 10)
panel$dem_age |> sort(decreasing = TRUE) |> head(10)
```

> There are some very old respondents in the survey, however there is no clear motivation for someone to exaggerate their age here. This does not raise immediate suspicion.

```{r}
median(panel$q_total_duration)/60
min(panel$q_total_duration)/60

mean(panel$dem_age)

panel |> arrange(desc(dem_age)) |>
  transmute(
    age  = dem_age,
    mins = q_total_duration / 60,
    dist_below_median = if_else(
      q_total_duration < median(q_total_duration),
      (median(q_total_duration) - q_total_duration) / 60,
      NA_real_)
  ) |>
  slice_head(n = 10)
```

> Our oldest respondent completed the survey faster than the median completion time (mean age is \~ 48). If anything, we should expect longer completion times. This begins to raise concern.

> Investigation of that oldest participant, however, does reveal variability in message ratings and a sensible user input response.

# Univariate Preferences

*Ordering*

```{r}
tone_scale = c("Strongly Disagree", "Disagree", "Somewhat Disagree",
               "Neutral", "Somewhat Agree", "Agree", "Strongly Agree")

panel <- panel |> mutate(
  across(c(q1_legitimizing:q5_norms),
      ~ factor(.x, levels = tone_scale)),
    q6_formality = factor(q6_formality,
                          levels = c("Strongly Prefer Informal", "Moderately Prefer Informal",
                                       "Slightly Prefer Informal", "Slightly Prefer Formal",
                                       "Moderately Prefer Formal", "Strongly Prefer Formal")))
```

*Tone Preferences*

```{r}
panel |> 
  select(q1_legitimizing:q5_norms) |>
  names() |>
  map(\(name) plot_bar(df = panel, x = name)) |>
  plot_grid(plotlist = _, ncol = 3)
```

> Described tones are generally agreed with.

*Style Preferences*

```{r}
plot_bar(df = panel, x = "q6_formality")
```

> Respondents generally prefer informal.

 # Message Ratings

*Order/Numeric*

```{r}
message_scale = c("strongly_disagree", "disagree", "somewhat_disagree",
                  "neutral", "somewhat_agree", "agree", "strongly_agree")

panel_long <- panel_long |> 
  mutate(
    message_rating = factor(message_rating, levels = message_scale),
    message_rating_num = case_when(
      message_rating == "strongly_disagree" ~ -3,
      message_rating == "disagree" ~ -2,
      message_rating == "somewhat_disagree" ~ -1,
      message_rating == "neutral" ~ 0,
      message_rating == "somewhat_agree" ~ 1,
      message_rating == "agree" ~ 2,
      message_rating == "strongly_agree" ~ 3)
  )

panel_long <- panel_long |> 
  mutate(
    dem_education = factor(dem_education,
                           levels = c("less_than_high_school_or_ged_degree",
                                      "high_school_or_ged", "some_college",
                                      "2_year_degree", "4_year_degree",
                                      "advanced_degree"))
  )

panel_long <- panel_long |> 
  mutate(dem_income = factor(dem_income,
                             levels = c(
                               "Less than $25,000",
                               "$25,000 - $37,499",
                               "$37,500 - $49,999",
                               "$50,000 - $74,999",
                               "$75,000 - $99,999",
                               "$100,000 - $149,999",
                               "$150,000 - $199,999",
                               "$200,000 or more")
                             ))

# All message ratings
plot_bar(panel_long, x = "message_rating")
```

> Messages are generally found helpful.

## Message Ratings by Demographics

*Message Ratings by Sex*

```{r}
ggplot(panel_long, aes(x = message_rating, fill = dem_sex)) +
  geom_bar(position = "dodge") +
  labs(x = "Message Rating", y = "Count", fill = "Sex")

panel_long |> group_by(dem_sex) |> 
  summarise(
    'mean rating' = mean(message_rating_num)
  )
```

*Message Ratings White x Other*

```{r}
panel_long <- panel_long |> mutate(
  white_x_other = case_when(
    dem_race_white == "yes" ~ "white",
    dem_race_white == "no" ~ "other")
  )
means_race <- panel_long |> summarise(
  mean_rating = mean(message_rating_num), .by = white_x_other
  )
panel_long |>
  count(white_x_other, message_rating) |>
  group_by(white_x_other) |>
  mutate(prop = n / sum(n)) |>
  ggplot(aes(x = message_rating, y = prop, fill = white_x_other)) +
  geom_col(position = position_dodge()) +
  geom_label(
    data = means_race |>
      mutate(nudge = if_else(white_x_other == "white", 0.24, 0.21)),
    aes(x = "disagree", y = nudge,
        label = paste0(white_x_other, " mean: ", round(mean_rating, 2)),
        color = white_x_other),
    fill = "white", size = 3, show.legend = FALSE) +
  labs(x = "Message Rating", y = "Proportion", fill = "Race/Ethnicity", color = NULL) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

*Message Ratings by Sexual Orientation*

```{r}
panel_long <- panel_long |> mutate(
  straight_x_other = if_else(dem_orientation == "straight", "straight", "other"))

means_straight <- panel_long |> summarise(
  mean_rating = mean(message_rating_num), .by = straight_x_other)

panel_long |>
  count(straight_x_other, message_rating) |>
  group_by(straight_x_other) |>
  mutate(prop = n / sum(n)) |>
  ggplot(aes(x = message_rating, y = prop, fill = straight_x_other)) +
  geom_col(position = position_dodge()) +
  geom_label(
    data = means_straight |>
      mutate(nudge = if_else(straight_x_other == "straight", 0.24, 0.21)),
    aes(x = "disagree", y = nudge,
        label = paste0(straight_x_other, " mean: ", round(mean_rating, 2)),
        color = straight_x_other),
    fill = "white", size = 3, show.legend = FALSE) +
  labs(x = "Message Rating", y = "Proportion", fill = "Orientation", color = NULL) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

*Message_Ratings by Age Group*

```{r}
panel_long <- panel_long |> 
  mutate(
    age_group = case_when(
      dem_age > 17 & dem_age < 30 ~ "18-20's",
      dem_age > 29 & dem_age < 40 ~ "30's",
      dem_age > 39 & dem_age < 50 ~ "40's",
      dem_age > 49 & dem_age < 60 ~ "50's",
      dem_age > 59 ~ "60+"
    )
  )
panel_long |> group_by(age_group) |> summarise(
  'mean rating' = mean(message_rating_num))
```

```{r}
panel_long |>
  summarise(mean_rating = mean(message_rating_num, na.rm = TRUE), .by = age_group) |>
  ggplot(aes(x = age_group, y = mean_rating)) +
  geom_col() +
  geom_text(aes(label = round(mean_rating, 2)), vjust = -0.5, size = 3)
```

*Income*
```{r}
```

# Eyeball Sample
```{r}
eyeball_ids <- read_csv(file.path(path_processed, "eyeball_ids.csv"), show_col_types = FALSE)

eyeball_wide <- panel |> filter(response_id %in% eyeball_ids$eyeball_ids)

eyeball_long <- panel_long |> filter(response_id %in% eyeball_ids$eyeball_ids)
```

## Preferences by Demographics

(IN PROGRESS - * check if correlation between preference and message rating differs by demographics)

#### Age by X

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q1_legitimizing", y = "dem_age")
```

> May be an older bias against legitimizing.

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q2_self_efficacy", y = "dem_age")
```
> Self-efficacy more preferred by younger participants.

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q3_acknowledging", y = "dem_age")
```

> Seems to trend younger for acknowledging, very few disagreements in general.

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q4_value_affirmation", y = "dem_age")
```

> Less strong relationship with age and self-affirmation.

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q5_norms", y = "dem_age")
```
> Less strong relationship with age and normalization.

```{r}
plot_grouped_box_violin(df = eyeball_wide, x = "q6_formality", y = "dem_age")
```

> Less strong relationship with age and formality. Younger folks may have the strongest desire for formality?

#### Gender by X

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q1_legitimizing")
```

> Male opinions are more neutral about legitimizing.

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q2_self_efficacy")
```

> Mixed.

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q3_acknowledging")
```

> Mixed.

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q4_value_affirmation")
```
> Male disagree more with value affirmation.

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q5_norms")
```
> Male opinions are more neutral on normalization.

```{r}
plot_grouped_barplot_percent(df = eyeball_wide, x = "dem_identity", y = "q6_formality")
```

> Male tend to prefer formal while Female tend to prefer informal, relative to each other.

#### Education by X

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q1_legitimizing")
```
> 

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q2_self_efficacy")
```
>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q3_acknowledging")
```

>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q4_value_affirmation")
```
>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q5_norms")
```
>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_education", y = "q6_formality")
```

>

#### Income by X

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q1_legitimizing")
```

>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q2_self_efficacy")
```

>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q3_acknowledging")
```
>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q4_value_affirmation")
```

>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q5_norms")
```
>

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_income", y = "q6_formality")
```
#### Minoritization by X

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q1_legitimizing")
```
> No change in trend with minoritization for legitimizing.

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q2_self_efficacy")
```

> No change in trend with minoritization for self-efficacy.

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q3_acknowledging")
```
> No change in trend with minoritizaition with acknowledging.

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q4_value_affirmation")
```
> No change in trend with minoritization for value_affirmation.

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q5_norms")
```
> Minoritization may find normalization less effective?

```{r}
plot_grouped_barplot_count(df = eyeball_wide, x = "dem_minority", y = "q6_formality")
```
> Minoritization may tend to favor formality more?

## Message Tone x Demographics

*Sex/Gender*

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num), .by = c(dem_sex, tone)) |>
  ggplot(aes(x = mean_rating, y = dem_sex, fill = tone)) +
  geom_col(position = position_dodge())
```

*Race/Ethnicity*

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num, na.rm = TRUE), .by = c(white_x_other, tone)) |>
  ggplot(aes(x = mean_rating, y = white_x_other, fill = tone)) +
  geom_col(position = position_dodge())
```

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num, na.rm = TRUE), .by = c(straight_x_other, tone)) |>
  ggplot(aes(x = mean_rating, y = straight_x_other, fill = tone)) +
  geom_col(position = position_dodge())
```
```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num, na.rm = TRUE), .by = c(age_group, tone)) |>
  ggplot(aes(x = mean_rating, y = age_group, fill = tone)) +
  geom_col(position = position_dodge())
```

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num, na.rm = TRUE), .by = c(dem_education, tone)) |>
  ggplot(aes(x = mean_rating, y = dem_education, fill = tone)) +
  geom_col(position = position_dodge())
```
> Note: only one 'less than HS' respondent in the eyeball sample.

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num), .by = c(dem_marital_status, tone)) |>
  ggplot(aes(x = mean_rating, y = dem_marital_status, fill = tone)) +
  geom_col(position = position_dodge())
```
> Note: only 1 'separated' and 4 'widowed' in the eyeball sample

```{r}
eyeball_long |>
  summarise(mean_rating = mean(message_rating_num), .by = c(dem_income, tone)) |>
  ggplot(aes(x = mean_rating, y = dem_income, fill = tone)) +
  geom_col(position = position_dodge())
```
