---
title: "Get GPS data for llmpanel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully Functional

## Purpose

- Clean open-text grocery store responses for better geocode results
- Use Google Maps API to geocode respondent city/state and grocery stores
- Identify respondents whose grocery store failed to verify via API for manual review

- This script overwrites panel.csv to include lat/long coordinates for every respondents' city + state, to be compared with IP address and grocery store location.

* This script saves 'grocer_gps.rds' in /data_raw to avoid re-running API calls. This is a nested large list object with the full output of geocode() for each grocery store address. Commented code lines in this script do not need to be re-run unless there are new respondents that require geocoding.

## Setup

```{r}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse)
library(ggmap)

source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")

path_credentials <- format_path("other")
path_raw <- format_path("llmpanel/data_raw")
path_processed <- format_path("llmpanel/data_processed")
```

*Get credentials*
```{r}
key_google <- get_credentials("google_api",
  file.path(path_credentials, "credentials.csv")) |>
  pull(key)

register_google(key = key_google)
```

*Load in data*
```{r}
panel <- read_csv(here::here(path_processed, "panel.csv"))

panel |> count(flag) |> print(n=100)
```

```{r}
# Separate our valid and manually rejected responses
panel_510 <- panel |> 
  filter(is.na(q_duplicate_respondent)) |> 
  filter(is.na(flag) | str_detect(flag, "_ip_") | flag == "straightliner")
```

## Cleaning open-text responses

*Clean grocery store open-responses for cross-validation*

Many typos and inconsistencies exist within the raw responses for nearest grocery store address (HEB vs. H-E-B, etc.)
This code enforces a series of standardized spellings/formats for various grocery stores, and fixes typos that were identified by manual review.

```{r}
grocer_name_stds <- c(
  # --- Walmart ---
  "(?i)^super\\s*wal[\\s-]*mart$"      = "Walmart Supercenter",
  "(?i)^walmart\\s*supercenter$"        = "Walmart Supercenter",
  "(?i)^wal[\\s-]*m[ao]?r?t$"          = "Walmart",
  "(?i)^wall\\s*mart$"                  = "Walmart",
  "(?i)^walm[ao]t$"                     = "Walmart",
  "(?i)^walmart,\\s*.+"                 = "Walmart",   # name field contains address
  # --- Kroger ---
  "(?i)^kri[ao]?ger['s]*$"             = "Kroger",
  "(?i)^kroger['s]*$"                  = "Kroger",
  # --- H-E-B ---
  "(?i)^h[\\.\\s]*e[\\.\\s]*b[\\.\\s]*(store)?$" = "H-E-B",
  "(?i)^heb$"                           = "H-E-B",
  # --- Hy-Vee ---
  "(?i)^hy[-\\s]*vee$"                  = "Hy-Vee",
  "(?i)^hyvee$"                         = "Hy-Vee",
  # --- Food Lion ---
  "(?i)^food[-\\s]*lion$"               = "Food Lion",
  # --- Dollar General ---
  "(?i)^dollar\\s*general$"             = "Dollar General",
  # --- Family Dollar ---
  "(?i)^family\\s*dollar$"              = "Family Dollar",
  # --- Trader Joe's ---
  "(?i)^trader['s]*\\s*joe['s]*$"       = "Trader Joe's",
  # --- Costco ---
  "(?i)^cos[t]?co$"                     = "Costco",
  # --- ShopRite ---
  "(?i)^shop[\\s-]*rite$"               = "ShopRite",
  "(?i)^shoperite$"                     = "ShopRite",
  # --- Winn-Dixie ---
  "(?i)^winn[\\s-]*dixie$"              = "Winn-Dixie",
  # --- Aldi ---
  "(?i)^aldi['s]*$"                     = "Aldi",
  # --- Piggly Wiggly ---
  "(?i)^piggly\\s*wiggly$"              = "Piggly Wiggly",
  # --- Whole Foods ---
  "(?i)^whole\\s*foods(\\s*market)?$"   = "Whole Foods",
  # --- Target ---
  "(?i)^targer$"                        = "Target",
  # --- 7-Eleven ---
  "(?i)^7[\\s-]*eleven$"                = "7-Eleven",
  "(?i)^seven\\s*eleven$"               = "7-Eleven",
  # --- Stater Bros ---
  "(?i)^stater\\s*br(os?|others)$"      = "Stater Bros",
  # --- Stop & Shop ---
  "(?i)^stop\\s*(and|&)\\s*shop$"       = "Stop & Shop",
  # --- Market Basket ---
  "(?i)^market\\s*basket$"              = "Market Basket",
  # --- Food City ---
  "(?i)^food[-\\s]*city$"               = "Food City",
  # --- Save-A-Lot ---
  "(?i)^sav[e]?[-\\s]*a[-\\s]*lot$"     = "Save-A-Lot",
  # --- WinCo ---
  "(?i)^winco[s]?$"                     = "WinCo",
  # --- Harris Teeter ---
  "(?i)^harris\\s*teeter$"              = "Harris Teeter",
  # --- Amazon Fresh ---
  "(?i)^amazon(\\s*fresh)?$"            = "Amazon Fresh",
  # --- IGA ---
  "(?i)^iga$"                           = "IGA",
  # --- Cub Foods ---
  "(?i)^cub(\\s*foods)?$"               = "Cub Foods",
  # --- Star Market ---
  "(?i)^star[-\\s]?market$"             = "Star Market",
  # --- Fred Meyer ---
  "(?i)^fred\\s*m[ey]+r[s]?$"           = "Fred Meyer",
  # --- Hannaford ---
  "(?i)^hann[ai]?ford$"                 = "Hannaford",
  # --- Brookshire's ---
  "(?i)^brookshire['s]*$"               = "Brookshire's",
  # --- Giant Eagle ---
  "(?i)^giant\\s*eagle$"                = "Giant Eagle",
  # --- Giant (standalone) ---
  "(?i)^giants?$"                       = "Giant",
  # --- Price Chopper ---
  "(?i)^price\\s*chopper$"              = "Price Chopper",
  # --- Pick 'N Save ---
  "(?i)^pick[\\s'-]*n[\\s'-]*save$"     = "Pick 'N Save",
  # --- BJ's ---
  "(?i)^bj['s]*(\\s*wholesale\\s*club)?$" = "BJ's",
  # --- Safeway ---
  "(?i)^saf[ae]?way$"                   = "Safeway",
  # --- Big Y ---
  "(?i)^big\\s*y$"                      = "Big Y",
  # --- Smith's ---
  "(?i)^smith['s]+$"                    = "Smith's",
  # --- Jewel ---
  "(?i)^jewels?$"                       = "Jewel",
  # --- Ralphs ---
  "(?i)^ralphs?$"                       = "Ralphs",
  # --- Tom Thumb ---
  "(?i)^tom\\s*thumb$"                  = "Tom Thumb",
  # --- Sun Fresh ---
  "(?i)^sun\\s*fresh$"                  = "Sun Fresh",
  # --- Case-only fixes (must be last) ---
  "(?i)^publix$"   = "Publix",
  "(?i)^safeway$"  = "Safeway",
  "(?i)^target$"   = "Target",
  "(?i)^ingles$"   = "Ingles",
  "(?i)^vons$"     = "Vons",
  "(?i)^sprouts$"  = "Sprouts",
  "(?i)^wegmans$"  = "Wegmans",
  "(?i)^meijer$"   = "Meijer",
  "(?i)^lidl$"     = "Lidl",
  "(?i)^schnucks$" = "Schnucks",
  "(?i)^albertsons$"    = "Albertsons",
  "(?i)^haggens?$"      = "Haggen",
  "(?i)^festival\\s*foods$" = "Festival Foods",
  "(?i)^fresh\\s*market$"   = "Fresh Market",
  "(?i)^smart\\s*(and|&)\\s*final.*" = "Smart & Final",
  "(?i)^fry's\\s*food\\s*store$"     = "Fry's",
  "(?i)^save\\s*mart$"               = "Save Mart"
)
state_abbrev_stds <- c(
  "(?i)^AL$" = "Alabama",        "(?i)^AK$" = "Alaska",
  "(?i)^AZ$" = "Arizona",        "(?i)^AR$" = "Arkansas",
  "(?i)^CA$" = "California",     "(?i)^CO$" = "Colorado",
  "(?i)^CT$" = "Connecticut",    "(?i)^DE$" = "Delaware",
  "(?i)^FL$" = "Florida",        "(?i)^GA$" = "Georgia",
  "(?i)^HI$" = "Hawaii",         "(?i)^ID$" = "Idaho",
  "(?i)^IL$" = "Illinois",       "(?i)^IN$" = "Indiana",
  "(?i)^IA$" = "Iowa",           "(?i)^KS$" = "Kansas",
  "(?i)^KY$" = "Kentucky",       "(?i)^LA$" = "Louisiana",
  "(?i)^ME$" = "Maine",          "(?i)^MD$" = "Maryland",
  "(?i)^MA$" = "Massachusetts",  "(?i)^MI$" = "Michigan",
  "(?i)^MN$" = "Minnesota",      "(?i)^MS$" = "Mississippi",
  "(?i)^MO$" = "Missouri",       "(?i)^MT$" = "Montana",
  "(?i)^NE$" = "Nebraska",       "(?i)^NV$" = "Nevada",
  "(?i)^NH$" = "New Hampshire",  "(?i)^NJ$" = "New Jersey",
  "(?i)^NM$" = "New Mexico",     "(?i)^NY$" = "New York",
  "(?i)^NC$" = "North Carolina", "(?i)^ND$" = "North Dakota",
  "(?i)^OH$" = "Ohio",           "(?i)^OK$" = "Oklahoma",
  "(?i)^OR$" = "Oregon",         "(?i)^PA$" = "Pennsylvania",
  "(?i)^RI$" = "Rhode Island",   "(?i)^SC$" = "South Carolina",
  "(?i)^SD$" = "South Dakota",   "(?i)^TN$" = "Tennessee",
  "(?i)^TX$" = "Texas",          "(?i)^UT$" = "Utah",
  "(?i)^VT$" = "Vermont",        "(?i)^VA$" = "Virginia",
  "(?i)^WA$" = "Washington",     "(?i)^WV$" = "West Virginia",
  "(?i)^WI$" = "Wisconsin",      "(?i)^WY$" = "Wyoming",
  "(?i)^DC$" = "District of Columbia"
)
panel <- panel |>
  mutate(
    # Normalize curly apostrophes, then standardize name
    grocer_name = str_replace_all(grocer_name, "\u2019", "'") |> str_squish(),
    grocer_name = str_replace_all(grocer_name, grocer_name_stds),
    # Expand state abbreviations to full names before building address
    state = str_replace_all(state, state_abbrev_stds),
    grocer_address = str_squish(
      paste(grocer_name, grocer_street, city, state, sep = " "))
  )
# Remove junk phrases from the full address string
remove_phrases <- regex(
  paste(
    "its in",
    "i dont know",
    "don't know",
    "not sure",
    "bronx n\\.y",
    "ottumwa iowa",
    sep = "|"
  ),
  ignore_case = TRUE
)
# Address-level fixes (duplicates, formatting, etc.)
address_fixes <- c(
  "(?i)tell13"                                                                    = "tell 13",
  "(?i)2800arapahoe"                                                              = "2800 Arapahoe",
  "(?i)Kroger, Kroger, Junction city, Ky"                                         = "Kroger, Junction city, Ky",
  "(?i)Smart and final on Arlington, Walmart on Van Buren, Riverside, California" = "Smart and final, Arlington, Riverside, California",
  "(?i)Walmart, Eisenhower dr., Aldi, Eisenhower dr., Hanover, PA"                = "Walmart, Eisenhower dr., Hanover, PA",
  "(?i)Walmart, 1010 112th St Amory MS, Amory, MS"                                = "Walmart, 1010 112th St, Amory, MS",
  "(?i)24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL 60104, United States, Chicago, IL"  = "24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL"
)
panel <- panel |>
  mutate(
    grocer_address = str_replace_all(grocer_address, "\u2019", "'"),
    grocer_address = grocer_address |>
      str_remove_all(remove_phrases) |>
      str_replace_all(address_fixes) |>
      str_squish()
  ) |> 
  relocate(city, .after = grocer_street) |> 
  relocate(state, .after = city) |>
  relocate(grocer_address, .after = state)
```

## Geocode

### City/State Coordinates 

These coordinates reference the respondent's home city, to be compared with IP address lat/long coordinates from Qualtrics.

```{r}
gps_info <- read_csv(here::here(path_processed, "gps_info.csv"))

panel_510 <- panel |>
  filter(response_id %in% grocery_info$response_id) |> 
  left_join(grocery_info, by = "response_id")

inv <- panel_510 |> select(response_id, city, state)

# Separate remaining valid participants - we only need to geocode these
#panel_valid <- panel |> filter(is.na(flag))
```

*Pull API and bind directly to panel*
```{r}
# API call only for valid respondents
city_gps <- inv |>
  mutate(geocode(paste(city, state)))

# Join back to full panel, NAs for invalid respondents
grocery_info_new <- grocery_info |>
  left_join(city_gps, by = "response_id") |>
  rename(
    city_longitude = lon,
    city_latitude = lat
  )

grocery_info_new <- grocery_info_new |> select(-city, -state)

grocery_info_new |> write_csv("C:/Users/Andrew/Desktop/gps_info.csv")
# Save updates to file
#panel |> write_csv(here::here(path_processed,"panel.csv"))
```

### Grocery Store Addresses

The reason for output = all is that any partial/incomplete match still returns lat/long coordinates that are indistinguishable from proper matches. If ggmap doesn't find a Walmart in Madison, WI, it will provide a generic lat/long for just Madison itself. The full geocode output includes a flag for these cases that is dropped otherwise.

Because there are costs associated with the Google Maps API, saving the full object allows us to refer back to any discarded information without needing to re-run the call. In other words, if we need to make changes or additions to this script in the future, we can load in grocer_gps.rds to test the script freely.

*Pull API and save separate object*
```{r}
valid_ids <- which(is.na(panel$flag))

grocer_gps_sub <- geocode(
  panel$grocer_address[valid_ids],
  output = "all")

grocer_gps <- vector("list", nrow(panel))
grocer_gps[valid_ids] <- grocer_gps_sub

grocer_gps |> saveRDS(here::here(path_raw, 'grocer_gps.rds'))
```

*Load in chunk for RDS file (last generated 8-2-2026)*
```{r}
grocer_gps <- readRDS(here::here(path_raw, "grocer_gps.rds"))
```

*Bind the returned addresses from geocode() + lat/long onto the panel itself.*
```{r}
extract_field <- function(gps_list, i, field) {
  res <- tryCatch(gps_list[[i]]$results[[1]], error = function(e) NULL)
  switch(field,
    formatted_address = if (is.null(res)) NA_character_ else res$formatted_address %||% NA_character_,
    lat               = if (is.null(res)) NA_real_      else res$geometry$location$lat %||% NA_real_,
    lng               = if (is.null(res)) NA_real_      else res$geometry$location$lng %||% NA_real_
  )
}
panel <- panel |>
  mutate(
    ggmap_grocer_address = map_chr(
      seq_along(grocer_gps),
      ~extract_field(grocer_gps, .x, "formatted_address")),
    
    grocer_latitude = map_dbl(
      seq_along(grocer_gps),
      ~extract_field(grocer_gps, .x, "lat")),
    
    grocer_longitude = map_dbl(
      seq_along(grocer_gps),
      ~extract_field(grocer_gps, .x, "lng"))
  ) |> 
  relocate(ggmap_grocer_address, .after = grocer_address) |> 
  relocate(grocer_latitude, .after = city_longitude) |> 
  relocate(grocer_longitude, .after = grocer_latitude)
```

*Spot check to ensure subids are matched appropriately*
```{r}
set.seed(1221)
check_idx <- sample(which(is.na(panel$flag)), 3)

tibble(
  idx               = check_idx,
  input_address     = panel$grocer_address[check_idx],
  returned_address  = panel$ggmap_grocer_address[check_idx],
  grocer_lat        = panel$grocer_latitude[check_idx],
  grocer_lng        = panel$grocer_longitude[check_idx],
  raw_lat           = map_dbl(check_idx, ~extract_field(grocer_gps, .x, "lat")),
  raw_lng           = map_dbl(check_idx, ~extract_field(grocer_gps, .x, "lng"))
)
```

## Grocer EDA

*Check where ggmap failed to fully match an address*
```{r}
partial_match_vals <- rep(NA, nrow(panel))
partial_match_vals[valid_ids] <- sapply(grocer_gps[valid_ids], function(x) {
  pm <- x$results[[1]]$partial_match
  if (is.null(pm)) FALSE else pm
})

table(partial_match_vals, useNA = "ifany")
```

*Check where ggmap did not label a location as a grocery store or supermarket*
```{r}
grocer_type_flag <- rep(NA_integer_, nrow(panel))
grocer_type_flag[valid_ids] <- map_int(grocer_gps[valid_ids], \(x) {
  types <- unlist(lapply(x$results, \(r) r$types))
  as.integer(any(c("grocery_or_supermarket", "supermarket") %in% types))
})

table(grocer_type_flag, useNA = "ifany")
```

*Add flags to panel*
```{r}
panel_flags <- panel |>
  mutate(grocer_partial_match = as.integer(partial_match_vals),
         grocer_type_flag = grocer_type_flag)
```

*Save panel w/ flags for manual review*
```{r}
#panel_flags |> write_csv(here::here(path_processed,"panel_test.csv"))
```

The full ggmap output provides two critical pieces of information: a flag for 'partial match', and a list of 'location types' for whatever location was identified, which includes if a location is marked as a "grocery_or_supermarket" or just "supermarket" (not sure why there is two, but in this case we are essentially grouping them together). The above code chunks are used to save a version of the panel with these flags, which can then be used to manually review responses.

### Manual Review Results

Manual review was conducted for the following respondents:

- ALL partial matches
- ANY full match that was not given the 'grocery_or_supermarket' or 'supermarket' type.

*Load in manual review results*
```{r}
grocer_codes <- read_csv(here::here(path_processed, "grocer_codes.csv"))
```

Manual review reduced the number of anomalous responses to 128/510 = 25.1%

These anomalies fall into a variety of categories, such as:

- Respondents providing a liquor store, gas station, restaurant, etc.
- Respondents who appear to have given their residential street name
- Respondents with undecipherable content in their responses
- Respondents with grocer stores that were simply not able to be found
- Respondents whose grocery store was a considerable drive away from their city
    *Currently, any store that was found to be greater than 30m away was flagged as anomalous, aside from some cases where the respondent clearly lived in a rural area. 



Respondents who gave a valid grocery store, but initially flagged as either partial match or wrong location type, also fell into a variety of categories:

- Simple typos

- Respondents putting the "wrong" cross-street for stores located on an intersection, and similar mishaps

- Failures for no good reason (e.g., local non-chain stores often are missing the location type info)

    *ggmap REALLY wants zip codes and exact street numbers, which we did not ask for. This was the cause of very many failures, at no fault to respondents, and warrants a complete redesign of this grocer store CV question idea in future projects.

    * Furthermore, if a respondent gave "Walmart - Highway 19", ggmap will fail if there are multiple Walmarts along that highway because we did not provide a zip code or street number. There were enough of these instances to make it worth mentioning. Some of our cities are so infested with Kroger's and the like that there were a bazillion of them all along the same "main street", and so on.

- Walmart is a pain: "Neighborhood Markets", "Supercenters" and regular stores are all treated as uniquely separate businesses by ggmap, meaning that either of these Walmart subtypes were given a partial match if the respondent just said "Walmart" (like a normal person would...)

### The rural respondent dilemma

I am concerned that imparting high scrutiny on respondents with anomalous responses will introduce some bias against those living in rural areas. It is reasonable to assume that some small, local grocery stores will not be cataloged properly online. While some respondents with long drive times to their grocery store were set aside as clearly being rural, some of the flagged respondents probably do have genuine long commute that shouldn't be cause for concern. The weight of these factors in our suspicion index and exclusions process should keep this in mind.

*Add grocer codes to panel*
```{r}
add_grocer_code <- function(panel, grocer_codes) {
  lookup <- grocer_codes |>
    pivot_longer(everything(), names_to = "grocer_code", values_to = "subid") |>
    drop_na(subid)

  dupe_ids <- lookup$subid[duplicated(lookup$subid)]
  if (length(dupe_ids) > 0) warning("Duplicate subids in grocer_codes: ", paste(dupe_ids, collapse = ", "))

  panel |>
    select(-any_of("grocer_code")) |>
    left_join(lookup, by = "subid") |>
    mutate(grocer_code = replace_na(grocer_code, "valid"))
}

panel <- add_grocer_code(panel, grocer_codes) |> 
  relocate(grocer_code, .after = grocer_longitude)
```

## Save updated panel
```{r}
panel |> filter(!is.na(gps_diff)) |> write_csv(here::here(path_processed,"panel.csv"))
```

Done! Next is panel_eda which will investigate these results and other aspects of the data.
