---
title: "Suspicion Index for llmpanel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In Progress

## Purpose

This script is used to conduct EDA and build a suspicion index to inform decision-making for any possible further exclusions from the remaining 456 eligible survey responses, prior to bringing data into the modelling workflow.

- Conduct EDA on multiple 'variables of concern' to establish a threshold where each variable will contribute a point towards the final suspicion index scores.

- Construct the final index, make comparisons between remaining eligible responses and manually excluded responses previously flagged.

- Decide suspicion index threshold to establish the final valid sample for analysis.

## Setup

```{r}
library(tidyverse)
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/study_llmpanel/blob/main/scripts/functions_llmpanel.R?raw=true")

#library(kableExtra, exclude = "group_rows")
#library(cowplot, include.only = c("plot_grid", "theme_half_open"))
#library(corrplot, include.only = "corrplot.mixed")
#source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
#source("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")

path_processed <- format_path("llmpanel/data_processed")

# Read in full panel
panel <- read_csv(here::here(path_processed, "panel.csv"), show_col_types = FALSE)
```

## Variables of Concern

Each variable will be investigated separately and assigned a unique threshold for suspicion.

### IP Address

We are concerned with responses with a non-unique IP (at least 1 other survey attempt matches). While all cases of IP + demographic matches have already been flagged as duplicates and removed from the remaining eligible sample, this component will add to the suspicion index if a respondent had a matching IP address with at least 1 other survey attempt that did not match on demographics.

2. A respondent completed multiple 

*Construct IP Flag*
```{r}
# Flag all responses with a non-unique IP
panel <- panel |>
  group_by(ip_address) |>
  mutate(
    grp_other = sum(!is.na(flag) & flag != "same_ip_dupe"),       # We are excluding cases where
    own       = as.integer(!is.na(flag) & flag != "same_ip_dupe"),# a respondent had multiple
    ip_sus    = n() > 1 & (grp_other - own) > 0                   # completed surveys from the
  ) |>                                                            # same IP with no logic fails.
  ungroup() |>
  select(-grp_other, -own)

# Separate out eligible, rejected, and a combined subset
split_panel(panel)
```

*Distributions*
```{r}
prop_table("ip_sus")
```

A higher proportion of non-unique IPs in our manually rejected responses is supporting evidence that IP address makes for a meaningful variable in the suspicion index.

### Tone Survey Straight-lining

We are concerned about responses with 0 variability in the tone preferences survey - also known as straight-lining. While respondents who straight-lined on message ratings have already been rejected, respondents who only straight-lined on the tone survey have remained eligible.

*Conduct straight-lining flag*
```{r}
# Flag responses with identical responses to all tone questions
panel <- panel |> 
  rowwise() |> 
  mutate(tone_sus = n_distinct(c_across(q1_legitimizing_1:q5_norms_1)) == 1) |> 
  ungroup()

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Proportions*
```{r}
prop_table("tone_sus")
```

Another higher proportion in the rejected subset for straight-lining! This should remain a key component in the suspicion index.

### Click Count

Click count metadata was collected by Qualtrics in addition to time spent on each survey block. Responses showing unusually high click counts may be indicative of bot scraping behavior, and may warrant suspicion as a result.

*Construct click count total*
```{r}
# Take the sum of all by-block click counts
panel <- panel |>
  rowwise() |> 
  mutate(click_total = sum(c_across(contains("_click_count")), na.rm = TRUE)) |> 
  ungroup()

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Distributions*
```{r}
compare_plot("click_total", bins = 3, display = 'max')
```

We actually have a higher median and max value in the eligible responses with a notable outlier.

```{r}
p_eligible |> filter(click_total == max(click_total)) |> 
  summarise(clicks = click_total,
            "duration (minutes)" = q_total_duration/60,
            clickrate = q_total_duration/click_total)

min(p_full$click_total)
```

The outlier averaged 1 click every 6.85 seconds for the entirety of their 41-minute survey duration, which is realistically achievable by a human hand. Knowing that the survey can be completed in as little as 41 clicks, however, does indicate very excessive mouse clicking by this individual. While this could be indicative botting behavior, there are also other reasonable explanations including a broken/faulty computer mouse, happy finger, etc.

#### Clicks per second

Looking at the rate/frequency of clicks may be more informative that click count alone.

*Create click rate variable*
```{r}
panel <- panel |> mutate(
  click_rate = click_total/q_total_duration # Switching to clicks per 1 second
)

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Distributions*
```{r}
compare_plot("click_rate")
```

Aside from our 1 outlier, the distribution appears roughly normal without a major discrepancy between the eligible and rejected subsets. Clicks will be excluded from the suspicion index for now.

### Completion Time / Duration

While a strict exclusion criteria was enforced for responses that would have required > 400 WPM reading speed, we may still be concerned with unusually fast responses among the remaining eligible sample.

*Distributions*
```{r}
panel <- panel |> 
  mutate(
    duration_mins = q_total_duration/60 # Convert from seconds to minutes
  )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)

compare_plot("duration_mins", stat = 'median', display = 'min', bins = 4)
```

Our eligible subset contains both the lowest and highest values, with a notable long-duration outlier. Previous discussions have posited this observation was likely from a respondent who left the survey open on their device from a prolonged period, before returning to finish the remainder. If anything, this is likely evidence of a respondent paying very close attention to the questions instead of speeding through carelessly, and does not warrant suspicion as a result. Let's look at the distribution for what are likely our one-sitting completions for more granularity.

```{r}
compare_plot("duration_mins", stat = 'median', display = 'min', bins = 10,
  top = p_rejected |> filter(duration_mins <= 60),
  mid = p_full     |> filter(duration_mins <= 60),
  bot = p_eligible |> filter(duration_mins <= 60)
)
```

```{r}
mad(p_eligible$duration_mins)
p_eligible |> filter(q_total_duration < 720) |> nrow()
```

A filter at <12m  (a bit more than 1 MAD below) flags 16 eligible respondents. Although we do not see major discrepancy between the eligible and rejected distributions, survey duration is still theoretically a very important indicator of how seriously a respondent considered each survey question. Because of our rather liberal cutoff of 400 wpm reading speed in the initial screening process, it feels proper to include suspicion for our remaining fastest responses.

*Create duration flag*
```{r}
# Set threshhold at 13m
panel <- panel |> 
  mutate(
    duration_sus = q_total_duration < 720
  )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

### ReCaptcha Score

We are concerned with responses with low or NA captcha scores. These scores are a direct probability measure of whether or not a respondent is a human being (and not a bot), provided by Qualtrics through ReCaptcha proprietary methods. While scores below 0.5 were automatically rejected from our sample, remaining values can be as low as 0.5 or NA in the event that a 3rd party survey provider contracted through Qualtrics did not share a score for their respondents.

*Distributions*
```{r}
compare_plot("q_recaptcha_score", stat = 'mean', bins =6, display = "min", labels = "left")
```

Captcha is an essential first step for identifying bots. As such, it feels proper to include suspicion for our lowest scores of 0.5, as well as NAs.

*Construct captcha flag variable*
```{r}
# Flag minimum values of 0.5 & NAs
panel <- panel |> 
  mutate(
    captcha_sus = q_recaptcha_score <= 0.5 |
                  is.na(q_recaptcha_score)
    )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Proportions*
```{r}
prop_table("captcha_sus")
```

While the histogram comparison did not indicate a major difference in the distribution of scores between the eligible and rejected subsets, our constructed captcha flag does see a higher proportion of suspicious responses among the rejected!

### Audit Score

We are concerned with respondents who may have exaggerated AUDIT responses in an attempt to screen into the survey for compensation. A threshold of "perfect" AUDIT scores of 40 will be used for the index, which can also be thought of as another instance of straight-lining.

*Distributions*
```{r}
compare_plot("audit_score", bins = 20, stat = "mean", display = "max")

panel |> filter(!is.na(audit_score)) |> nrow()
panel |> filter(!is.na(audit_score)) |>
  count(audit_score) |> arrange(desc(audit_score)) |> print(n=40)

panel |> filter(audit_score == 40) |> count(flag)
```

It first looks like we lack supporting evidence with the rejected subset containing no responses with a max audit score of 40, but this is also reasonably expected given how rare a max score is and the small size of the rejected subset. Out of the 3886 survey attempts that got through the AUDIT, only 13 provided a perfect score of 40. With only 2 of these cases making their way into eligible sample, the remaining 11 automatically flagged out on either a captcha or attention-check failure.

All that said, it feels proper to include suspicion for max value AUDIT scores.

*Create AUDIT flag variable*
```{r}
# Flag "perfect" 40/40 scores
panel <- panel |> 
  mutate(
    audit_sus = audit_score == 40
  )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

### GPS Data

We are concerned with respondents having a large discrepancy between their reported and observed location, which may indicate VPN usage or other identity-masking attempts. The gps_diff variable contains the lowest of two value:

- Distance from reported city/state to IP address location
- Distance from reported city/state to reported grocery store

*Distributions*
```{r}
compare_plot("gps_diff", bins = 4, display = "max", stat = "median")
```

As with AUDIT scores, this may be another case where the small rejected subset size is the reason why we don't see as many outliers when compared to the eligible subset. Regardless, a distance of hundreds or thousands of kilometers is convincingly suspicious. 

```{r}
mad(p_eligible$gps_diff)
p_eligible |> filter(gps_diff > 500) |> nrow()
```

A threshold of 100km distance (~311 miles) is over 30 MADs above the median, and feels like a plenty liberal threshold to use. This will flag 39 responses in the eligible subset.

While a lower threshold could be set for establishing suspicion, the large 500km number was chosen for two reasons:

1. There are some genuine explanations for large distances - IP addresses behave weirdly for smartphones completing the survey through cellular data, respondents living in very rural areas, etc. This current threshold should excuse most of these honest discrepancies, leaving suspicion primarily for distances so egregious that something is definitely wrong.

2. Lower thresholds do not create the increase in flagged proportion between the valid and rejected subset that we are in part using to calibrate the suspicion index. By 500km it has become pronounced enough to support the inclusion of this component.

*Create GPS flag*
```{r}
# Flag responses with a distance over 500km
panel <- panel |> 
  mutate(
    gps_sus = gps_diff > 500
  )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Proportions*
```{r}
prop_table('gps_sus')
```

The flag threshold sees the rejected subset show a higher proportion of suspicious responses.

### Grocery Store Anomalies

We are concerned with respondents who gave anamalous open-text responses to the grocery store questions, across a variety of categories. While many were excused as non-suspicious (e.g., online delivery), the remaining types were considered suspicious. 

*Construct grocery flag variable*
```{r}
# Flag all anomalous response types
panel <- panel |> 
  mutate(
    grocery_sus = replace_na(
      grocery_code == "gave_liquorstore" |
      grocery_code == "grocer_notfound" |
      grocery_code == "match_plus_anomaly" |
      grocery_code == "missing_street" |
      grocery_code == "gave_twostores" |
      grocery_code == "gave_closedstore" |
      grocery_code == "gave_hospital", FALSE)
  )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

*Proportions*
```{r}
prop_table('grocery_sus')
```

The rejected subset shows a higher proportion of suspicious grocery responses!

## Suspicion Index Calculation

All variables except for click count/rate will be included in the index. There are currently no additional weightings being applied to any suspicion components, meaning that each component is being considered equally suspicious as all others.

*Create suspicion index variable*
```{r}
# Add relevant columns
panel <- panel |> 
  mutate(
       suspicion_index = ip_sus +
                      tone_sus +
                      duration_sus +
                      captcha_sus +
                      audit_sus +
                      gps_sus +
                      grocery_sus
       )

# Redefine eligible, rejected, and combined subsets
split_panel(panel)
```

### RESULTS

*Distributions*
```{r}
compare_plot("suspicion_index", bins = 5, stat = "mean", display = "max")
```

1. The rejected sample shows a higher mean score for the final suspicion index, which is a sign of good calibration. The rejected sample also has a higher max value of 4, compared to a max value of 3 in the eligible subset.

2. The highest possible score would be all 7, but the max value of 3 in the eligible sample means that even our most suspicious candidates were still FALSE for most of the suspicion components.

3. If we exclude the most suspicious respondents among the remaining eligible sample, we will lose 4 with a final total of n = 452 for analysis.

## Exclusions
```{r}
panel_final <- p_eligible |> filter(suspicion_index < 4) # PLACEHOLDER
```
