---
title: "Suspicion Index for llmpanel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In Progress

## Purpose

This script is used to conduct EDA and build a suspicion index to inform decision-making for any possible further exclusions from the remaining 456 eligible survey responses, prior to bringing data into the modelling workflow.

- Conduct EDA on 8 'variables of concern' to establish a threshold where each variable will contribute a point towards the final suspicion index scores.

- Construct the final index, make comparisons between remaining eligible responses and manually excluded responses previously flagged.

- Decide suspicion index threshold to establish the final valid sample for analysis.

## Setup

```{r}
library(tidyverse) 
#library(kableExtra, exclude = "group_rows")
#library(cowplot, include.only = c("plot_grid", "theme_half_open"))
#library(corrplot, include.only = "corrplot.mixed")

#source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
#source("https://github.com/jjcurtin/lab_support/blob/main/fun_plots.R?raw=true")

path_processed <- format_path("llmpanel/data_processed")

# Read in full panel
panel <- read_csv(here::here(path_processed, "panel.csv"), show_col_types = FALSE)
p_full <- panel |> filter(!is.na(gps_diff))

# Separate out remaining eligible and manually rejected responses
p_eligible <- p_full |>
  filter(is.na(flag))

p_rejected <- p_full |> 
  filter(!is.na(flag))
```

## Variables of Concern

Each variable will be investigated separately with a unique threshhold determined by analyzing distributions.
Note that the distributions being considered here will be restricted

*Compare plot function*
```{r}
compare_plot <- function(var,
                         top = NULL,
                         mid = NULL,
                         bot = NULL,
                         top_label = "Rejected    (n = 54)",
                         mid_label = "Total    (n = 510)",
                         bot_label = "Eligible   (n = 456)",
                         bins = 10,
                         display = "none",
                         stat = "median")
  {defaults <- c(top = "p_rejected", mid = "p_full", bot = "p_eligible")
  for (nm in names(defaults)) {
    if (is.null(get(nm))) {
      if (!exists(defaults[[nm]], envir = globalenv()))
        stop("Default object '", defaults[[nm]],
             "' not found. Either create it or pass a data frame to `", nm, "`.")
      assign(nm, get(defaults[[nm]], envir = globalenv()))
    }
  }
  panel_labels <- c(top = top_label, mid = mid_label, bot = bot_label)
  panels <- list(top = top, mid = mid, bot = bot)
  panel_names <- c("top", "mid", "bot"
                   )
  stat_fn <- if (stat == "mean") mean else median
  stat_label <- if (stat == "mean") "Mean" else "Median"

  combined <- bind_rows(
    lapply(panel_names, \(nm) panels[[nm]] |> mutate(panel = panel_labels[[nm]]))
  ) |>
    mutate(panel = factor(panel, levels = panel_labels))

  x_range <- range(combined[[var]], na.rm = TRUE)
  bin_breaks <- seq(x_range[1], x_range[2], length.out = bins + 1)

  stats <- bind_rows(
    lapply(panel_names, \(nm) {
      panels[[nm]] |>
        summarise(
          center = stat_fn(.data[[var]], na.rm = TRUE),
          min_val = min(.data[[var]], na.rm = TRUE),
          max_val = max(.data[[var]], na.rm = TRUE),
          panel = nm
        )
    })
  ) |>
    mutate(
      panel = factor(panel_labels[panel], levels = panel_labels),
      label = case_when(
        display == "min" ~ paste0(stat_label, ": ", round(center, 2), "\nMin: ", round(min_val, 2)),
        display == "max" ~ paste0(stat_label, ": ", round(center, 2), "\nMax: ", round(max_val, 2)),
        .default = paste0(stat_label, ": ", round(center, 2))
      )
    )

  fill_colors <- setNames(c("red3", "darkgoldenrod2", "chartreuse4"), panel_labels)

  ggplot(combined, aes(x = .data[[var]], fill = panel)) +
    geom_histogram(breaks = bin_breaks, alpha = 0.7) +
    geom_vline(data = stats, aes(xintercept = center),
      linetype = "dashed", linewidth = 0.8) +
    geom_text(data = stats,
      aes(x = Inf, y = Inf, label = label),
      vjust = 1.2, hjust = 1.05, size = 3.5, lineheight = 0.9) +
    stat_bin(breaks = bin_breaks, geom = "text",
             aes(label = after_stat(ifelse(count > 0, count, ""))),
      vjust = -0.3, size = 3) +
    facet_wrap(~panel, ncol = 1, scales = "free_y") +
    scale_y_continuous(expand = expansion(mult = c(0, 0.15))) +
    scale_fill_manual(values = fill_colors) +
    labs(x = var, y = "Count") +
    guides(fill = "none")
}
```

### IP Address

IP is a variable of concern when an eligible respondent has a non-unique IP (at least 1 other survey attempt matches)

*Construct IP Flag*
```{r}
# Flag all responses with a non-unique IP
panel <- panel |> 
  mutate(
    ip_sus = duplicated(ip_address) | duplicated(ip_address, fromLast = TRUE)
  )

# Separate eligible and rejected responses
split_panel <- function(data = panel) {
  p_full     <- data |> filter(!is.na(gps_diff))
  p_eligible <- data |> filter(is.na(flag))
  p_rejected <- data |> filter(!response_id %in% p_eligible$response_id)

  assign("p_full",     p_full,     envir = parent.frame())
  assign("p_eligible", p_eligible, envir = parent.frame())
  assign("p_rejected", p_rejected, envir = parent.frame())
}

split_panels()

```

*Distributions*
```{r}
bind_rows(
  p_full |> mutate(group = "Full n=510"), 
  p_eligible |> mutate(group = "Eligible n=456"),
  p_rejected |> mutate(group = "Rejected n=54")
) |>
  summarise(prop_ip_sus = mean(ip_sus, na.rm = TRUE), .by = group)
```

A higher proportion of flagged responses in the manually rejected subset is supporting evidence that we have selected a meaningful variable for the suspicion index.

### Tone Survey Straight-lining

We are concerned with responses that demonstrated 0 variability in the tone preferences survey - also known as straight-lining, a common method for speeding through surveys imprecisely.

*Conduct straight-lining flag*
```{r}
# Flag responses with identical responses to all tone questions
panel <- panel |> 
  rowwise() |> 
  mutate(tone_sus = n_distinct(c_across(q1_legitimizing_1:q5_norms_1)) == 1) |> 
  ungroup()

# Redefine eligible and rejected responses to include the flag
p_full <- panel |> filter(!is.na(gps_diff))
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Distributions*
```{r}
p_eligible |> count(tone_sus)
p_rejected |> count(tone_sus)

bind_rows(
  p_full |> mutate(group = "Full n=510"), 
  p_eligible |> mutate(group = "Eligible n=456"),
  p_rejected |> mutate(group = "Rejected n=54")
) |>
  summarise(prop_tone_sus = mean(tone_sus, na.rm = TRUE), .by = group)
```

Another higher proportion of flags in the previously rejected subset!

### Click Count

Click count metadata was collected by Qualtrics in addition to time spent on each survey block. We are concerned with responses showing unusually high click counts which may be indicative of bot scraping behavior.

*Construct click count total*
```{r}
# Take the sum of all by-block click counts
panel <- panel |>
  rowwise() |> 
  mutate(click_total = sum(c_across(contains("_click_count")), na.rm = TRUE)) |> 
  ungroup()

# Redefine eligible and rejected responses to include the total
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Distributions*
```{r}
compare_plot("click_total", bins = 5, display = 'max')
```

We actually have higher median and max values in the eligible responses, with a notable outlier.

```{r}
p_eligible$click_total |> sort(decreasing = TRUE) |> head(10)
median(p_eligible$click_total)
mad(p_eligible$click_total)

p_eligible |> filter(click_total >= 75) |> nrow()
p_eligible |> filter(click_total == 358) |> select(q_total_duration) |> print()
```

The outlier averaged roughly 1 click every 10 seconds for their ~40 survey completion time, realistically achievable. This variable may not be necessary to include in the suspicion index.

#### Clicks per second

Looking at the rate/frequency of clicks may be more informative that click count alone.

*Create click rate variable*
```{r}
panel <- panel |> mutate(
  click_rate = click_total / q_total_duration
)

# Redefine eligible and rejected responses to include the rate
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Distributions*
```{r}
compare_plot("click_rate")
```

No concerning click rates

### Completion Time / Duration

While a script exclusion criteria was enforced for responses that would have required > 400 WPM reading speed, we may still be concerned with unusually fast responses among the remaining eligible sample.

*Distributions*
```{r}
compare_plot("q_total_duration", stat = 'median', display = 'min', bins = 30)
```

```{r}
mad(p_eligible$q_total_duration)
p_eligible |> filter(q_total_duration < 780) |> nrow()
```

A filter at <13m flags 34 eligible respondents

*Create duration flag*
```{r}
# Set threshhold at 13m
panel <- panel |> 
  mutate(
    duration_sus = q_total_duration < 780
  )

# Redefine eligible and rejected responses to include the rate
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

```{r}
p_eligible |> count(duration_sus)
```

### ReCaptcha Score

We are concerned with responses with low or NA captcha scores

*Distributions*
```{r}
compare_plot("q_recaptcha_score", stat = 'mean', bins = 10)

mean(p_eligible$q_recaptcha_score, na.rm = TRUE)
mean(p_rejected$q_recaptcha_score, na.rm = TRUE)

sd(p_eligible$q_recaptcha_score, na.rm = TRUE)
```

*Construct captcha flag variable*
```{r}
# Flag minimum values of 0.5 & NAs
panel <- panel |> 
  mutate(
    captcha_sus = q_recaptcha_score <= 0.5 |
                  is.na(q_recaptcha_score)
    )

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Proportions*
```{r}
mean(p_eligible$captcha_sus)
mean(p_rejected$captcha_sus)

p_eligible |> count(captcha_sus)
```

Rejects retain a higher proportion of flagged responses

### Audit Score

We are concerned with respondents who may have exaggerated AUDIT responses in an attempt to screen into the survey for compensation. A threshold of "perfect" AUDIT scores of 40 will be used for the index, which can also be thought of as another instance of straight-lining.

*Distributions*
```{r}
compare_plot("audit_score", bins = 10, stat = "mean", display = "max")
p_eligible |> filter(audit_score == 40) |> nrow()
```

Minimum and median scores are higher in the rejected subset, but only the eligible respondents retained perfect scores of 40 (2 total).

*Create AUDIT flag variable*
```{r}
# Flag "perfect" 40/40 scores
panel <- panel |> 
  mutate(
    audit_sus = audit_score == 40
  )

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

### GPS Data

We are concerned with respondents having a large discrepancy between their reported and observed location. The gps_diff variable contains the lowest of two value:

- Distance from reported city/state to IP address location
- Distance from reported city/state to reported grocery store

*Distributions*
```{r}
compare_plot("gps_diff", bins = 10, display = "max", stat = "median")
mad(p_eligible$gps_diff)
p_eligible |> filter(gps_diff > 750) |> nrow()
```

- The median distance in the rejected subset is lower by ~5km
- A threshold at 750km flags 23 eligible respondents

*Create GPS flag*
```{r}
# Flag responses with a distance over 750km
panel <- panel |> 
  mutate(
    gps_sus = gps_diff > 750
  )

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Proportions*
```{r}
mean(p_eligible$gps_sus)
mean(p_rejected$gps_sus)
```

The flag threshold sees the rejected subset show a higher proportion of suspicious responses.

### Straightliner Flag

```{r}
panel <- panel |> mutate(
  straight_sus = flag == "straightliner"
)

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```


### Dupe response
```{r}
panel <- panel |> mutate(
  dupe_sus = str_detect(flag, "_ip_")
)

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

### Grocery Store Anomalies

We are concerned with respondents who gave anamalous open-text responses to the grocery store questions, across a variety of categories.

*Construct grocery flag variable*
```{r}
# Flag all anomalous response types
panel <- panel |> 
  mutate(
    grocery_sus = replace_na(
      grocery_code == "gave_liquorstore" |
      grocery_code == "grocer_notfound" |
      grocery_code == "match_plus_anomaly" |
      grocery_code == "missing_street" |
      grocery_code == "gave_twostores" |
      grocery_code == "gave_closedstore" |
      grocery_code == "gave_hospital", FALSE)
  )

# Redefine eligible and rejected responses to include the flag
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Proportions*
```{r}
mean(p_eligible$grocery_sus)
mean(p_rejected$grocery_sus)

p_eligible |> count(grocery_sus)
```

The rejected subset shows a higher proportion of suspicious grocery responses.

## Suspicion Index Calculation

All variables except for click_count will be included in the index.

*Create suspicion index variable*
```{r}
# Add relevant columns
panel <- panel |> 
  mutate(
       suspicion_index = ip_sus +
                      tone_sus +
                      duration_sus +
                      captcha_sus +
                      audit_sus +
                      gps_sus +
                      grocery_sus +
                      straight_sus +
                      dupe_sus
  )

# Redefine eligible and rejected responses to include the index
p_eligible <- panel |> filter(is.na(flag))
p_rejected <- panel |> filter(!response_id %in% p_eligible$response_id)
```

*Distributions*
```{r}
compare_plot("suspicion_index", bins = 5, stat = "mean")
```

*Counts*
```{r}
p_eligible |> count(suspicion_index)
```

### Exclusions
```{r}
panel_final <- p_full
```
