---
title: "Get Qualtrics"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully functional

- Qualtrics has occasionally modified the format of exported data files when
downloaded or pulled via API. Re-running this script over time may produce
files with slightly different formats as a result, possibly leading to errors
when passed into proceeding scripts for cleaning and EDA. Inspect every file.

## Purpose

-   Pull panel data from Qualtrics via API
-   Save a raw export file with the unmodified data file

*Setup*

```{r}
#| include: false

library(tidyverse) 
options(conflicts.policy = "depends.ok")

#source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/download_qualtrics.R?raw=true")

path_data <- format_path("llmpanel/data_raw")
path_credentials <- format_path("other")
```

*Get Credentials*

```{r}
token_qualtrics <- get_credentials("qualtrics",
  here::here(path_credentials, "credentials.csv")) |>
  pull(token)
```

*Download results by API*

```{r}
panel_api_raw <- NULL

# Retry on intermittent 404s from Qualtrics until successful download. 

repeat {
  panel_api_raw <- tryCatch(
    {download_qualtrics(
        survey_id = "SV_dbAKSR75ATWSo2q",
        api_token = token_qualtrics,
        display_progress = TRUE)
      },
    error = function(e) {
      if (str_detect(conditionMessage(e), "404")) {
        message("Qualtrics returned 404. Retrying in 5 seconds...")
        Sys.sleep(5)
        return(NULL)}
      stop(e)
      })
  if (!is.null(panel_api_raw)) {break}
  }
```

*save raw API file*

```{r}
panel_api_raw |>
  write_csv(here::here(path_data,"panel_api_raw.csv"))
```