---
title: "GPS data for llmpanel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully Functional

* The list of incomplete matches for grocery addresses has not been fully investigated. This does not appear to be any issue with the code, rather a lack of precise information in the open-responses from respondents, but future changes to cleaning steps could possibly improve performance and reduce the amount of manual review required.

## Purpose

- Use Google Maps API to geocode respondent city/state and match grocery store addresses for EDA / Cross-Validation

- This script saves two files: 

--- panel_eda.csv is an updated panel_wide.csv from mak_panel.qmd with geocoded lat/long coordinates joined.

--- grocer_gps.rds is the full nested list object that geocode produces for grocery store addresses, which contains more information than is relevant to join to the panel object.

* Saved copies of these files are located in the S drive, meaning this script does not need to be rerun unless changes are made or there is an expected difference in geocode results. 


## Setup

```{r}
#| include: false

options(conflicts.policy = "depends.ok")
library(tidyverse)
library(ggmap)
library(geosphere)

source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")

path_credentials <- format_path("other")
path_raw <- format_path("llmpanel/data_raw")
path_processed <- format_path("llmpanel/data_processed")
```

*Get credentials*
```{r}
key_google <- get_credentials("google_api",
  file.path(path_credentials, "credentials.csv")) |>
  pull(key)

register_google(key = key_google)
```

*Load in data*
```{r}
panel <- read_csv(here::here(path_processed, "panel_wide.csv"))
```

## Geocode

*Google API for geocode city/state*

These coordinates are a pinpoint in the respondent's indicated city of residence, to be compared to the device-level lat/long coordinates that Qualtrics provided.

```{r}
panel <- cbind(panel, geocode(paste(panel$city, panel$state))) |> 
  rename(
    city_longitude = lon,
    city_latitude = lat)

panel <- panel |> 
  relocate(city_latitude, .after = location_longitude) |> 
  relocate(city_longitude, .after = city_latitude)

panel |> write_csv(here::here(path_processed, str_c("panel_eda_", format(Sys.Date(), "%Y_%m_%d"), ".csv")))
```

*Google API for geocode grocery store addresses*

The reason for output = all and saving the separate file is because any partial/incomplete matches of addresses will still return lat/long coordinates that are otherwise indistinguishable from complete/proper matches. If ggmap doesn't find a Walmart in Madison, WI, it will provide a generic lat/long for just the city itself. The full geocode object will allow us to investigate where any why partial matches occur.

```{r}
grocer_gps <- geocode(
panel$grocer_address,
output = "all")

grocer_gps |> saveRDS(here::here(path_processed, str_c('grocer_gps_', format(Sys.Date(), "%Y_%m_%d"), ".rds")))
```

All done! Exploration of this data will occur in panel_eda.qmd