---
title: "Clean Panel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully functional.

## Purpose

-   Remove dropouts by screening method:
    -   Unfinished
    -   Previews
    -   Duplicate Responses
    -   CAPTCHA fails
    -   Healthy screen fails
    -   AUDIT fails
    -   Consent declines
    -   Age fails
    -   Attention check fails
    -   Timing check fails
    
-   Clean and pivot to long format for modeling
-   Save intermediary wide-format file for additional EDA and cross-validation

## Setup

```{r}
library(tidyverse) 
options(conflicts.policy = "depends.ok")

source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

path_raw <- format_path("llmpanel/data_raw")
path_processed <- format_path("llmpanel/data_processed")
```

*Load raw API data*

```{r}
#UPDATE IF USING A NEWER EXPORT FILE (AND CHECK FOR FORMAT DIFFRENCES)
panel_raw <- read.csv(here::here(path_raw, "panel_api_raw_2026_06_14.csv"))
panel_screen <- panel_raw
```

*Remove dummy rows*

```{r}
head(panel_screen, 1) # First row in export is a copy of question text. Remove:
panel_screen <- panel_screen |> slice(-1)
```

```{r}
head(panel_screen, 1) # Next row contains Qualtrics question IDs. Remove:
panel_screen <- panel_screen |> slice(-1)
head(panel_screen, 1) # Good to go
```

*Clean names and add summary variables for screening*

```{r}
panel_screen <- panel_screen |>
  janitor::clean_names("snake")  |>
  rename(health_drink = x47280739)

#Health screener flags
panel_screen <- panel_screen |> 
  mutate(
    all_health_no =
        health_food == "No" &
        health_floss == "No" &
        health_sleep == "No" &
        health_drink == "No" &
        health_water == "No",
    eligible_health = if_else(
        health_drink == "No" & !all_health_no, "eligible", "ineligible"))

# Collapse attention check Q's into a single flag for all respondents
panel_screen <- panel_screen |>
  mutate(att_check = if_any(contains("attention"), \(col) col == "Strongly Disagree")) |> 
  select(-contains("attention"))
```

## Filtering by screen-out

*Start tracking tibble for participant flow*

```{r}
flow <- tibble(flow = "total_submissions", 
               n_remaining = nrow(panel_screen), 
               n_failed = NA) |>
  print()
```

*Function for filtering based on valid values or thresholds*

```{r}
filter_value <- function(data, col, valid = NULL, threshold = NULL, keep_col = FALSE, print = FALSE, num = FALSE) {
  if (num) data <- data |> mutate(!!col := as.numeric(.data[[col]]))

  if (!is.null(threshold)) {
    keep <- \(x) is.na(x) | x >= threshold
    drop <- \(x) !is.na(x) & x < threshold
  } else if (is.na(valid)) {
    keep <- \(x) is.na(x)
    drop <- \(x) !is.na(x)
  } else {
    keep <- \(x) x == valid
    drop <- \(x) x != valid
  }

  flow <<- flow |> full_join(tibble(
    flow        = col,
    n_remaining = data |> filter(keep(.data[[col]])) |> nrow(),
    n_failed    = data |> filter(drop(.data[[col]])) |> nrow()
  ))

  if (print) print(flow, n = 100)

  data |>
    filter(keep(.data[[col]])) |>
    (\(d) if (!keep_col) select(d, -all_of(col)) else d)()
}
```

*Screen-outs*

```{r}
panel_screen <- panel_screen |> 
  filter_value(col = "finished", valid = "True") |>
  
  # Remove previews
  filter_value(col = "distribution_channel", valid = "anonymous") |>
  
  filter_value(col = "q_duplicate_respondent", valid = NA) |> 
  filter_value(col = "q_recaptcha_score", threshold = 0.5, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "all_health_no", valid = FALSE) |> 
  filter_value(col = "eligible_health", valid = "eligible") |> 
  filter_value(col = "audit_score", threshold = 8, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "consent_agree", valid = "I consent to participate and wish to proceed to the survey.") |> 
  filter_value(col = "q1_age", threshold = 18, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "att_check", valid = TRUE) |>
  
  # Timing thresholds at 400 wpm reading speed
  filter_value(col = "x1_hi_timing_page_submit", threshold = 101, num = TRUE) |> 
  filter_value(col = "x1_hd_timing_page_submit", threshold = 104, num = TRUE) |> 
  filter_value(col = "x1_li_timing_page_submit", threshold = 94, num = TRUE) |> 
  filter_value(col = "x2_hi_timing_page_submit", threshold = 102, num = TRUE) |> 
  filter_value(col = "x2_hd_timing_page_submit", threshold = 104, num = TRUE) |> 
  filter_value(col = "x2_li_timing_page_submit", threshold = 98, num = TRUE) |> 
  filter_value(col = "x3_hi_timing_page_submit", threshold = 102, num = TRUE) |> 
  filter_value(col = "x3_hd_timing_page_submit", threshold = 106, num = TRUE) |> 
  filter_value(col = "x3_li_timing_page_submit", threshold = 98, num = TRUE) |> 
  filter_value(col = "x4_hi_timing_page_submit", threshold = 100, num = TRUE) |> 
  filter_value(col = "x4_hd_timing_page_submit", threshold = 105, num = TRUE) |> 
  filter_value(col = "x4_li_timing_page_submit", threshold = 99, num = TRUE) |> 
  filter_value(col = "tone_timing_page_submit", threshold = 59, num = TRUE, print = TRUE)
```

The panel is now reduced to the final sample size of n = 510.

## Clean and format

*Convert empty strings to NAs, rename demographic cols, tidy responses*

```{r}
panel_clean <- panel_screen |> 
  mutate(
    across(q4_sexual_orientation:q5_race_ethnicity_7_text, ~na_if(.x, ""))
  ) |> 
  rename(dem_age = q1_age,
         dem_sex = q2_sex_at_birth,
         dem_identity = q3_gender_identity,
         dem_orientation = q4_sexual_orientation,
         dem_orientation_other_text = q4_sexual_orientation_6_text,
         dem_race_native_alaskan = q5_race_ethnicity_1, 
         dem_race_asian = q5_race_ethnicity_2,
         dem_race_hispanic = q5_race_ethnicity_3,
         dem_race_hawaiian_pacific = q5_race_ethnicity_4,
         dem_race_black = q5_race_ethnicity_5,
         dem_race_white = q5_race_ethnicity_6,
         dem_race_other = q5_race_ethnicity_7,
         dem_race_other_text = q5_race_ethnicity_7_text,
         dem_education = q6_education, 
         dem_student = q7_student_status,
         dem_income = q8_household_income,
         dem_n_household = q9_people_in_household,
         dem_marital_status = q10_marital_status, 
         dem_minority = q11_un_minoritization
         )
```

*Orientation*

- One respondent indicated 'other' with no additional information. This value will be rendered bi/pan as the most likely congruent option.
- Tidy responses.

```{r}
panel_clean |> count(dem_orientation_other_text)
panel_clean <- panel_clean |> select(-dem_orientation_other_text)

panel_clean <- panel_clean |> 
  mutate(
    dem_orientation = case_when(
      dem_orientation ==
        'Asexual' ~ 'asexual',
      dem_orientation ==
        'Heterosexual/Straight' ~ 'straight',
      dem_orientation ==
        'Lesbian/Gay' ~ 'gay_or_lesbian',
      dem_orientation ==
        'Bisexual/Pansexual' ~ 'bisexual_or_pansexual',
      dem_orientation ==
        'None of the above work for me, let me explain:' ~ 'bisexual_or_pansexual'))
```

*Race/Ethnicity*

The Qualtrics export provides a dummy-coded variable for every option from the check-all-that-apply.

- Clean to true/false flags for each option.

- Only one respondent indicated 'other' as Portuguese in addition to White/Caucasian. This has been considered additional information, but not another unique race/ethnic identity for our demographics. 'Other' columns will be removed.

- Only one respondent indicated Hawaiian/Pacific Islander, while also indicating Native American and White. This column will be removed as too specific in favor of Native American which is comparable.

```{r}
panel_clean <- panel_clean |>
  mutate(across(starts_with("dem_race_") & !contains("other"),
                ~ !is.na(.x)))
```

```{r}
panel_clean |> count(dem_race_other_text)
panel_clean |> count(dem_race_hawaiian_pacific)
panel_clean <- panel_clean |> select(-dem_race_other, -dem_race_other_text, -dem_race_hawaiian_pacific)
```

*Gender Identity*

- Many open-response values indicating male/female contained typos. Corrections here are ~hard-coded and may need updating if any new typos emerge in additional responses (510 completes currently)

- One respondent appears to have indicated their age again by mistake for this question. The value will be rendered to an assumption that the respondent is cisgender.

- One respondent each indicated 'Binary' and 'Trans'. 'Binary' in this case may indicate cisgender, or could be a typo of attempting to respond non-binary. These values will be left unchanged, with modelling recipes to consider dropping this variable in favor of solely incorporating sex at birth due to a very low representation of non-cis gender identities.

```{r}
panel_clean |> count(dem_identity)

panel_clean <- panel_clean |> 
  mutate(
    dem_identity = case_when(
      str_detect(dem_identity,
                 regex("^m", ignore_case = TRUE)) ~ "male",
      str_detect(dem_identity,
                 regex("^f", ignore_case = TRUE)) ~ "female",
      str_detect(dem_identity,
                 regex("^w", ignore_case = TRUE)) ~ "female",
      dem_identity == '38' ~ dem_sex,
      TRUE ~ dem_identity))
```

## Finish and save files

*Assign sub-ids #s (instead of response ID strings), remove redundant cols, tidy responses*
```{r}
panel_clean <- panel_clean |> 
  mutate(subid = row_number()) |> 
  relocate(subid) |> 
  select(where(~ n_distinct(., na.rm = FALSE) > 1)) |> 
  mutate(across(c(health_food:dem_orientation,
                  dem_education, dem_student,
                  dem_marital_status, dem_minority,
                  q1_legitimizing_1:q6_formality_1,
                  x1_hi_1_fl_1:x4_li_3_fn_1) & where(\(x) is.character(x) | is.factor(x)) & !contains("timing"),
                tidy_responses))
```

*Save wide format panel with all information for EDA/CV*
```{r}
panel_clean |> write_csv(here::here(path_processed, str_c("panel_wide_", format(Sys.Date(), "%Y_%m_%d"), ".csv")))
```

## Long Formatting

```{r}
panel_long <- panel_clean |>
  select(subid, dem_age:dem_minority, q1_legitimizing_1:q6_formality_1,
         `x1_hi_1_fl_1`:`x4_li_3_fn_1`,
         -contains("timing"), -contains("attention")) |>
  pivot_longer(
    cols= `x1_hi_1_fl_1`:`x4_li_3_fn_1`,
    values_to = "message_rating",
    names_to = "message_type") |>
  separate(message_type,
    sep = "_", into = c(
      "survey_version", "context", "q_num", "tone_style"),
    extra = "drop") |> 
  mutate(
    style = if_else(substr(tone_style, 1, 1) == "f", "formal", "informal"),
    tone = case_when(
      substr(tone_style, 2, 2) == "l" ~ "legitimizing",
      substr(tone_style, 2, 2) == "n" ~ "norms",
      substr(tone_style, 2, 2) == "s" ~ "self_efficacy",
      substr(tone_style, 2, 2) == "a" ~ "acknowledging",
      substr(tone_style, 2, 2) == "v" ~ "value_affirmation"),
    context = case_when(
      context == "hi" ~ "high_increasing",
      context == "hd" ~ "high_decreasing",
      context == "li" ~ "low_increasing")
    ) |>
  select(-q_num, -tone_style) |> 
  filter(!is.na(message_rating),
         str_trim(message_rating) != "")
```

*Save file for modelling*

```{r}
panel_clean |> write_csv(here::here(path_processed, str_c("panel_long_", format(Sys.Date(), "%Y_%m_%d"), ".csv")))
```
