---
title: "Make/Clean Panel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully functional.

## Purpose

-   Remove dropouts by screening method:
    -   Unfinished
    -   Previews
    -   Duplicate Responses
    -   CAPTCHA fails
    -   Healthy screen fails
    -   AUDIT fails
    -   Consent declines
    -   Age fails
    -   Attention check fails
    -   Timing check fails
    
-   Clean and pivot to long format for modeling
-   Clean open-response grocery store data for cross-validation
-   Save intermediary wide-format file for additional EDA and cross-validation

## Setup

```{r}
library(tidyverse) 
options(conflicts.policy = "depends.ok")

source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

path_raw <- format_path("llmpanel/data_raw")
path_processed <- format_path("llmpanel/data_processed")
```

*Load raw API data*

```{r}
#UPDATE IF USING A NEWER EXPORT FILE (AND CHECK FOR FORMAT DIFFRENCES)
panel_raw <- read.csv(here::here(path_raw, "panel_api_raw_2026_06_14.csv"))
panel_screen <- panel_raw
```

*Remove dummy rows*

```{r}
head(panel_screen, 1) # First row in export is a copy of question text. Remove:
panel_screen <- panel_screen |> slice(-1)
```

```{r}
head(panel_screen, 1) # Next row contains Qualtrics question IDs. Remove:
panel_screen <- panel_screen |> slice(-1)
head(panel_screen, 1) # Good to go
```

*Clean names and add summary variables for screening*

```{r}
panel_screen <- panel_screen |>
  janitor::clean_names("snake")  |>
  rename(health_drink = x47280739)

#Health screener flags
panel_screen <- panel_screen |> 
  mutate(
    all_health_no =
        health_food == "No" &
        health_floss == "No" &
        health_sleep == "No" &
        health_drink == "No" &
        health_water == "No",
    eligible_health = if_else(
        health_drink == "No" & !all_health_no, "eligible", "ineligible"))

# Collapse attention check Q's into a single flag for all respondents
panel_screen <- panel_screen |>
  mutate(att_check = if_any(contains("attention"), \(col) col == "Strongly Disagree")) |> 
  select(-contains("attention"))
```

## Filtering by screen-out

*Start tracking tibble for participant flow*

```{r}
flow <- tibble(flow = "total_submissions", 
               n_remaining = nrow(panel_screen), 
               n_failed = NA) |>
  print()
```

*Function for filtering based on valid values or thresholds*

```{r}
filter_value <- function(data, col, valid = NULL, threshold = NULL, keep_col = FALSE, print = FALSE, num = FALSE) {
  if (num) data <- data |> mutate(!!col := as.numeric(.data[[col]]))

  if (!is.null(threshold)) {
    keep <- \(x) is.na(x) | x >= threshold
    drop <- \(x) !is.na(x) & x < threshold
  } else if (is.na(valid)) {
    keep <- \(x) is.na(x)
    drop <- \(x) !is.na(x)
  } else {
    keep <- \(x) x == valid
    drop <- \(x) x != valid
  }

  flow <<- flow |> full_join(tibble(
    flow        = col,
    n_remaining = data |> filter(keep(.data[[col]])) |> nrow(),
    n_failed    = data |> filter(drop(.data[[col]])) |> nrow()
  ))

  if (print) print(flow, n = 100)

  data |>
    filter(keep(.data[[col]])) |>
    (\(d) if (!keep_col) select(d, -all_of(col)) else d)()
}
```

*Screen-outs*

```{r}
panel_screen <- panel_screen |> 
  filter_value(col = "finished", valid = "True") |>
  
  # Remove previews
  filter_value(col = "distribution_channel", valid = "anonymous") |>
  
  filter_value(col = "q_duplicate_respondent", valid = NA) |> 
  filter_value(col = "q_recaptcha_score", threshold = 0.5, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "all_health_no", valid = FALSE) |> 
  filter_value(col = "eligible_health", valid = "eligible") |> 
  filter_value(col = "audit_score", threshold = 8, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "consent_agree", valid = "I consent to participate and wish to proceed to the survey.") |> 
  filter_value(col = "q1_age", threshold = 18, keep_col = TRUE, num = TRUE) |> 
  filter_value(col = "att_check", valid = TRUE) |>
  
  # Timing thresholds at 400 wpm reading speed
  filter_value(col = "x1_hi_timing_page_submit", threshold = 101, num = TRUE) |> 
  filter_value(col = "x1_hd_timing_page_submit", threshold = 104, num = TRUE) |> 
  filter_value(col = "x1_li_timing_page_submit", threshold = 94, num = TRUE) |> 
  filter_value(col = "x2_hi_timing_page_submit", threshold = 102, num = TRUE) |> 
  filter_value(col = "x2_hd_timing_page_submit", threshold = 104, num = TRUE) |> 
  filter_value(col = "x2_li_timing_page_submit", threshold = 98, num = TRUE) |> 
  filter_value(col = "x3_hi_timing_page_submit", threshold = 102, num = TRUE) |> 
  filter_value(col = "x3_hd_timing_page_submit", threshold = 106, num = TRUE) |> 
  filter_value(col = "x3_li_timing_page_submit", threshold = 98, num = TRUE) |> 
  filter_value(col = "x4_hi_timing_page_submit", threshold = 100, num = TRUE) |> 
  filter_value(col = "x4_hd_timing_page_submit", threshold = 105, num = TRUE) |> 
  filter_value(col = "x4_li_timing_page_submit", threshold = 99, num = TRUE) |> 
  filter_value(col = "tone_timing_page_submit", threshold = 59, num = TRUE, print = TRUE)
```

The panel is now reduced to the final sample size of n = 510.

## Clean and format

*Convert empty strings to NAs, rename demographic cols, tidy responses*

```{r}
panel_clean <- panel_screen |> 
  mutate(
    across(q4_sexual_orientation:q5_race_ethnicity_7_text, ~na_if(.x, ""))
  ) |> 
  rename(dem_age = q1_age,
         dem_sex = q2_sex_at_birth,
         dem_identity = q3_gender_identity,
         dem_orientation = q4_sexual_orientation,
         dem_orientation_other_text = q4_sexual_orientation_6_text,
         dem_race_native_alaskan = q5_race_ethnicity_1, 
         dem_race_asian = q5_race_ethnicity_2,
         dem_race_hispanic = q5_race_ethnicity_3,
         dem_race_hawaiian_pacific = q5_race_ethnicity_4,
         dem_race_black = q5_race_ethnicity_5,
         dem_race_white = q5_race_ethnicity_6,
         dem_race_other = q5_race_ethnicity_7,
         dem_race_other_text = q5_race_ethnicity_7_text,
         dem_education = q6_education, 
         dem_student = q7_student_status,
         dem_income = q8_household_income,
         dem_n_household = q9_people_in_household,
         dem_marital_status = q10_marital_status, 
         dem_minority = q11_un_minoritization,
         grocer_name = q12_grocer_1,  # For geocode later
         grocer_street = q12_grocer_2,# ^
         city = id_location_1,        # ^
         state = id_location_2       # ^^^
         )
```

*Orientation*

- One respondent indicated 'other' with no additional information. This value will be rendered bi/pan as the most likely congruent option.
- Tidy responses.

```{r}
panel_clean |> count(dem_orientation_other_text)
panel_clean <- panel_clean |> select(-dem_orientation_other_text)

panel_clean <- panel_clean |> 
  mutate(
    dem_orientation = case_when(
      dem_orientation ==
        'Asexual' ~ 'asexual',
      dem_orientation ==
        'Heterosexual/Straight' ~ 'straight',
      dem_orientation ==
        'Lesbian/Gay' ~ 'gay_or_lesbian',
      dem_orientation ==
        'Bisexual/Pansexual' ~ 'bisexual_or_pansexual',
      dem_orientation ==
        'None of the above work for me, let me explain:' ~ 'bisexual_or_pansexual'))
```

*Race/Ethnicity*

The Qualtrics export provides a dummy-coded variable for every option from the check-all-that-apply.

- Clean to true/false flags for each option.

- Only one respondent indicated 'other' as Portuguese in addition to White/Caucasian. This has been considered additional information, but not another unique race/ethnic identity for our demographics. 'Other' columns will be removed.

- Only one respondent indicated Hawaiian/Pacific Islander, while also indicating Native American and White. This column will be removed as too specific in favor of Native American which is comparable.

```{r}
panel_clean <- panel_clean |>
  mutate(across(starts_with("dem_race_") & !contains("other"),
                ~ !is.na(.x)))
```

```{r}
panel_clean |> count(dem_race_other_text)
panel_clean |> count(dem_race_hawaiian_pacific)
panel_clean <- panel_clean |> select(-dem_race_other, -dem_race_other_text, -dem_race_hawaiian_pacific)
```

*Gender Identity*

- Many open-response values indicating male/female contained typos. Corrections here are ~hard-coded and may need updating if any new typos emerge in additional responses (510 completes currently)

- One respondent appears to have indicated their age again by mistake for this question. The value will be rendered to an assumption that the respondent is cisgender.

- One respondent each indicated 'Binary' and 'Trans'. 'Binary' in this case may indicate cisgender, or could be a typo of attempting to respond non-binary. These values will be left unchanged, with modelling recipes to consider dropping this variable in favor of solely incorporating sex at birth due to a very low representation of non-cis gender identities.

```{r}
panel_clean |> count(dem_identity)

panel_clean <- panel_clean |> 
  mutate(
    dem_identity = case_when(
      str_detect(dem_identity,
                 regex("^m", ignore_case = TRUE)) ~ "male",
      str_detect(dem_identity,
                 regex("^f", ignore_case = TRUE)) ~ "female",
      str_detect(dem_identity,
                 regex("^w", ignore_case = TRUE)) ~ "female",
      dem_identity == '38' ~ dem_sex,
      TRUE ~ dem_identity))
```

## Finish and save files

*Assign sub-ids #s (instead of response ID strings), remove redundant cols, tidy responses*
```{r}
panel_clean <- panel_clean |> 
  mutate(subid = row_number()) |> 
  relocate(subid) |> 
  select(where(~ n_distinct(., na.rm = FALSE) > 1)) |> 
  mutate(across(c(health_food:dem_orientation,
                  dem_education, dem_student,
                  dem_marital_status, dem_minority,
                  q1_legitimizing_1:q6_formality_1,
                  x1_hi_1_fl_1:x4_li_10_in_1) & where(\(x) is.character(x) | is.factor(x)) &
                  !contains("timing") & !contains("grocer"),
                tidy_responses))
```

*Clean grocery store open-responses for cross-validation*

Many typos and inconsistencies exist within the raw responses for nearest grocery store address (HEB vs. H-E-B, etc.)

- responses will be standardized for the sake of EDA and improving geocode accuracy.

```{r}
grocer_name_stds <- c(
  # --- Walmart ---
  "(?i)^super\\s*wal[\\s-]*mart$"      = "Walmart Supercenter",
  "(?i)^walmart\\s*supercenter$"        = "Walmart Supercenter",
  "(?i)^wal[\\s-]*m[ao]?r?t$"          = "Walmart",
  "(?i)^wall\\s*mart$"                  = "Walmart",
  "(?i)^walm[ao]t$"                     = "Walmart",
  "(?i)^walmart,\\s*.+"                 = "Walmart",   # name field contains address
  # --- Kroger ---
  "(?i)^kri[ao]?ger['s]*$"             = "Kroger",
  "(?i)^kroger['s]*$"                  = "Kroger",
  # --- H-E-B ---
  "(?i)^h[\\.\\s]*e[\\.\\s]*b[\\.\\s]*(store)?$" = "H-E-B",
  "(?i)^heb$"                           = "H-E-B",
  # --- Hy-Vee ---
  "(?i)^hy[-\\s]*vee$"                  = "Hy-Vee",
  "(?i)^hyvee$"                         = "Hy-Vee",
  # --- Food Lion ---
  "(?i)^food[-\\s]*lion$"               = "Food Lion",
  # --- Dollar General ---
  "(?i)^dollar\\s*general$"             = "Dollar General",
  # --- Family Dollar ---
  "(?i)^family\\s*dollar$"              = "Family Dollar",
  # --- Trader Joe's ---
  "(?i)^trader['s]*\\s*joe['s]*$"       = "Trader Joe's",
  # --- Costco ---
  "(?i)^cos[t]?co$"                     = "Costco",
  # --- ShopRite ---
  "(?i)^shop[\\s-]*rite$"               = "ShopRite",
  "(?i)^shoperite$"                     = "ShopRite",
  # --- Winn-Dixie ---
  "(?i)^winn[\\s-]*dixie$"              = "Winn-Dixie",
  # --- Aldi ---
  "(?i)^aldi['s]*$"                     = "Aldi",
  # --- Piggly Wiggly ---
  "(?i)^piggly\\s*wiggly$"              = "Piggly Wiggly",
  # --- Whole Foods ---
  "(?i)^whole\\s*foods(\\s*market)?$"   = "Whole Foods",
  # --- Target ---
  "(?i)^targer$"                        = "Target",
  # --- 7-Eleven ---
  "(?i)^7[\\s-]*eleven$"                = "7-Eleven",
  "(?i)^seven\\s*eleven$"               = "7-Eleven",
  # --- Stater Bros ---
  "(?i)^stater\\s*br(os?|others)$"      = "Stater Bros",
  # --- Stop & Shop ---
  "(?i)^stop\\s*(and|&)\\s*shop$"       = "Stop & Shop",
  # --- Market Basket ---
  "(?i)^market\\s*basket$"              = "Market Basket",
  # --- Food City ---
  "(?i)^food[-\\s]*city$"               = "Food City",
  # --- Save-A-Lot ---
  "(?i)^sav[e]?[-\\s]*a[-\\s]*lot$"     = "Save-A-Lot",
  # --- WinCo ---
  "(?i)^winco[s]?$"                     = "WinCo",
  # --- Harris Teeter ---
  "(?i)^harris\\s*teeter$"              = "Harris Teeter",
  # --- Amazon Fresh ---
  "(?i)^amazon(\\s*fresh)?$"            = "Amazon Fresh",
  # --- IGA ---
  "(?i)^iga$"                           = "IGA",
  # --- Cub Foods ---
  "(?i)^cub(\\s*foods)?$"               = "Cub Foods",
  # --- Star Market ---
  "(?i)^star[-\\s]?market$"             = "Star Market",
  # --- Fred Meyer ---
  "(?i)^fred\\s*m[ey]+r[s]?$"           = "Fred Meyer",
  # --- Hannaford ---
  "(?i)^hann[ai]?ford$"                 = "Hannaford",
  # --- Brookshire's ---
  "(?i)^brookshire['s]*$"               = "Brookshire's",
  # --- Giant Eagle ---
  "(?i)^giant\\s*eagle$"                = "Giant Eagle",
  # --- Giant (standalone) ---
  "(?i)^giants?$"                       = "Giant",
  # --- Price Chopper ---
  "(?i)^price\\s*chopper$"              = "Price Chopper",
  # --- Pick 'N Save ---
  "(?i)^pick[\\s'-]*n[\\s'-]*save$"     = "Pick 'N Save",
  # --- BJ's ---
  "(?i)^bj['s]*(\\s*wholesale\\s*club)?$" = "BJ's",
  # --- Safeway ---
  "(?i)^saf[ae]?way$"                   = "Safeway",
  # --- Big Y ---
  "(?i)^big\\s*y$"                      = "Big Y",
  # --- Smith's ---
  "(?i)^smith['s]+$"                    = "Smith's",
  # --- Jewel ---
  "(?i)^jewels?$"                       = "Jewel",
  # --- Ralphs ---
  "(?i)^ralphs?$"                       = "Ralphs",
  # --- Tom Thumb ---
  "(?i)^tom\\s*thumb$"                  = "Tom Thumb",
  # --- Sun Fresh ---
  "(?i)^sun\\s*fresh$"                  = "Sun Fresh",
  # --- Case-only fixes (must be last) ---
  "(?i)^publix$"   = "Publix",
  "(?i)^safeway$"  = "Safeway",
  "(?i)^target$"   = "Target",
  "(?i)^ingles$"   = "Ingles",
  "(?i)^vons$"     = "Vons",
  "(?i)^sprouts$"  = "Sprouts",
  "(?i)^wegmans$"  = "Wegmans",
  "(?i)^meijer$"   = "Meijer",
  "(?i)^lidl$"     = "Lidl",
  "(?i)^schnucks$" = "Schnucks",
  "(?i)^albertsons$"    = "Albertsons",
  "(?i)^haggens?$"      = "Haggen",
  "(?i)^festival\\s*foods$" = "Festival Foods",
  "(?i)^fresh\\s*market$"   = "Fresh Market",
  "(?i)^smart\\s*(and|&)\\s*final.*" = "Smart & Final",
  "(?i)^fry's\\s*food\\s*store$"     = "Fry's",
  "(?i)^save\\s*mart$"               = "Save Mart"
)

state_abbrev_stds <- c(
  "(?i)^AL$" = "Alabama",        "(?i)^AK$" = "Alaska",
  "(?i)^AZ$" = "Arizona",        "(?i)^AR$" = "Arkansas",
  "(?i)^CA$" = "California",     "(?i)^CO$" = "Colorado",
  "(?i)^CT$" = "Connecticut",    "(?i)^DE$" = "Delaware",
  "(?i)^FL$" = "Florida",        "(?i)^GA$" = "Georgia",
  "(?i)^HI$" = "Hawaii",         "(?i)^ID$" = "Idaho",
  "(?i)^IL$" = "Illinois",       "(?i)^IN$" = "Indiana",
  "(?i)^IA$" = "Iowa",           "(?i)^KS$" = "Kansas",
  "(?i)^KY$" = "Kentucky",       "(?i)^LA$" = "Louisiana",
  "(?i)^ME$" = "Maine",          "(?i)^MD$" = "Maryland",
  "(?i)^MA$" = "Massachusetts",  "(?i)^MI$" = "Michigan",
  "(?i)^MN$" = "Minnesota",      "(?i)^MS$" = "Mississippi",
  "(?i)^MO$" = "Missouri",       "(?i)^MT$" = "Montana",
  "(?i)^NE$" = "Nebraska",       "(?i)^NV$" = "Nevada",
  "(?i)^NH$" = "New Hampshire",  "(?i)^NJ$" = "New Jersey",
  "(?i)^NM$" = "New Mexico",     "(?i)^NY$" = "New York",
  "(?i)^NC$" = "North Carolina", "(?i)^ND$" = "North Dakota",
  "(?i)^OH$" = "Ohio",           "(?i)^OK$" = "Oklahoma",
  "(?i)^OR$" = "Oregon",         "(?i)^PA$" = "Pennsylvania",
  "(?i)^RI$" = "Rhode Island",   "(?i)^SC$" = "South Carolina",
  "(?i)^SD$" = "South Dakota",   "(?i)^TN$" = "Tennessee",
  "(?i)^TX$" = "Texas",          "(?i)^UT$" = "Utah",
  "(?i)^VT$" = "Vermont",        "(?i)^VA$" = "Virginia",
  "(?i)^WA$" = "Washington",     "(?i)^WV$" = "West Virginia",
  "(?i)^WI$" = "Wisconsin",      "(?i)^WY$" = "Wyoming",
  "(?i)^DC$" = "District of Columbia"
)

panel_clean <- panel_clean |>
  mutate(
    # Normalize curly apostrophes, then standardize name
    grocer_name = str_replace_all(grocer_name, "\u2019", "'") |> str_squish(),
    grocer_name = str_replace_all(grocer_name, grocer_name_stds),
    # Expand state abbreviations to full names before building address
    state = str_replace_all(state, state_abbrev_stds),
    grocer_address = str_squish(
      paste(grocer_name, grocer_street, city, state, sep = " "))
  )

# Remove junk phrases from the full address string
remove_phrases <- regex(
  paste(
    "its in",
    "i dont know",
    "don't know",
    "not sure",
    "bronx n\\.y",
    "ottumwa iowa",
    sep = "|"
  ),
  ignore_case = TRUE
)

# Address-level fixes (duplicates, formatting, etc.)
address_fixes <- c(
  "(?i)tell13"                                                                    = "tell 13",
  "(?i)2800arapahoe"                                                              = "2800 Arapahoe",
  "(?i)Kroger, Kroger, Junction city, Ky"                                         = "Kroger, Junction city, Ky",
  "(?i)Smart and final on Arlington, Walmart on Van Buren, Riverside, California" = "Smart and final, Arlington, Riverside, California",
  "(?i)Walmart, Eisenhower dr., Aldi, Eisenhower dr., Hanover, PA"                = "Walmart, Eisenhower dr., Hanover, PA",
  "(?i)Walmart, 1010 112th St Amory MS, Amory, MS"                                = "Walmart, 1010 112th St, Amory, MS",
  "(?i)24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL 60104, United States, Chicago, IL"  = "24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL"
)

panel_clean <- panel_clean |>
  mutate(
    grocer_address = str_replace_all(grocer_address, "\u2019", "'"),
    grocer_address = grocer_address |>
      str_remove_all(remove_phrases) |>
      str_replace_all(address_fixes) |>
      str_squish()
  ) |> 
  relocate(city, .after = grocer_street) |> 
  relocate(state, .after = city) |>
  relocate(grocer_address, .after = state)
  
```

*Save wide format panel with all information for EDA/CV*
```{r}
panel_clean |> write_csv(here::here(path_processed, str_c("panel_wide_", format(Sys.Date(), "%Y_%m_%d"), ".csv")))
```

## Long Formatting

```{r}
panel_long <- panel_clean |>
  select(subid, dem_age:dem_minority, q1_legitimizing_1:q6_formality_1,
         `x1_hi_1_fl_1`:`x4_li_10_in_1`,
         -contains("timing"), -contains("attention")) |>
  pivot_longer(
    cols= `x1_hi_1_fl_1`:`x4_li_10_in_1`,
    values_to = "message_rating",
    names_to = "message_type") |>
  separate(message_type,
    sep = "_", into = c(
      "survey_version", "context", "q_num", "tone_style"),
    extra = "drop") |> 
  mutate(
    style = if_else(substr(tone_style, 1, 1) == "f", "formal", "informal"),
    tone = case_when(
      substr(tone_style, 2, 2) == "l" ~ "legitimizing",
      substr(tone_style, 2, 2) == "n" ~ "norms",
      substr(tone_style, 2, 2) == "s" ~ "self_efficacy",
      substr(tone_style, 2, 2) == "a" ~ "acknowledging",
      substr(tone_style, 2, 2) == "v" ~ "value_affirmation"),
    context = case_when(
      context == "hi" ~ "high_increasing",
      context == "hd" ~ "high_decreasing",
      context == "li" ~ "low_increasing")
    ) |>
  select(-q_num, -tone_style) |> 
  filter(!is.na(message_rating),
         str_trim(message_rating) != "")
```

*Save file for modelling*

```{r}
panel_clean |> write_csv(here::here(path_processed, str_c("panel_long_", format(Sys.Date(), "%Y_%m_%d"), ".csv")))
```
