---
title: "Create Panel"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

Fully functional, not the cleanest still.

-   Left previously commented out code alone.

## Purpose

-   Review incoming panel data
-   Remove dropouts by screening method:
    -   Unfinished
    -   Previews
    -   Duplicate Responses
    -   CAPTCHA fails
    -   Healthy screen fails
    -   AUDIT fails
    -   Consent declines
    -   Age fails
    -   Attention check fails
    -   Timing check fails
-   Clean predictors and pivot to long format for modeling

## Set up

```{r}
#| include: false

library(tidyverse) 
options(conflicts.policy = "depends.ok")

source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/get_credentials.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/download_qualtrics.R?raw=true")
# source("https://github.com/jjcurtin/lab_support/blob/main/fun_gps.R?raw=true")

# source function file
# source("functions/fun_opt.R")
# path_qualtrics <- format_path("optimize/data_raw/qualtrics")

path_panel <- format_path("llmpanel/data_raw/panel")
path_processed <- format_path("llmpanel/data_processed")
path_credentials <- format_path("other")
```

*Get credentials*

```{r}
token_qualtrics <- get_credentials("qualtrics",
  here::here(path_credentials, "credentials.csv")) |>
  pull(token)
```

*Download results by API and clean variable names*

```{r}
panel_export_raw <- NULL

# Retry on intermittent 404s from Qualtrics until a successful download. 

repeat {
  panel_export_raw <- tryCatch(
    {download_qualtrics(
        survey_id = "SV_dbAKSR75ATWSo2q",
        api_token = token_qualtrics,
        display_progress = FALSE)
      },
    error = function(e) {
      if (str_detect(conditionMessage(e), "404")) {
        message("Qualtrics returned 404. Retrying in 5 seconds...")
        Sys.sleep(5)
        return(NULL)}
      stop(e)
      })
  if (!is.null(panel_export_raw)) {break}
  }


#FIX HERE!!!!
panel_export_raw <- panel_export_raw |>
  janitor::clean_names("snake")  |> # Fix health survey variables
  rename(health_brush = health_floss,
         health_drink = x47280739
         ) |> view()
  select(-c(q89, description,intro_tone, intro_context, # remove text intro variables
            x, x_1, x_2, x_3, x_4, x_5, x_6, x_7, x_8, x_9, x_10,x_11)
         ) |>
    rename_with(~ str_replace_all(.x, pattern = ("^x"), replacement ="")) |>
    rename_with(~ str_replace_all(.x, pattern = "_1$", replacement ="")) |>
  rename(audit_1 = audit) #fix one that got caught by the rename 
```

*Clean randomizer variables for easier reading (although I'm still leaving them in the dataframe)*

```{r}
randomizer_vars <- panel_export_raw |>
  select(response_id, starts_with("ro_"), starts_with("block_order")) |> 
  rename(tone_message_ro   = ro_br_fl_99,
         survey_version_ro = ro_br_fl_12,
         survey1_block_ro  = ro_br_fl_85,
         survey2_block_ro  = ro_br_fl_23,
         survey3_block_ro  = ro_br_fl_35,
         survey4_block_ro  = ro_br_fl_47
         ) |>
  mutate(
    tone_message_ro = if_else(
      tone_message_ro == "FL_146|FL_98", "tone first", "messages first"),
    survey_version_ro = case_when(
      survey_version_ro == "FL_81" ~ 1,
      survey_version_ro == "FL_82" ~ 2,
      survey_version_ro == "FL_83" ~ 3,
      survey_version_ro == "FL_84" ~ 4),
    across(survey1_block_ro:survey4_block_ro,
           ~ str_replace_all(string = .x,
                             pattern = "FL_86|FL_70|FL_59|FL_48",
                             replacement = "hi")),
    across(survey1_block_ro:survey4_block_ro,
           ~ str_replace_all(string = .x,
                             pattern = "FL_87|FL_71|FL_60|FL_49",
                             replacement = "hd")),
    across(survey1_block_ro:survey4_block_ro,
           ~ str_replace_all(string = .x,
                             pattern = "FL_88|FL_72|FL_61|FL_50",
                             replacement = "li"))
         ) |>
  unite(
    context_order, survey1_block_ro:survey4_block_ro, sep = "") |>
  mutate(
    block_1 = case_when(
      tone_message_ro == "tone first" ~ "tone",
      tone_message_ro == "messages first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, 1,2)),
      .default = ""),
    block_2 = case_when(
      tone_message_ro == "tone first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, 1,2)),
      tone_message_ro == "messages first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, 4,5)),
      .default = ""),
    block_3 = case_when(
      tone_message_ro == "tone first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, 4,5)),
      tone_message_ro == "messages first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, -2)),
      .default = ""),
    block_4 = case_when(
      tone_message_ro == "messages first" ~ "tone",
      tone_message_ro == "tone first" ~ str_c(
        survey_version_ro, "_", str_sub(context_order, -2)),
      .default = "")
    )
# rejoin to main dataframe
panel_export <- panel_export_raw |>
  left_join(randomizer_vars)
```

*There ARE variables in the export that aren't in the API download. Use the download to add them back in.*

```{r}
panel_download <- read_csv(
  tibble(
    path = list.files(path_panel,
                      pattern = "^panel_2026",
                      full.names = TRUE)) |>
    mutate(
      mdate = file.mtime(path)) |>
    filter(mdate == max(mdate)) |>
    pull(path)) |> tail(-2) |> 
  janitor::clean_names("snake")  |> 
  rename(
    health_brush = health_floss,
    health_drink = x47280739) |>
  select(
    response_id,
    q_recaptcha_score,
    q_duplicate_respondent)

panel_export <- panel_export |>
  left_join(panel_download)
```

## Filtering by screenout

*Start a tibble to track participant flow now that we've removed the most basic non-real responses*

```{r}
panel_clean <- panel_export

flow <- tibble(flow = "total_submissions", 
               n_passed = nrow(panel_clean), 
               n_failed = NA) |> print()
```

### Finished surveys

```{r}
# remove incomplete submissions and update flow
flow <- flow |>
  full_join(tibble(flow = "finished", 
                   n_passed = nrow(panel_clean |>
                                     filter(finished == "1")), 
                   n_failed = nrow(panel_clean |>
                                     filter(finished == "0") ))) |>
  print()

panel_clean <- panel_clean |> filter(finished == "1") 
```

### Previews

```{r}
flow <- flow |>
  full_join(tibble(flow = "preview", 
                   n_passed = nrow(panel_clean |>
                                     filter(q_chl  == "anonymous")), 
                   n_failed = nrow(panel_clean |>
                                     filter(q_chl  == "preview") ))) |>
  print()
#remove previews
panel_clean <- panel_clean |> 
  filter(q_chl != "preview") 
```

### Duplicate responses

Note: Email from Qualtrics 2026_0225 states they removed q_duplicate_respondent and now are only using q_ballot_box_stuffing to show duplicates.

HOWEVER, all values of q_ballot_box_stuffing are NA. I will use the downloaded extra variables for now, which may be incomplete, and then continue to yell at qualtrics to provide me with valid information, since they seem to consistently ignore those requests.

```{r}
flow <- flow |> full_join(
  tibble(flow = "duplicate respondents (not available by API)", 
         n_passed = panel_clean |>
           filter(is.na(q_duplicate_respondent)) |> nrow(),
         n_failed = panel_clean |>
           filter(q_duplicate_respondent == "true") |> nrow())) |>
  print()

#remove duplicates
panel_clean <- panel_clean |> 
  filter(is.na(q_duplicate_respondent))
```

### Recaptcha score

-   This variable is also missing from API pulls.
-   We are keeping NA values (they took a captcha from the panel provider before hitting our survey) and values \> .5

```{r}
flow <- flow |> full_join(
  tibble(flow = "captcha (not available by API)",
         n_passed = panel_clean |>
           filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5) |> nrow(),
         n_failed = panel_clean |>
           filter(q_recaptcha_score <.5) |> nrow())) |>
  print()

#remove captcha fails
panel_clean <- panel_clean |> 
  filter(is.na(q_recaptcha_score) | q_recaptcha_score >= .5)
```

### Health Screener

```{r}
#add some summary variable
panel_clean <- panel_clean |> 
  mutate(
    all_no = health_food == "No" &
      health_brush == "No" &
      health_sleep == "No" &
      health_drink == "No" &
      health_water == "No") |>
  mutate(
    eligible_health = if_else(
      health_drink == "No" & !all_no, "eligible", "ineligible")) 

# All no's
flow <- flow |> full_join(
  tibble(flow = "health screener - all No's",
         n_passed = panel_clean |> filter(!all_no) |> nrow(),
         n_failed = panel_clean |> filter(all_no) |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(!all_no) 

# non drinkers
flow <- flow |> full_join(
  tibble(flow = "health screener - non-binge drinker",
         n_passed = panel_clean |>
           filter(eligible_health == "eligible") |> nrow(),
         n_failed = panel_clean |>
           filter(eligible_health == "ineligible") |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(eligible_health == "eligible")
```

### AUDIT Screener

```{r}
flow <- flow |> full_join(
  tibble(flow = "AUDIT screener",
         n_passed = panel_clean |>
           filter(audit_score >= 8) |> nrow(),
         n_failed = panel_clean |>
           filter(audit_score < 8) |> nrow())) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(audit_score >= 8)
```

### Consent

```{r}
flow <- flow |> full_join(
  tibble(flow = "consented",
         n_passed = panel_clean |> filter(
           consent_agree == "I consent to participate and wish to proceed to the survey.") |> nrow(),
         n_failed = panel_clean |> 
           filter(consent_agree == "I wish to exit the survey without providing consent.") |> nrow())
  )|>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(consent_agree == "I consent to participate and wish to proceed to the survey.") 
```

### Age

Has anyone got this far who was under 18 and screened out on demographics?

```{r}
panel_clean <- panel_clean |>
  mutate(q1_age = as.numeric(q1_age))

flow <- flow |> full_join(
  tibble(flow = "over 18",
         n_passed = panel_clean |> 
           filter(q1_age >=18) |> nrow(),
         n_failed = panel_clean |> 
           filter(q1_age <18) |> nrow())
  )|>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(q1_age >=18) 
```

### Per-block failures

*Set up thresholds and pull our attention and timing variables*

```{r}
#| echo: false

#get timing thresholds
timing <- tibble(block = c(
"tone", 
"1_hi", "1_hd", "1_li",
"2_hi", "2_hd", "2_li", 
"3_hi", "3_hd", "3_li", 
"4_hi", "4_hd", "4_li"
),
threshold = c(
59,
101, 104, 94,
102, 104, 98,
102, 106, 98,
100, 105, 99
),
max_100 = c(
235,
405, 417, 375,
406, 414, 393,
410, 422, 394,
400, 419, 397)
)
panel_integrity <- panel_clean |>
  select(response_id,
         contains((c("timing_2","attention"))),
         starts_with("block_order"),
         tone_order, survey_order, survey_version, block_1:block_4
         ) |>
  rename_with(~ str_replace_all(.x, pattern = "_timing_2", replacement =""))
```

*Block 1 fails (Timing only)*

```{r}
block1 <- panel_integrity |>
  rowwise() |>
  mutate(block_1_timing = (
    panel_integrity |> 
      select(ends_with(block_1)) |> 
      filter(response_id == panel_integrity$response_id) |> pull()
    ),
    block_1_threshold = if_else(
      is.na(block_1), NA, timing$threshold[timing$block == block_1]
      ),
    block1_timing_fail = block_1_timing < block_1_threshold)

flow <- flow |> full_join(
  tibble(flow = "block1 timing", 
         n_passed = panel_clean |> 
           filter(response_id %in% (
             block1 |> filter(!block1_timing_fail) |>
               pull(response_id))) |> nrow(),
         n_failed = panel_clean |> filter(response_id %in% (
             block1 |> filter(block1_timing_fail) |>
               pull(response_id))) |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block1 |>
                              filter(!block1_timing_fail) |>
                              pull(response_id)))
```

*Block 2 Timing:*

```{r}
block2 <- panel_integrity |>
  filter(response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(
    block_2_timing = panel_integrity |> 
      select(ends_with(block_2)) |> 
      filter(response_id == panel_integrity$response_id) |>
      pull(),
    block_2_threshold = if_else(
      is.na(block_2), NA, timing$threshold[timing$block == block_2]
      ),
    block2_timing_fail = block_2_timing < block_2_threshold,
    block_2_attention = panel_integrity |> 
      select(starts_with(block_2) & ends_with("_attention")) |> 
      filter(response_id == panel_integrity$response_id) |> pull()
    )

flow <- flow |> full_join(
  tibble(flow = "block2 timing",
         n_passed = panel_clean |> filter(response_id %in% (
           block2 |> filter(!block2_timing_fail) |>pull(response_id))
           ) |> nrow(),
         n_failed = panel_clean |> filter(response_id %in% (
           block2 |> filter(block2_timing_fail) |> pull(response_id))
           ) |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> filter(
  response_id %in% (block2 |> filter(!block2_timing_fail) |> pull(response_id)))
```

*Block 2 Attention:*

```{r}
flow <- flow |> full_join(
  tibble(flow = "block2 attention",
         n_passed = panel_clean |> filter(
           response_id %in% (block2 |> filter(
             block_2_attention == "Strongly Disagree" || block_2_attention == "") |>
               pull(response_id))) |> nrow(),
         n_failed = panel_clean |> filter(
           response_id %in% (block2 |> filter(
             block_2_attention != "Strongly Disagree" && !(block_2_attention == "")) |>
               pull(response_id)))  |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> filter(
  response_id %in% (block2 |> filter(
    block_2_attention == "Strongly Disagree" || block_2_attention == "") |>
      pull(response_id)))
```

*Block 3 Timing:*

```{r}
block3 <- panel_integrity |> filter(
  response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(
    block_3_timing = panel_integrity |> 
           select(ends_with(block_3)) |> 
           filter(response_id == panel_integrity$response_id) |> pull(),
         block_3_threshold = if_else(
           is.na(block_3), NA, timing$threshold[timing$block == block_3]),
         block3_timing_fail = block_3_timing < block_3_threshold,
         block_3_attention = panel_integrity |> 
           select(starts_with(block_3) & ends_with("_attention")) |> 
           filter(response_id == panel_integrity$response_id) |> pull()
    )

flow <- flow |> full_join(
  tibble(flow = "block3 timing",
         n_passed = panel_clean |> filter(response_id %in% (
           block3 |> filter(!block3_timing_fail) |>
             pull(response_id))) |> nrow(),
         n_failed = panel_clean |> filter(response_id %in% (
           block3 |> filter(block3_timing_fail) |>
             pull(response_id))) |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> 
   filter(response_id %in% (block3 |> filter(!block3_timing_fail) |> pull(response_id)))
```

*Block 3 Attention:*

```{r}
flow <- flow |> full_join(
  tibble(flow = "block3 attention", n_passed = panel_clean |> 
           filter(response_id %in% (block3 |>filter(
             block_3_attention == "Strongly Disagree" || block_3_attention == "") |>
               pull(response_id))) |> nrow(),
         n_failed = panel_clean |> 
           filter(response_id %in% (block3 |> filter(
             block_3_attention != "Strongly Disagree" && !(block_3_attention == "")) |>
               pull(response_id)))  |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> filter(
  response_id %in% (block3 |> filter(
    block_3_attention == "Strongly Disagree" || block_3_attention == "") |>
      pull(response_id)))
```

*Block 4 (Timing only)*

```{r}
block4 <- panel_integrity |> filter(
  response_id %in% panel_clean$response_id) |>
  rowwise() |>
  mutate(
    block_4_timing = panel_integrity |> 
      select(ends_with(block_4)) |> filter(
        response_id == panel_integrity$response_id) |> pull(),
    block_4_threshold = if_else(
      is.na(block_4), NA, timing$threshold[timing$block == block_4]),
    block4_timing_fail = block_4_timing < block_4_threshold
    )

flow <- flow |> full_join(
  tibble(flow = "block4 timing",
         n_passed = panel_clean |> filter(
           response_id %in% (block4 |> filter(
             !block4_timing_fail) |> pull(response_id))) |> nrow(),
         n_failed = panel_clean |> filter(response_id %in% (
           block4 |> filter(block4_timing_fail) |> 
             pull(response_id))) |> nrow())
  ) |>
  print()

#remove 
panel_clean <- panel_clean |> filter(
  response_id %in% (block4 |> filter(!block4_timing_fail) |> pull(response_id)))
```

*Clean some variable names*

```{r}
panel_clean <- panel_clean |> 
  mutate(
    across(q4_sexual_orientation:q5_race_ethnicity_7_text, ~na_if(.x, "")),
    
    dem_orientation = case_when(
      q4_sexual_orientation == 'None of the above work for me, let me explain:'
      ~ 'other',
      q4_sexual_orientation == 'Heterosexual/Straight' ~ 'straight',
      q4_sexual_orientation == 'Lesbian/Gay' ~ 'gay_or_lesbian',
      q4_sexual_orientation == 'Bisexual/Pansexual' ~ 'bisexual_or_pansexual',
      q4_sexual_orientation == 'Asexual' ~ 'asexual'),
    dem_orientation_other_text = if_else(
      q4_sexual_orientation == 'None of the above work for me, let me explain:',
      q4_sexual_orientation_text, NA)
    ) |> select(-q4_sexual_orientation, -q4_sexual_orientation_text) |>
  rowwise() |> 
  mutate(
    sum_race = sum(
      !is.na(q5_race_ethnicity), !is.na(q5_race_ethnicity_2), !is.na(q5_race_ethnicity_4), !is.na(q5_race_ethnicity_5),
      !is.na(q5_race_ethnicity_6))) |> 
  rowwise() |>
  mutate(
    dem_race_multiple = if_else(sum_race > 1,"yes", "no"),
    dem_hispanic = if_else(!is.na(q5_race_ethnicity_3), "yes", "no")) |>
  select(-sum_race, -q5_race_ethnicity_3) |>
  rowwise() |>
  mutate(
    dem_race = case_when(
      !is.na(q5_race_ethnicity) & is.na(dem_race_multiple) ~ q5_race_ethnicity,
      !is.na(q5_race_ethnicity_2) & is.na(dem_race_multiple) ~ q5_race_ethnicity_2,
      !is.na(q5_race_ethnicity_4) & is.na(dem_race_multiple) ~ q5_race_ethnicity_4,
      !is.na(q5_race_ethnicity_5)  & is.na(dem_race_multiple) ~ q5_race_ethnicity_5,
      !is.na(q5_race_ethnicity_6)  & is.na(dem_race_multiple) ~ q5_race_ethnicity_6,
      !is.na(q5_race_ethnicity_7)  & is.na(dem_race_multiple) ~ q5_race_ethnicity_7,
      !is.na(dem_race_multiple) ~ dem_race_multiple,
      !is.na(dem_race_multiple) & is.na(q5_race_ethnicity_7) & !is.na(dem_hispanic) ~ "Hispanic or Latino")) |> 
  rename(dem_age = q1_age,
         dem_sex = q2_sex_at_birth ,
         dem_identity = q3_gender_identity , 
         dem_race_native_alaskan = q5_race_ethnicity, 
         dem_race_asian = q5_race_ethnicity_2 ,
         dem_race_hawaiian_pacific = q5_race_ethnicity_4 ,
         dem_race_black = q5_race_ethnicity_5 ,
         dem_race_white = q5_race_ethnicity_6 ,
         dem_race_other = q5_race_ethnicity_7 ,
         dem_race_other_text = q5_race_ethnicity_7_text ,
         dem_education = q6_education, 
         dem_student = q7_student_status,
         dem_income = q8_household_income,
         dem_n_household = q9_people_in_household,
         dem_marital_status = q10_marital_status, 
         dem_minority = q11_un_minoritization) |> 
    relocate(starts_with("dem_"), .after = consent_agree)
```

---Updated Section--- (everything before has been largely unchanged from cln_panel.qmd aside from tidying)

-   Corrections to open-response typos are hard-coded, would need updating if any new typos emerge in additional responses (510 completes currently)

```{r}
panel_clean <- panel_clean |> 
  mutate(
    dem_race_native_alaskan   = if_else(is.na( dem_race_native_alaskan ), "no", "yes"),
    dem_race_asian            = if_else(is.na(      dem_race_asian     ), "no", "yes"),
    dem_race_hawaiian_pacific = if_else(is.na(dem_race_hawaiian_pacific), "no", "yes"),
    dem_race_black            = if_else(is.na(      dem_race_black     ), "no", "yes"),
    dem_race_white            = if_else(is.na(      dem_race_white     ), "no", "yes"),
    dem_race_other            = if_else(is.na(      dem_race_other     ), "no", "yes"),
    dem_race_multiple = if_else(
      rowSums(across(starts_with("dem_race_"), ~ .x == "yes"), na.rm = TRUE) > 1, "yes", "no"),
    dem_identity = case_when(
      str_detect(dem_identity, regex("^m", ignore_case = TRUE)) ~ "male",
      str_detect(dem_identity, regex("^f", ignore_case = TRUE)) ~ "female",
      str_detect(dem_identity, regex("^w", ignore_case = TRUE)) ~ "female",
      TRUE ~ dem_identity),
    dem_identity_other_text = if_else(
      dem_identity != 'male' & dem_identity != 'female', dem_identity, NA),
    dem_identity = case_when(
      dem_identity == 'male' | dem_identity == 'female' ~ dem_identity,
      dem_identity == '38' ~ NA,
      TRUE ~ 'other'),
    dem_student = if_else(dem_student == "", NA, dem_student),
    q7_user_input = if_else(q7_user_input == "", NA, q7_user_input)
    ) |> 
  relocate(dem_race_multiple, .after = dem_race_white) |>
  relocate(dem_hispanic, .after = dem_race_white) |>
  relocate(dem_identity_other_text, .after = dem_identity) |>
  relocate(dem_orientation, .after = dem_identity_other_text) |> 
  relocate(dem_orientation_other_text, .after = dem_orientation) |> 
  select(-dem_race) # original column redundant
```

*Save wide format panel with all information for EDA*
```{r}
panel_wide <- panel_clean |> ungroup() |> 
  mutate(subid = row_number()) |> 
  relocate(subid) |> 
  select(where(~ n_distinct(., na.rm = FALSE) > 1))

panel_wide |> write_csv(here::here(path_processed, "panel_wide.csv"))
```

## Long Formatting

```{r}
panel_trim <- panel_clean |>
  select(
    response_id,
    dem_age:dem_minority,
    q1_legitimizing:q7_user_input,
    `1_hi_1_fl`:`4_li_10_in`
  ) |>
  select(
    -contains("timing"),
    -contains("attention")
  ) |>
  ungroup() |>
  mutate(
    subid = row_number()
  ) |>
  relocate(subid)

panel_long <- panel_trim |> 
  pivot_longer(
    cols= `1_hi_1_fl`:`4_li_10_in`,
    values_to = "message_rating",
    names_to = "message_type") |>
  separate(
    message_type,
    sep ="_", into = c("survey_version", "context", "q_num", "tone_style")
    ) |> 
  mutate(
    style = substr(tone_style, 1,1),
    tone = substr(tone_style, 2,2),
    style = if_else(
      style == "f", "formal", "informal"),
    tone = case_when(
      tone == "l" ~ "legitimizing",
      tone== "n" ~ "norms",
      tone== "s" ~ "self_efficacy",
      tone== "a" ~ "acknowledging",
      tone== "v" ~ "value_affirmation"),
    context = case_when(
      context == "hi" ~ "high_increasing",
      context== "hd" ~ "high_decreasing",
      context== "li" ~ "low_increasing")
    ) |>
  select(-q_num, -tone_style) |> 
  filter(!is.na(message_rating),
         str_trim(message_rating) != "")
```

*Tidy responses*

```{r}
panel_tidy <- panel_long |>
  mutate(
    across(-c(response_id, dem_income, q7_user_input) & where(is.factor),
      tidy_responses),
    across(-c(response_id, dem_income, q7_user_input) & where(is.character),
      tidy_responses),
    )
```

*Write out eyeball sample*

```{r}
eyeball_ids <- read_csv(here::here(path_processed, "eyeball_ids.csv"))

panel_eyeball <- panel_tidy |> filter(response_id %in% eyeball_ids$eyeball_ids)

panel_eyeball |> write_csv(here::here(path_processed, "panel_eyeball.csv"))
```

*Write out full panel*

```{r}
panel_tidy |> write_csv(here::here(path_processed, str_c("panel_long.csv")))
```
