---
title: "Make/Clean Panel (Flag-Based)"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In development.

## Purpose

1. Basic cleaning of raw API data

2. Flag respondents who either failed to screen into the survey, or failed on
at least one logic check making them ineligible for the final sample. Flagged
responses include:

    -   Previews (Internal test takes of the survey)
    -   reCAPTCHA fails
    -   Healthy Behavior Questionnaire fails
    -   AUDIT fails
    -   Consent declines
    -   Underage fails
    -   Attention check fails
    -   Timing check fails
    -   Unfinished/abandoned responses
    -   Qualtrics-identiified duplicates.
    
3. Identify additional duplicate responses for removal based upon matching IP
addresses and/or identical demographics.

4. Standardization of open-text grocery store data for geocode.

## Setup

```{r}
library(tidyverse) 
options(conflicts.policy = "depends.ok")

source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")

path_raw <- format_path("llmpanel/data_raw")
path_processed <- format_path("llmpanel/data_processed")
```

*Load in data and remove dummy rows*

```{r}
# Load raw API data
panel_raw <- read.csv(here::here(path_raw, "panel_api_raw.csv"))
panel_screen <- panel_raw

# First row in export is a copy of question text.
panel_screen[1,]

# Second row contains Qualtrics question IDs. 
panel_screen[2,]

# Remove:
panel_screen <- panel_screen |> slice(-(1:2))
panel_screen |> head(1) # Good to go
```

*Clean names and add summary variables for screening*

```{r}
panel_screen <- panel_screen |>
  janitor::clean_names("snake")  |>
  
# Clean column names
  rename(health_drink = x47280739,
         dem_age = q1_age,
         dem_sex = q2_sex_at_birth,
         dem_identity = q3_gender_identity,
         dem_orientation = q4_sexual_orientation,
         dem_orientation_other_text = q4_sexual_orientation_6_text,
         dem_race_native_alaskan = q5_race_ethnicity_1, 
         dem_race_asian = q5_race_ethnicity_2,
         dem_race_hispanic = q5_race_ethnicity_3,
         dem_race_hawaiian_pacific = q5_race_ethnicity_4,
         dem_race_black = q5_race_ethnicity_5,
         dem_race_white = q5_race_ethnicity_6,
         dem_race_other = q5_race_ethnicity_7,
         dem_race_other_text = q5_race_ethnicity_7_text,
         dem_education = q6_education, 
         dem_student = q7_student_status,
         dem_income = q8_household_income,
         dem_n_household = q9_people_in_household,
         dem_marital_status = q10_marital_status, 
         dem_minority = q11_un_minoritization,
         grocer_name = q12_grocer_1, 
         grocer_street = q12_grocer_2,
         city = id_location_1, 
         state = id_location_2  
         ) |> 
  
# Health screener variables
  mutate(
    all_health_no =
        health_food == "No" &
        health_floss == "No" &
        health_sleep == "No" &
        health_drink == "No" &
        health_water == "No",
    eligible_health = if_else(
        health_drink == "No" & !all_health_no, "eligible", "ineligible"),
    
# Universal attention check flag
    att_check = if_any(contains("attention"),
                       \(col) col == "Strongly Disagree")) |>
    mutate(term = if_else(att_check & is.na(term), "att_check", term)) |>

# Remove now-redundant attention check columns
  select(-contains("attention"))
```

## Flagging ineligible responses

*Initialize `flag` column — NA means valid*

```{r}
panel_screen <- panel_screen |> 
  mutate(flag = NA_character_)
```

*Start tracking tibble for participant flow*

```{r}
flow <- tibble(flow = "total_submissions", 
               n_remaining = nrow(panel_screen), 
               n_failed = NA_integer_) |>
  print()
```

*Function for flagging based on valid values or thresholds*

Instead of filtering rows out, `flag_value()` writes a reason into the `flag` column.
Only rows not already flagged are evaluated (first failure wins).

```{r}
flag_value <- function(data, col, valid = NULL, threshold = NULL, reason = col, num = FALSE, print = FALSE) {
  if (num) data <- data |> mutate(!!col := as.numeric(.data[[col]]))

  if (!is.null(threshold)) {
    fails <- \(x) !is.na(x) & x < threshold
  } else if (is.na(valid)) {
    fails <- \(x) !is.na(x)
  } else {
    fails <- \(x) is.na(x) | x != valid
  }

  # Only flag rows not already removed
  data <- data |>
    mutate(flag = if_else(is.na(flag) & fails(.data[[col]]), reason, flag))

  flow <<- flow |> bind_rows(tibble(
    flow        = reason,
    n_remaining = sum(is.na(data$flag)),
    n_failed    = sum(data$flag == reason, na.rm = TRUE)
  ))

  if (print) print(flow, n = 100)

  data
}
```

*Flag Responses*

```{r}
# Flag previews
panel_screen <- panel_screen |>
  flag_value(col = "distribution_channel", valid = "anonymous")

# Flag recaptcha failures
panel_screen <- panel_screen |>
  flag_value(col = "q_recaptcha_score", threshold = 0.5, num = TRUE)

# Flag healthy behaviors questionnaire failures
panel_screen <- panel_screen |>
  flag_value(col = "all_health_no", valid = FALSE)

panel_screen <- panel_screen |>
  flag_value(col = "eligible_health", valid = "eligible")

# Flag AUDIT failures
panel_screen <- panel_screen |>
  flag_value(col = "audit_score", threshold = 8, num = TRUE)

# Flag non-consents
panel_screen <- panel_screen |>
  flag_value(col = "consent_agree",
             valid = "I consent to participate and wish to proceed to the survey.")

# Flag under 18 y/o
panel_screen <- panel_screen |>
  flag_value(col = "dem_age", threshold = 18, num = TRUE)

# Flag attention check failures
panel_screen <- panel_screen |>
  flag_value(col = "att_check", valid = TRUE)

# Flag timing check failures (above 400 wpm reading speed)
panel_screen <- panel_screen |>
  flag_value(col = "x1_hi_timing_page_submit", threshold = 101, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x1_hd_timing_page_submit", threshold = 104, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x1_li_timing_page_submit", threshold = 94, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x2_hi_timing_page_submit", threshold = 102, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x2_hd_timing_page_submit", threshold = 104, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x2_li_timing_page_submit", threshold = 98, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x3_hi_timing_page_submit", threshold = 102, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x3_hd_timing_page_submit", threshold = 106, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x3_li_timing_page_submit", threshold = 98, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x4_hi_timing_page_submit", threshold = 100, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x4_hd_timing_page_submit", threshold = 105, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "x4_li_timing_page_submit", threshold = 99, num = TRUE)

panel_screen <- panel_screen |>
  flag_value(col = "tone_timing_page_submit", threshold = 59, num = TRUE)

# NOTE: Important that these next two run after all of the above checks - The
#       function will not overwrite existing values in the 'removed' column,
#       meaning that failures on screening or survey logic take priority.

# Flag abandoned/incomplete responses
panel_screen <- panel_screen |>
  flag_value(col = "finished", valid = "True")

# Flag Qualtrics-identified duplicates
panel_screen <- panel_screen |>
  flag_value(col = "q_duplicate_respondent", valid = NA, print = TRUE)
```

The remaining unflagged sample should be n = 510 responses.

*Convert empty strings to NAs*

```{r}
#panel_screen <- panel_screen |> 
#  mutate(
#    across(q4_sexual_orientation:q5_race_ethnicity_7_text, ~na_if(.x, ""))
```

## Manual detection of duplicates

Qualtrics failed to identify many convincing cases of a single person attempting and/or completing the survey multiple times. First, let's explore cases where a valid respondent in our remaining sample of n = 510 has both a matching IP address and identical demographics to at least 1 other failed response.

* Note: In this case, matching demographics will include all demographics columns excluding open-text fields and dem_minority.

*Define columns to be checked for matching responses*

```{r}
demo_cols <- panel_screen |> select(dem_age:dem_marital_status) |> 
  select(-c(dem_identity, dem_orientation_other_text, dem_race_other_text)) |> 
  names()

text_cols <- c("grocer_name", "grocer_street")
```

*Isolate valid & flagged responses for comparison*

```{r}
valid <- panel_screen |> filter(is.na(flag))
flagged <- panel_screen |> filter(!is.na(flag))
```

### IP + demographic matches between valid and removed responses

```{r}
# Match valid responses to flagged ones sharing same IP + demographics
demo_ip_matches <- inner_join(valid, flagged,
           by = c("ip_address", match_cols),
           suffix = c("_valid", "_flagged"),
           relationship = "many-to-many") |>
  
  # One row per valid response ID within each IP
  group_by(ip_address, valid_id = response_id_valid) |>
  summarise(
    dupe_only = all(flag_flagged == "q_duplicate_respondent"),
    .groups = "drop") |>
  arrange(dupe_only)

demo_ip_matches |> as.data.frame()
```

We are concerned with IPs showing 1 or more additional attempts (before or after the valid response) that failed for any reason other that q_duplicate_respondent.

If all matches found were otherwise valid expect Qualtrics successfully flagged them as duplicate, we will retain the valid response and dismiss the IP as non-suspicious.

All remaining IPs will have open-text responses for grocery store manually reviewed.

*Dismiss non-suspicious IPs and look at grocery store responses*

```{r}
demo_ip_sus <- demo_ip_matches |>
  filter(dupe_only == FALSE) |>
  pull(ip_address) |>
  unique()
```

There should be 17 IPs (each corresponding to an eligible response) marked here for review.

*Review table for remaining suspicious IPs*

```{r}
panel_screen |>
  filter(ip_address %in% demo_ip_sus) |>
  arrange(ip_address, !is.na(flag)) |>
  select(ip_address, response_id, grocer_name, grocer_street, flag) |>
  
# Clean output for repeated IP across rows
  mutate(ip_address = if_else(
    ip_address == lag(ip_address, default = ""), "", ip_address)) |>
  as.data.frame()
```

If the provided grocery store is also a match with at least one failed attempt, the observation will be deemed invalid and marked in a separate file. 13 responses have been flagged for removal from the final sample by this table.

### Demographic only matches between valid and flagged responses

```{r}
demo_only_matches <- inner_join(valid, flagged,
           by = match_cols,
           suffix = c("_valid", "_flagged"),
           relationship = "many-to-many") |>
  filter(ip_address_valid != ip_address_flagged) |>
  group_by(valid_id = response_id_valid) |>
  summarise(dupe_only = all(flag_flagged == "q_duplicate_respondent"),
            .groups = "drop") |>
  arrange(dupe_only)

as.data.frame(demo_summary)
```

This tables should identify 50 eligible responses with a demographic match in the flagged group, this time with new IPs.

*Dismiss non-suspicious IPs and look at grocery store responses*

```{r}
demo_only_sus <- demo_only_matches |>
  filter(dupe_only == FALSE) |>
  pull(valid_id)

seeds <- panel_screen |>
  filter(response_id %in% demo_only_sus) |>
  select(all_of(demo_cols))

# Create matching demographic groups
seed_groups <- seeds |>
  distinct() |>
  mutate(demo_group = row_number())

# Create table for review
panel_screen |>
  semi_join(seeds, by = demo_cols) |> 
  inner_join(seed_groups, by = demo_cols) |>
  
# Sort seeds to top within each group
  mutate(is_seed = response_id %in% demo_only_sus) |>
  arrange(demo_group, desc(is_seed)) |>
  select(demo_group, response_id, ip_address, grocer_name, grocer_street, flag) |>
  mutate(demo_group = as.character(demo_group),
         demo_group = if_else(demo_group == lag(demo_group, default = ""), "", demo_group)) |>
  as.data.frame()
```

Review of this table should identify 9 responses for removal - demographic + grocery store matches with unique IPs

### IP + demographic matches within eligible responses

```{r}
valid |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup() |>
  arrange(ip_address, start_date) |>
  select(response_id, ip_address, grocer_name, grocer_street, start_date) |>
  as.data.frame()
```

Review of this table should identify 6 unique responses for removal - IP + demographics match to a survey completed earlier.

### Demographic only matches within eligible responses

```{r}
valid_seeds <- valid |>
  select(all_of(demo_cols))

valid_seed_groups <- valid_seeds |>
  distinct() |>
  mutate(demo_group = row_number())

valid |>
  semi_join(valid_seeds, by = demo_cols) |> 
  inner_join(valid_seed_groups, by = demo_cols) |>
  group_by(demo_group) |>
  filter(n() > 1) |>
  ungroup() |>
  arrange(demo_group, start_date) |>
  select(demo_group, response_id, ip_address, grocer_name, grocer_street, start_date) |>
  mutate(demo_group = as.character(demo_group),
         demo_group = if_else(demo_group == lag(demo_group, default = ""), "", demo_group)) |>
  as.data.frame()
```



```{r}
valid |>
  group_by(across(all_of(match_cols))) |>
  filter(n() > 1) |>
  ungroup() |>
  select(response_id, ip_address, ip_n) |>
  arrange(ip_address) |>
  as.data.frame()
```


```{r}
valid |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup() |>
  group_by(across(all_of(match_cols))) |>
  mutate(demo_group = cur_group_id()) |>
  ungroup() |>
  arrange(demo_group, ip_address) |>
  select(demo_group, response_id, ip_address, grocer_name, grocer_street, start_date) |>
  mutate(demo_group = if_else(demo_group == lag(demo_group, default = -1L), NA_integer_, demo_group)) |>
  as.data.frame()
```






*Review table for remaining suspicious responses*

Review of this table should identify 6 additional response IDs for removal, matches on all demographics + grocery store with separate IPs.

```{r}
valid |>
  group_by(ip_address) |>
  filter(n() > 1) |>
  ungroup() |>
  group_by(across(all_of(match_cols))) |>
  mutate(demo_group = cur_group_id()) |>
  ungroup() |>
  arrange(demo_group, ip_address) |>
  select(demo_group, response_id, ip_address, grocer_name, grocer_street, start_date) |>
  mutate(demo_group = if_else(demo_group == lag(demo_group, default = -1L), NA_integer_, demo_group)) |>
  as.data.frame()
```

Review of this table should identify 6 responses for removal, each of which are an IP + demographic match of a previously completed survey that failed to automatically flag as a duplicate entry.







```{r}
demo_summary <- inner_join(valid, flagged,
           by = match_cols,
           suffix = c("_valid", "_removed"),
           relationship = "many-to-many") |>
  filter(ip_address_valid != ip_address_removed) |>
  group_by(ip_address = ip_address_valid, valid_id = response_id_valid) |>
  summarise(logic_fail = any(!is.na(term_removed)),
            min_recaptcha = suppressWarnings(min(as.numeric(q_recaptcha_score_removed), na.rm = TRUE)) |> na_if(Inf),
            found_dupe = all(removed_removed == "q_duplicate_respondent"),
            .groups = "drop") |>
  arrange(desc(logic_fail), min_recaptcha, found_dupe)

as.data.frame(demo_summary)
```

```{r}

```






*Within valid responses*
```{r}
valid |>
  group_by(ip_address, across(all_of(match_cols))) |>
  filter(n() > 1) |>
  mutate(ip_n = n()) |>
  ungroup() |>
  select(response_id, ip_address, ip_n) |>
  arrange(ip_address) |>
  as.data.frame()
```



*Orientation*

- One respondent indicated 'other' with no additional information. This value will be rendered bi/pan as the most likely congruent option.
- Tidy responses.

```{r}
panel_clean |> count(dem_orientation_other_text)
panel_clean <- panel_clean |> select(-dem_orientation_other_text)

panel_clean <- panel_clean |> 
  mutate(
    dem_orientation = case_when(
      dem_orientation ==
        'Asexual' ~ 'asexual',
      dem_orientation ==
        'Heterosexual/Straight' ~ 'straight',
      dem_orientation ==
        'Lesbian/Gay' ~ 'gay_or_lesbian',
      dem_orientation ==
        'Bisexual/Pansexual' ~ 'bisexual_or_pansexual',
      dem_orientation ==
        'None of the above work for me, let me explain:' ~ 'bisexual_or_pansexual'))
```

*Race/Ethnicity*

The Qualtrics export provides a dummy-coded variable for every option from the check-all-that-apply.

- Clean to true/false flags for each option.

- Only one respondent indicated 'other' as Portuguese in addition to White/Caucasian. This has been considered additional information, but not another unique race/ethnic identity for our demographics. 'Other' columns will be removed.

- Only one respondent indicated Hawaiian/Pacific Islander, while also indicating Native American and White. This column will be removed as too specific in favor of Native American which is comparable.

```{r}
panel_clean <- panel_clean |>
  mutate(across(starts_with("dem_race_") & !contains("other"),
                ~ !is.na(.x)))
```

```{r}
panel_clean |> count(dem_race_other_text)
panel_clean |> count(dem_race_hawaiian_pacific)
panel_clean <- panel_clean |> select(-dem_race_other, -dem_race_other_text, -dem_race_hawaiian_pacific)
```

*Gender Identity*

- Many open-response values indicating male/female contained typos. Corrections here are ~hard-coded and may need updating if any new typos emerge in additional responses (510 completes currently)

- One respondent appears to have indicated their age again by mistake for this question. The value will be rendered to an assumption that the respondent is cisgender.

- One respondent each indicated 'Binary' and 'Trans'. 'Binary' in this case may indicate cisgender, or could be a typo of attempting to respond non-binary. These values will be left unchanged, with modelling recipes to consider dropping this variable in favor of solely incorporating sex at birth due to a very low representation of non-cis gender identities.

```{r}
panel_clean |> count(dem_identity)

panel_clean <- panel_clean |> 
  mutate(
    dem_identity = case_when(
      str_detect(dem_identity,
                 regex("^m", ignore_case = TRUE)) ~ "male",
      str_detect(dem_identity,
                 regex("^f", ignore_case = TRUE)) ~ "female",
      str_detect(dem_identity,
                 regex("^w", ignore_case = TRUE)) ~ "female",
      dem_identity == '38' ~ dem_sex,
      TRUE ~ dem_identity))
```

## Finish and save files

*Assign sub-ids #s (instead of response ID strings), remove redundant cols, tidy responses*
```{r}
panel_clean <- panel_clean |> 
  mutate(subid = row_number()) |> 
  relocate(subid) |> 
  relocate(removed, .after = subid) |>
  select(health_drink, removed, where(~ n_distinct(., na.rm = FALSE) > 1)) |> 
  mutate(across(c(health_food:dem_orientation,
                  dem_education, dem_student,
                  dem_marital_status, dem_minority,
                  q1_legitimizing_1:q6_formality_1,
                  x1_hi_1_fl_1:x4_li_10_in_1) & where(\(x) is.character(x) | is.factor(x)) &
                  !contains("timing") & !contains("grocer"),
                tidy_responses))
```

*Clean grocery store open-responses for cross-validation*

Many typos and inconsistencies exist within the raw responses for nearest grocery store address (HEB vs. H-E-B, etc.)

- responses will be standardized for the sake of EDA and improving geocode accuracy.

```{r}
grocer_name_stds <- c(
  # --- Walmart ---
  "(?i)^super\\s*wal[\\s-]*mart$"      = "Walmart Supercenter",
  "(?i)^walmart\\s*supercenter$"        = "Walmart Supercenter",
  "(?i)^wal[\\s-]*m[ao]?r?t$"          = "Walmart",
  "(?i)^wall\\s*mart$"                  = "Walmart",
  "(?i)^walm[ao]t$"                     = "Walmart",
  "(?i)^walmart,\\s*.+"                 = "Walmart",   # name field contains address
  # --- Kroger ---
  "(?i)^kri[ao]?ger['s]*$"             = "Kroger",
  "(?i)^kroger['s]*$"                  = "Kroger",
  # --- H-E-B ---
  "(?i)^h[\\.\\s]*e[\\.\\s]*b[\\.\\s]*(store)?$" = "H-E-B",
  "(?i)^heb$"                           = "H-E-B",
  # --- Hy-Vee ---
  "(?i)^hy[-\\s]*vee$"                  = "Hy-Vee",
  "(?i)^hyvee$"                         = "Hy-Vee",
  # --- Food Lion ---
  "(?i)^food[-\\s]*lion$"               = "Food Lion",
  # --- Dollar General ---
  "(?i)^dollar\\s*general$"             = "Dollar General",
  # --- Family Dollar ---
  "(?i)^family\\s*dollar$"              = "Family Dollar",
  # --- Trader Joe's ---
  "(?i)^trader['s]*\\s*joe['s]*$"       = "Trader Joe's",
  # --- Costco ---
  "(?i)^cos[t]?co$"                     = "Costco",
  # --- ShopRite ---
  "(?i)^shop[\\s-]*rite$"               = "ShopRite",
  "(?i)^shoperite$"                     = "ShopRite",
  # --- Winn-Dixie ---
  "(?i)^winn[\\s-]*dixie$"              = "Winn-Dixie",
  # --- Aldi ---
  "(?i)^aldi['s]*$"                     = "Aldi",
  # --- Piggly Wiggly ---
  "(?i)^piggly\\s*wiggly$"              = "Piggly Wiggly",
  # --- Whole Foods ---
  "(?i)^whole\\s*foods(\\s*market)?$"   = "Whole Foods",
  # --- Target ---
  "(?i)^targer$"                        = "Target",
  # --- 7-Eleven ---
  "(?i)^7[\\s-]*eleven$"                = "7-Eleven",
  "(?i)^seven\\s*eleven$"               = "7-Eleven",
  # --- Stater Bros ---
  "(?i)^stater\\s*br(os?|others)$"      = "Stater Bros",
  # --- Stop & Shop ---
  "(?i)^stop\\s*(and|&)\\s*shop$"       = "Stop & Shop",
  # --- Market Basket ---
  "(?i)^market\\s*basket$"              = "Market Basket",
  # --- Food City ---
  "(?i)^food[-\\s]*city$"               = "Food City",
  # --- Save-A-Lot ---
  "(?i)^sav[e]?[-\\s]*a[-\\s]*lot$"     = "Save-A-Lot",
  # --- WinCo ---
  "(?i)^winco[s]?$"                     = "WinCo",
  # --- Harris Teeter ---
  "(?i)^harris\\s*teeter$"              = "Harris Teeter",
  # --- Amazon Fresh ---
  "(?i)^amazon(\\s*fresh)?$"            = "Amazon Fresh",
  # --- IGA ---
  "(?i)^iga$"                           = "IGA",
  # --- Cub Foods ---
  "(?i)^cub(\\s*foods)?$"               = "Cub Foods",
  # --- Star Market ---
  "(?i)^star[-\\s]?market$"             = "Star Market",
  # --- Fred Meyer ---
  "(?i)^fred\\s*m[ey]+r[s]?$"           = "Fred Meyer",
  # --- Hannaford ---
  "(?i)^hann[ai]?ford$"                 = "Hannaford",
  # --- Brookshire's ---
  "(?i)^brookshire['s]*$"               = "Brookshire's",
  # --- Giant Eagle ---
  "(?i)^giant\\s*eagle$"                = "Giant Eagle",
  # --- Giant (standalone) ---
  "(?i)^giants?$"                       = "Giant",
  # --- Price Chopper ---
  "(?i)^price\\s*chopper$"              = "Price Chopper",
  # --- Pick 'N Save ---
  "(?i)^pick[\\s'-]*n[\\s'-]*save$"     = "Pick 'N Save",
  # --- BJ's ---
  "(?i)^bj['s]*(\\s*wholesale\\s*club)?$" = "BJ's",
  # --- Safeway ---
  "(?i)^saf[ae]?way$"                   = "Safeway",
  # --- Big Y ---
  "(?i)^big\\s*y$"                      = "Big Y",
  # --- Smith's ---
  "(?i)^smith['s]+$"                    = "Smith's",
  # --- Jewel ---
  "(?i)^jewels?$"                       = "Jewel",
  # --- Ralphs ---
  "(?i)^ralphs?$"                       = "Ralphs",
  # --- Tom Thumb ---
  "(?i)^tom\\s*thumb$"                  = "Tom Thumb",
  # --- Sun Fresh ---
  "(?i)^sun\\s*fresh$"                  = "Sun Fresh",
  # --- Case-only fixes (must be last) ---
  "(?i)^publix$"   = "Publix",
  "(?i)^safeway$"  = "Safeway",
  "(?i)^target$"   = "Target",
  "(?i)^ingles$"   = "Ingles",
  "(?i)^vons$"     = "Vons",
  "(?i)^sprouts$"  = "Sprouts",
  "(?i)^wegmans$"  = "Wegmans",
  "(?i)^meijer$"   = "Meijer",
  "(?i)^lidl$"     = "Lidl",
  "(?i)^schnucks$" = "Schnucks",
  "(?i)^albertsons$"    = "Albertsons",
  "(?i)^haggens?$"      = "Haggen",
  "(?i)^festival\\s*foods$" = "Festival Foods",
  "(?i)^fresh\\s*market$"   = "Fresh Market",
  "(?i)^smart\\s*(and|&)\\s*final.*" = "Smart & Final",
  "(?i)^fry's\\s*food\\s*store$"     = "Fry's",
  "(?i)^save\\s*mart$"               = "Save Mart"
)

state_abbrev_stds <- c(
  "(?i)^AL$" = "Alabama",        "(?i)^AK$" = "Alaska",
  "(?i)^AZ$" = "Arizona",        "(?i)^AR$" = "Arkansas",
  "(?i)^CA$" = "California",     "(?i)^CO$" = "Colorado",
  "(?i)^CT$" = "Connecticut",    "(?i)^DE$" = "Delaware",
  "(?i)^FL$" = "Florida",        "(?i)^GA$" = "Georgia",
  "(?i)^HI$" = "Hawaii",         "(?i)^ID$" = "Idaho",
  "(?i)^IL$" = "Illinois",       "(?i)^IN$" = "Indiana",
  "(?i)^IA$" = "Iowa",           "(?i)^KS$" = "Kansas",
  "(?i)^KY$" = "Kentucky",       "(?i)^LA$" = "Louisiana",
  "(?i)^ME$" = "Maine",          "(?i)^MD$" = "Maryland",
  "(?i)^MA$" = "Massachusetts",  "(?i)^MI$" = "Michigan",
  "(?i)^MN$" = "Minnesota",      "(?i)^MS$" = "Mississippi",
  "(?i)^MO$" = "Missouri",       "(?i)^MT$" = "Montana",
  "(?i)^NE$" = "Nebraska",       "(?i)^NV$" = "Nevada",
  "(?i)^NH$" = "New Hampshire",  "(?i)^NJ$" = "New Jersey",
  "(?i)^NM$" = "New Mexico",     "(?i)^NY$" = "New York",
  "(?i)^NC$" = "North Carolina", "(?i)^ND$" = "North Dakota",
  "(?i)^OH$" = "Ohio",           "(?i)^OK$" = "Oklahoma",
  "(?i)^OR$" = "Oregon",         "(?i)^PA$" = "Pennsylvania",
  "(?i)^RI$" = "Rhode Island",   "(?i)^SC$" = "South Carolina",
  "(?i)^SD$" = "South Dakota",   "(?i)^TN$" = "Tennessee",
  "(?i)^TX$" = "Texas",          "(?i)^UT$" = "Utah",
  "(?i)^VT$" = "Vermont",        "(?i)^VA$" = "Virginia",
  "(?i)^WA$" = "Washington",     "(?i)^WV$" = "West Virginia",
  "(?i)^WI$" = "Wisconsin",      "(?i)^WY$" = "Wyoming",
  "(?i)^DC$" = "District of Columbia"
)

panel_clean <- panel_clean |>
  mutate(
    # Normalize curly apostrophes, then standardize name
    grocer_name = str_replace_all(grocer_name, "\u2019", "'") |> str_squish(),
    grocer_name = str_replace_all(grocer_name, grocer_name_stds),
    # Expand state abbreviations to full names before building address
    state = str_replace_all(state, state_abbrev_stds),
    grocer_address = str_squish(
      paste(grocer_name, grocer_street, city, state, sep = " "))
  )

# Remove junk phrases from the full address string
remove_phrases <- regex(
  paste(
    "its in",
    "i dont know",
    "don't know",
    "not sure",
    "bronx n\\.y",
    "ottumwa iowa",
    sep = "|"
  ),
  ignore_case = TRUE
)

# Address-level fixes (duplicates, formatting, etc.)
address_fixes <- c(
  "(?i)tell13"                                                                    = "tell 13",
  "(?i)2800arapahoe"                                                              = "2800 Arapahoe",
  "(?i)Kroger, Kroger, Junction city, Ky"                                         = "Kroger, Junction city, Ky",
  "(?i)Smart and final on Arlington, Walmart on Van Buren, Riverside, California" = "Smart and final, Arlington, Riverside, California",
  "(?i)Walmart, Eisenhower dr., Aldi, Eisenhower dr., Hanover, PA"                = "Walmart, Eisenhower dr., Hanover, PA",
  "(?i)Walmart, 1010 112th St Amory MS, Amory, MS"                                = "Walmart, 1010 112th St, Amory, MS",
  "(?i)24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL 60104, United States, Chicago, IL"  = "24 Hours Food Mart Grocery Store, 500 Mannheim Rd, Bellwood, IL"
)

panel_clean <- panel_clean |>
  mutate(
    grocer_address = str_replace_all(grocer_address, "\u2019", "'"),
    grocer_address = grocer_address |>
      str_remove_all(remove_phrases) |>
      str_replace_all(address_fixes) |>
      str_squish()
  ) |> 
  relocate(city, .after = grocer_street) |> 
  relocate(state, .after = city) |>
  relocate(grocer_address, .after = state)
  
```

*Save full dataset with `removed` column*
```{r}
panel_clean |> write_csv(here::here(path_processed,"panel_full.csv"))
```
