---
title: "Investigate Duplicate Respondents"
format: 
  html:
    page-layout: full
    self-contained: true
    toc: true
    toc-depth: 3
execute: 
  warning: false
editor_options: 
  chunk_output_type: console
---

## Code Status

In Progress, expected to be joined onto mak_panel upon completion.

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
has_term <- panel_raw |>
  filter(!is.na(term)) |>
  select(IPAddress, ResponseId, term, Q1_Age, Q2_SexAtBirth)

no_term_dup <- panel_raw |>
  filter(is.na(term), Q_DuplicateRespondent == "true") |>
  select(IPAddress, ResponseId, Q1_Age, Q2_SexAtBirth)

inner_join(has_term, no_term_dup,
           by = c("IPAddress", "Q1_Age", "Q2_SexAtBirth"),
           suffix = c("_with_term", "_no_term")) |>
  select(
    SharedIP = IPAddress,
    ResponseId_with_term,
    ResponseId_no_term,
    term
  )
```

You can add options to executable code like this

```{r}
match_cols <- names(panel_raw)[
  which(names(panel_raw) == "Q1_Age"):which(names(panel_raw) == "Q11_UnMinoritization")
]

# Pool valid-term and flagged-duplicate observations
all_candidates <- bind_rows(
  panel_raw |>
    filter(!is.na(term)) |>
    select(IPAddress, ResponseId, term, all_of(match_cols)) |>
    mutate(group = "with_term"),
  panel_raw |>
    filter(is.na(term), Q_DuplicateRespondent == "true") |>
    select(IPAddress, ResponseId, term, all_of(match_cols)) |>
    mutate(group = "no_term")
)

# Keep only demographic profiles shared by exactly 2 observations
profile_exact2 <- all_candidates |>
  group_by(across(all_of(match_cols))) |>
  mutate(n_in_profile = n()) |>
  ungroup() |>
  filter(n_in_profile == 2)

inner_join(
  profile_exact2 |> filter(group == "with_term"),
  profile_exact2 |> filter(group == "no_term"),
  by = match_cols,
  suffix = c("_with_term", "_no_term")
) |>
  filter(IPAddress_with_term != IPAddress_no_term) |>
  select(
    IP_with_term = IPAddress_with_term,
    IP_no_term = IPAddress_no_term,
    ResponseId_with_term,
    ResponseId_no_term,
    term = term_with_term
  )
```

The `echo: false` option disables the printing of code (only output is displayed).
