---
title: "Descriptives"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 2
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
params:
  version: "v5"
---

## Setup
```{r}
#| include: false

library(tidyverse)
source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

path_chtc <- format_path(str_c("llmpanel/chtc/train_", params$version))
path_data <- format_path("llmpanel/data_processed")

source(here::here(path_chtc, "input", "training_controls.R"))
theme_set(theme_classic()) 

likert_num <- 1:7
likert_txt <- c("strongly_disagree", "disagree", "somewhat_disagree",
               "neutral", "somewhat_agree", "agree", "strongly_agree")
```

## Data
```{r}
d <- read_csv(here::here(path_chtc, "input", "data_trn.csv"), show_col_types = FALSE) |> 
  format_data() |> 
  mutate(y_txt = recode_values(y,
                               from = likert_num,
                               to = likert_txt),
         y_txt = fct(y_txt, levels = likert_txt)) |> 
  glimpse()

# f <- read_csv(here::here(path_chtc, "output",
#                          str_c("batch_results_", params$version, ".csv")), 
#               show_col_types = FALSE) |> 
#   glimpse()

# p <- read_csv(here::here(path_data, "posterior_rsq.csv"))

```


## Message ratings Histogram

LLM messages are generally rated as helpful
```{r}
d |>
  ggplot(aes(x = y_txt)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Message Rating", y = "Count", title = "Distribution of Message Ratings")
```

```{r}
d |> summarize(mean = mean(y),
               med = median(y),
               iqr = IQR(y),
               sd = sd(y),
               min = min(y),
               max = max(y))
```

## Messages by tone and style

There is not one uniformly preferred tone or style by any substantial margin.

This is clear in the plots of means by tone and style
```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone)) |> 
  ggplot(aes(x = tone, y = avg_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", 
       title = "Mean Message Rating by Tone") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(style)) |> 
  ggplot(aes(x = style, y = avg_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Style", y = "Mean Message Rating", 
       title = "Mean Message Rating by Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone, style)) |> 
  ggplot(aes(x = tone, y = avg_rating, fill = style)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", fill = "Style",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```


This is also clear in when selecting the top tone and style for each participant
```{r}
d |> group_by(subid, tone) |> 
  summarize(mean = mean(y)) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  tab(tone)
  
d |> group_by(subid, style) |> 
  summarize(mean = mean(y)) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  tab(style)
```


And if we look at the mean ratings in their best and worst tone/style
```{r}

top <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "best") 
bot <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(mean) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "worst") 

all <- top |> 
  bind_rows(bot)

all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond)
```

```{r}
all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond) |>
  ggplot(aes(x = cond, y = mean)) +
  geom_col() +
  labs(x = "Condition", y = "Mean")
```


If we want the best response, need to identify best tone/style per person

We need a prediction model that can predict their ratings in each tone/style and then we can select 
the best condition for them

## Posterior

```{r}
pp_wide_rsq <- read_csv(here::here(path_data, "posterior_rsq.csv"),
                        show_col_types = FALSE)

# Colin - UPDATE THIS AND ALSO UPDATE LATER FOR MAE
q = c(.025, .5, .975)

# baseline
pp_wide_rsq |> 
  summarize(mean = mean(baseline),
            median = quantile(baseline, probs = q[2]),
            lower = quantile(baseline, probs = q[1]), 
            upper = quantile(baseline, probs = q[3]))

# demographics
pp_wide_rsq |> 
  summarize(mean = mean(demographics),
            median = quantile(demographics, probs = q[2]),
            lower = quantile(demographics, probs = q[1]), 
            upper = quantile(demographics, probs = q[3]))

# preferences
pp_wide_rsq |> 
  summarize(mean = mean(preferences),
            median = quantile(preferences, probs = q[2]),
            lower = quantile(preferences, probs = q[1]), 
            upper = quantile(preferences, probs = q[3]))

# dem vs base
pp_wide_rsq |> 
  summarize(mean = mean(dem_v_base),
            median = quantile(dem_v_base, probs = q[2]),
            lower = quantile(dem_v_base, probs = q[1]), 
            upper = quantile(dem_v_base, probs = q[3]))

# pref vs dem 
pp_wide_rsq |> 
  summarize(mean = mean(pref_v_dem),
            median = quantile(pref_v_dem, probs = q[2]),
            lower = quantile(pref_v_dem, probs = q[1]), 
            upper = quantile(pref_v_dem, probs = q[3]))
```

```{r}
pp_tidy_rsq |> 
  ggplot(aes(x = posterior, fill = model)) +
  geom_histogram(bins = 30) +
  scale_fill_manual(values = c("#dadfe1", "#646569", "#9b0000"), guide = "none") +
  xlab("R-Squared") +
  facet_wrap(vars(model), nrow = 3)
```


## Assignment

```{r}
assign <- d |> 
  mutate(min_tone = pmin(q1_legitimizing_num, q2_self_efficacy_num, q3_acknowledging_num,
                         q4_value_affirmation_num, q5_norms_num, na.rm = TRUE)) |> 
  mutate(max_tone = pmax(q1_legitimizing_num, q2_self_efficacy_num, q3_acknowledging_num,
                         q4_value_affirmation_num, q5_norms_num, na.rm = TRUE)) |> 
  mutate(diff = max_tone - min_tone) 

assign_best <- assign |>
  group_by(subid) |>
  filter((style == "formal" & str_detect(q6_formality, "_formal")) |
         (style == "informal" & str_detect(q6_formality, "_informal"))) |>
  ungroup() |>
  filter_out(tone == "legitimizing" & q1_legitimizing_num < max_tone) |> 
  filter_out(tone == "self_efficacy" & q2_self_efficacy_num < max_tone) |> 
  filter_out(tone == "acknowledging" & q3_acknowledging_num < max_tone) |> 
  filter_out(tone == "value_affirmation" & q4_value_affirmation_num < max_tone) |> 
  filter_out(tone == "norms" & q5_norms_num < max_tone)  |> 
  mutate(assign = "preferred")


mean(assign_best$message_rating_num)

assign_other <- assign |>
  group_by(subid) |>
  filter((style == "formal" & str_detect(q6_formality, "_informal")) |
         (style == "informal" & str_detect(q6_formality, "_formal"))) |>
  ungroup() |>
  filter_out(tone == "legitimizing" & q1_legitimizing_num == max_tone) |> 
  filter_out(tone == "self_efficacy" & q2_self_efficacy_num == max_tone) |> 
  filter_out(tone == "acknowledging" & q3_acknowledging_num == max_tone) |> 
  filter_out(tone == "value_affirmation" & q4_value_affirmation_num == max_tone) |> 
  filter_out(tone == "norms" & q5_norms_num == max_tone)  |> 
  mutate(assign = "other")

mean(assign_other$message_rating_num)

assign_all <- assign_best |> 
  bind_rows(assign_other)


assign_all |>
  summarise(mean_rating = mean(message_rating_num),
            sd = sd(message_rating_num) / sqrt(n()),
            .by = assign) |> 
  ggplot(aes(x = assign, y = mean_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean_rating - sd, ymax = mean_rating + sd),
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Message Category", y = "Mean Message Rating", fill = "Style",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

