---
title: "Descriptives"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 2
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
params:
  version: "v7"
---

## Setup
```{r}
#| include: false

library(tidyverse)
library(tidymodels)
library(Matrix)

source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

path_chtc <- format_path(str_c("llmpanel/chtc/train_", params$version))
path_data <- format_path("llmpanel/data_processed")

source(here::here(path_chtc, "input", "training_controls.R"))
theme_set(theme_classic()) 

likert_num <- 1:7
likert_txt <- c("strongly_disagree", "disagree", "somewhat_disagree",
               "neutral", "somewhat_agree", "agree", "strongly_agree")
```

## Data & Models
```{r}
d <- read_csv(here::here(path_chtc, "input", "data_trn.csv"), 
              show_col_types = FALSE) |> 
  format_data() |> 
  mutate(y_txt = recode_values(y,
                               from = likert_num,
                               to = likert_txt),
         y_txt = fct(y_txt, levels = likert_txt)) |> 
  glimpse()

# update to use long format
pp_wide_rsq <- read_csv(here::here(path_data, 
                                   str_c("posterior_rsq_", 
                                         params$version, ".csv")),
                        show_col_types = FALSE)

# ADD PP for mean y


model <- read_rds(here::here(path_data, 
                             str_c("model_pref_", params$version, ".rds")))


#  NEED to get data on individual tones/styles

```


## Message ratings Histogram

LLM messages are generally rated as helpful
```{r}
d |>
  ggplot(aes(x = y_txt)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Message Rating", y = "Count", title = "Distribution of Message Ratings")
```


## Messages by tone and style

There is not one uniformly preferred tone or style by any substantial margin.

This is clear in the plots of means by tone and style

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone, style)) |> 
  ggplot(aes(x = tone, y = avg_rating, fill = style)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", fill = "Style",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```


This is also clear in when selecting the top tone and style for each participant
```{r}
d |> unite(tone_style,tone, style, sep = " & ") |> 
  summarize(mean = mean(y), 
            .by = c(subid, tone_style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  tab(tone_style) |> 
  arrange(desc(prop))
```

And if we look at the mean ratings in their best and worst tone/style


NOTE:   THIS  NEEDS TO BE DONE IN HELD OUT DATA using CV
We can then do a bayesian comparison with same performance from model predictions
```{r}
top <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "best") 
bot <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(mean) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "worst") 

all <- top |> 
  bind_rows(bot)

all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond)
```

```{r}
all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond) |>
  ggplot(aes(x = cond, y = mean)) +
  geom_col() +
  labs(x = "Condition", y = "Mean")
```


If we want the best response, need to identify best tone/style per person

We need a prediction model that can predict their ratings in each tone/style and then we can select 
the best condition for them

## Posterior

```{r}

q = c(.025, .5, .975)

# preferences
pp_wide_rsq |> 
  summarize(mean = mean(preferences),
            median = quantile(preferences, probs = q[2]),
            lower = quantile(preferences, probs = q[1]), 
            upper = quantile(preferences, probs = q[3]))

```

```{r}
pp_wide_rsq |> 
  select(sample, preferences) |> 
  ggplot(aes(x = preferences)) +
  geom_histogram(bins = 30) +
  scale_fill_manual(values = "#dadfe1", guide = "none") +
  xlab("R-Squared")
```


## Display model

```{r}

tidy(model) |>
  filter(term != "(Intercept)") |>
  filter(estimate != 0) |>
  mutate(
    direction = if_else(estimate > 0, "positive", "negative"),
    abs_estimate = abs(estimate),
    feature_type = if_else(str_detect(term, "_x_"), "Interaction", "Main Effect")
  ) |>
  filter(feature_type == "Interaction") |> 
  slice_max(abs_estimate, n = 30) |>
  arrange(abs_estimate) |>
  mutate(term = factor(term, levels = term)) |>
  ggplot(aes(x = abs_estimate, y = term, fill = direction)) +
  geom_col() +
  scale_fill_manual(
    values = c("positive" = "forestgreen", "negative" = "firebrick"),
    name = "Direction"
  ) +
  labs(
    x = "Absolute Coefficient",
    y = NULL,
    title = "Feature Importance"
  )
```

## Assignment


And here is what people are assigned

Compare to what we get with MEAN model

```{r}
preds |> 
  group_by(subid) |> 
  slice_head(n = 1) |> 
  ungroup() |> 
  unite(tone_style, tone, style, sep = " & ", remove = FALSE) |> 
  tab(tone_style) |> 
  arrange(desc(prop))
```

