---
title: "Descriptives"
author: "John Curtin"
date: "`r lubridate::today()`"
params:
  version: "v8"
format:
  html:
    embed-resources: true
    toc: true 
    toc_depth: 2
editor_options: 
  chunk_output_type: console
---

## Setup
```{r}
#| include: false

library(tidyverse)
library(tidymodels)
library(Matrix)

source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

path_chtc <- format_path(str_c("llmpanel/chtc/train_", params$version))
path_data <- format_path("llmpanel/data_processed")

source(here::here(path_chtc, "input", "training_controls.R"))
theme_set(theme_classic()) 

```

## Data & Models
```{r}
# raw data
likert_num <- 1:7
likert_txt <- c("strongly_disagree", "disagree", "somewhat_disagree",
               "neutral", "somewhat_agree", "agree", "strongly_agree")
d <- read_csv(here::here(path_chtc, "input", "data_trn.csv"), 
              show_col_types = FALSE) |> 
  format_data() |> 
  mutate(y_txt = recode_values(y,
                               from = likert_num,
                               to = likert_txt),
         y_txt = fct(y_txt, levels = likert_txt))

# pp for model 
pp_rsq <- read_csv(here::here(path_data, 
                                   str_c("posterior_rsq_", 
                                         params$version, ".csv")),
                        show_col_types = FALSE)

# PP for mean y
pp_mean_y<- read_csv(here::here(path_data, 
                                   str_c("posterior_mean_y_", 
                                         params$version, ".csv")),
                       show_col_types = FALSE)
                     
                     
# individual tones and styles                     
preds_best <- read_csv(here::here(path_data, 
                                  str_c("preds_best_", params$version, ".csv")),
                       show_col_types = FALSE)

# prediction model
model <- read_rds(here::here(path_data, 
                             str_c("model_pref_", params$version, ".rds")))
```


## Message ratings Histogram

LLM messages are generally rated as helpful
```{r}
d |>
  ggplot(aes(x = y_txt)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Message Rating", y = "Count", title = "Distribution of Message Ratings")
```


## Messages by tone and style

There is not one uniformly preferred tone or style by any substantial margin.

This is clear in the plots of means by tone and style

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone, style)) |> 
  arrange(desc(avg_rating))
```

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone, style)) |> 
  ggplot(aes(x = tone, y = avg_rating, fill = style)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", fill = "Style",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```


This is also clear in when selecting the top tone and style for each participant
```{r}
d |> unite(tone_style,tone, style, sep = " & ") |> 
  summarize(mean = mean(y), 
            .by = c(subid, tone_style)) |> 
  slice_max(order_by = mean, n = 1,
            by = subid) |>  
  tab(tone_style) |> 
  arrange(desc(prop))
```

## Prediction model

### Posterior
```{r}
q = c(.025, .5, .975)
pp_rsq |> 
  summarize(mean = mean(posterior),
            median = quantile(posterior, probs = q[2]),
            lower = quantile(posterior, probs = q[1]), 
            upper = quantile(posterior, probs = q[3]))
```

```{r}
pp_rsq |> 
  ggplot(aes(x = posterior)) +
  geom_histogram(bins = 30) +
  scale_fill_manual(values = "#dadfe1", guide = "none") +
  xlab("R-Squared")
```


### Feature importance

JJC code
```{r}
tidy(model) |>
  filter(term != "(Intercept)") |>
  filter(estimate != 0) |>
  mutate(
    direction = if_else(estimate > 0, "positive", "negative"),
    abs_estimate = abs(estimate),
    feature_type = if_else(str_detect(term, "_x_"), 
                           "Interaction", 
                           "Main Effect")) |>
  filter(feature_type == "Interaction") |> 
  mutate(feature_cat = if_else(str_detect(term, "pref_"), 
                               "Preferences", 
                               "Demographics")) |>
  mutate(feature_cat = fct(feature_cat, 
                           levels = c("Preferences", "Demographics"))) |>
  slice_max(abs_estimate, n = 12, by = feature_cat) |>
  arrange(feature_cat, abs_estimate) |>
  mutate(term = factor(term, levels = term)) |>
  ggplot(aes(x = abs_estimate, y = term, fill = direction)) +
  geom_col() +
  scale_fill_manual(
    values = c("positive" = "forestgreen", "negative" = "firebrick"),
    name = "Direction"
  ) +
  facet_wrap(~ feature_cat, scales = "free_y") +
  labs(
    x = "Absolute Coefficient",
    y = NULL
  )
```

```{r}
interaction_df <- tidy(model) |>
  filter(term != "(Intercept)", estimate != 0) |>
  mutate(
    direction = if_else(estimate > 0, "positive", "negative"),
    abs_estimate = abs(estimate),
    feature_type = if_else(str_detect(term, "_x_"), "Interaction", "Main Effect")
  ) |>
  filter(feature_type == "Interaction") |>
  mutate(
    left  = str_split_fixed(term, "_x_", 2)[,1],
    right = str_split_fixed(term, "_x_", 2)[,2],
    left = left |>
      str_remove("^(tone|style)_") |> 
      str_replace_all("_", " ") |>
      (\(x) {
        words <- str_split(x, " ")
        sapply(words, \(w) if (length(w) > 1) w[2] else w[1])
      })(),
    right = right |>
      str_replace("^dem_.*?_(.*?)_yes$", "dem_\\1") |>
      str_replace_all("_", " "),
    clean_term = paste(left, "×", right)
  )

plot_interactions <- function(df, right_prefix, plot_title) {
  df |>
    filter(str_starts(right, right_prefix)) |>
    slice_max(abs_estimate, n = 30) |>
    arrange(abs_estimate) |>
    mutate(clean_term = factor(clean_term, levels = clean_term)) |>
    ggplot(aes(x = abs_estimate, y = clean_term, fill = direction)) +
    geom_col() +
    scale_fill_manual(
      values = c("positive" = "forestgreen", "negative" = "firebrick"),
      name = "Direction"
    ) +
    scale_x_continuous(
      breaks = seq(0, 0.7, by = 0.1),
      limits = c(0, 0.7)
    ) +
    labs(
      x = "Absolute Coefficient",
      y = NULL,
      title = plot_title
    )
}

plot_dem  <- plot_interactions(interaction_df, "dem",  "Feature Importance — Demographics")
plot_pref <- plot_interactions(interaction_df, "pref", "Feature Importance — Baseline Preferences")

plot_dem
plot_pref
```

Model assignments

```{r}
preds_best |> tab(tone_style) |> 
  arrange(desc(n))
```


## Comparing strategies

```{r}
old_labels <- unique(pp_mean_y$model)
new_labels <- c("all tones/styles", "mean tones/styles", "individual tones/styles")

pp_mean_y |> 
  mutate(model = recode_values(model, from = old_labels, to = new_labels),
         model = fct(model, levels = new_labels)) |> 
  ggplot(aes(x = posterior, fill = model)) +
  geom_histogram(bins = 30) +
  scale_fill_manual(values = c("#dadfe1", "#646569", "#9b0000"), guide = "none") +
  xlab("Posterior(Mean Message Helpfulness)") +
  facet_wrap(vars(model), nrow = 3)
```