---
title: "Descriptives"
author: "John Curtin"
date: "`r lubridate::today()`"
output: 
  html_document:
    toc: true 
    toc_depth: 2
format:
  html:
    embed-resources: true
editor_options: 
  chunk_output_type: console
params:
  version: "v6"
---

## Setup
```{r}
#| include: false

library(tidyverse)
library(tidymodels)
library(Matrix)

source("https://github.com/jjcurtin/lab_support/blob/main/format_path.R?raw=true")
source("https://github.com/jjcurtin/lab_support/blob/main/fun_eda.R?raw=true")

path_chtc <- format_path(str_c("llmpanel/chtc/train_", params$version))
path_data <- format_path("llmpanel/data_processed")

source(here::here(path_chtc, "input", "training_controls.R"))
theme_set(theme_classic()) 

likert_num <- 1:7
likert_txt <- c("strongly_disagree", "disagree", "somewhat_disagree",
               "neutral", "somewhat_agree", "agree", "strongly_agree")
```

## Data & Models
```{r}
d <- read_csv(here::here(path_chtc, "input", "data_trn.csv"), 
              show_col_types = FALSE) |> 
  format_data() |> 
  mutate(y_txt = factor(y, levels = likert_num, labels = likert_txt)) |> 
  glimpse()

pp_wide_rsq <- read_csv(here::here(path_data, 
                                   str_c("posterior_rsq_", 
                                         params$version, ".csv")),
                        show_col_types = FALSE)

model <- read_rds(here::here(path_data, 
                             str_c("model_pref_", params$version, ".rds")))

preds <- read_csv(here::here(path_data, 
                             str_c("pred_conditions_", params$version, ".csv")),
                  show_col_types = FALSE)

# f <- read_csv(here::here(path_chtc, "output",
#                          str_c("batch_results_", params$version, ".csv")), 
#               show_col_types = FALSE) |> 
#   glimpse()

# p <- read_csv(here::here(path_data, "posterior_rsq.csv"))

```

## GOAL 1: Can we generate messages using LLMs, and will people find them helpful?

## Message ratings Histogram

LLM messages are generally rated as helpful
```{r}
d |>
  ggplot(aes(x = y_txt)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 30)) +
  labs(x = "Message Rating", y = "Count", title = "Perceived Helpfulness of Message Ratings")
```

```{r}
d |> summarize(mean = mean(y),
               sd = sd(y),
               min = min(y),
               max = max(y))
```

## GOAL 2: Is there an overall preferred tone and style?

## Messages by tone and style

There is not one uniformly preferred tone or style by any substantial margin.

This is clear in the plots of means by tone and style
```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone)) |> 
  ggplot(aes(x = tone, y = avg_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", 
       title = "Mean Message Rating by Tone") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(style)) |> 
  ggplot(aes(x = style, y = avg_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Style", y = "Mean Message Rating", 
       title = "Mean Message Rating by Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

```{r}
d |>
  summarise(avg_rating = mean(y),
            .by = c(tone, style)) |> 
  ggplot(aes(x = tone, y = avg_rating, fill = style)) +
  geom_bar(stat = "identity", position = "dodge") +
  # geom_errorbar(aes(ymin = avg_rating - sd, ymax = mean_rating + sd),
  #               position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Tone", y = "Mean Message Rating", fill = "Style",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

## GOAL 3: Can we build a prediction model to determine the best tone/style for each participant?

This is also clear in when selecting the top tone and style for each participant
```{r}
d |> summarize(mean = mean(y), 
               .by = c(subid, tone)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  tab(tone)
  
d |> summarize(mean = mean(y),
               .by = c(subid, style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  tab(style)

## and now for both tone and style:
d |> 
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  unite(tone_style, tone, style, sep = " & ", remove = FALSE) |> 
  tab(tone_style)

```

And if we look at the mean ratings in their best and worst tone/style
```{r}
top <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(desc(mean)) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "best") 
bot <- d |>
  summarize(mean = mean(y), 
            .by = c(subid, tone, style)) |> 
  group_by(subid) |> 
  arrange(mean) |>  
  slice_head(n = 1) |> 
  ungroup() |> 
  mutate(cond = "worst") 

all <- top |> 
  bind_rows(bot)

all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond)
```

```{r}
all |>
  summarise(mean = mean(mean, na.rm = TRUE), .by = cond) |>
  ggplot(aes(x = cond, y = mean)) +
  geom_col() +
  labs(x = "Condition", y = "Mean")
```


If we want the best response, need to identify best tone/style per person

We need a prediction model that can predict their ratings in each tone/style and then we can select 
the best condition for them EDIT: removed model comparisons


## Display model

```{r}

tidy(model) |>
  filter(term != "(Intercept)") |>
  filter(estimate != 0) |>
  filter(str_detect(term, "_x_")) |>
  mutate(
    direction = if_else(estimate > 0, "positive", "negative"),
    abs_estimate = abs(estimate),
    feature_type = if_else(str_detect(term, "_x_"), "Interaction", "Main Effect")
  ) |>
  slice_max(abs_estimate, n = 15, by = feature_type) |>
  arrange(feature_type, abs_estimate) |>
  mutate(term = factor(term, levels = term)) |>
  ggplot(aes(x = abs_estimate, y = term, fill = direction)) +
  geom_col() +
  scale_fill_manual(
    values = c("positive" = "forestgreen", "negative" = "firebrick"),
    name = "Direction"
  ) +
  facet_wrap(~ feature_type, scales = "free_y") +
  labs(
    x = "Absolute Coefficient",
    y = NULL,
    title = "Feature Importance"
  )
```
## GOAL 4: If we assign to best category, what are the categories and what are the ratings?

## Assignment

```{r}
preds |>
  summarise(mean_rating = mean(y),
            sd = sd(y),
            .by = cond) 

preds |>
  summarise(mean_rating = mean(y),
            sd = sd(y) / sqrt(n()),
            .by = cond) |> 
  ggplot(aes(x = cond, y = mean_rating)) +
  geom_bar(stat = "identity", position = "dodge") +
  geom_errorbar(aes(ymin = mean_rating - sd, ymax = mean_rating + sd),
                position = position_dodge(width = 0.9), width = 0.25) +
  labs(x = "Message Category", y = "Mean Message Rating",
       title = "Mean Message Rating by Tone and Style") +
  ylim(0, 7) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

And here is what people are assigned

```{r}
preds |> 
  group_by(subid) |> 
  slice_head(n = 1) |> 
  ungroup() |> 
  unite(tone_style, tone, style, sep = " & ", remove = FALSE) |> 
  tab(tone_style)
```

